---
title: "Step I: Data Cleaning"
subtitle: "Project.title"
author:
  - name: Nicholas R. Jenkins 
    affiliation: University of California, Riverside
    affiliation_url: https://www.ucr.edu
description: |
  This document shows all the code used to clean the data for this project. 
  Each step has been carefully documented and will replicate the data set used
  in the study. For any questions about this code, please contact 
  Nick Jenkins at [nicholas.jenkins@email.ucr.edu](mailto:nicholas.jenkins@email.ucr.edu).
abstract: |
  This document shows all the code used to clean the data for this project. 
  Each step has been carefully documented and will replicate the data set used
  in the study. For any questions about this code, please contact 
  Nick Jenkins at [nicholas.jenkins@email.ucr.edu](mailto:nicholas.jenkins@email.ucr.edu).
date: "`r Sys.Date()`"
output: 
  radix: radix::radix_article
  html_notebook: 
    highlight: monochrome
    theme: simplex
    toc: yes
    code_folding: 
  html_document:
    highlight: monochrome
    theme: simplex
    toc: yes
    code_folding:
  pdf_document:
    toc: yes
  github_document:
    toc: yes
#bibliography: /Users/nick/Documents/Research/References/BibTeX/biblatex.bib
---

# Environment Preperation

This section clears the current working environment and loads the packages used to clean the data. I also create the function `comma()` to format any in-line output values to have thousands separators and only two digits. 

```{r setup, warning = FALSE, message = FALSE, results = "hide", echo = TRUE}
# Clear Environment -----------------------------------------------------------
rm(list = ls())

# Load Packages ---------------------------------------------------------------
packages <- c("tidyverse", "stargazer", "foreign", "sqldf")
lapply(packages, require, character.only = TRUE)

# Inline Formatting -----------------------------------------------------------
comma <- function(x) format(x, digits = 2, big.mark = ",")
```

# Import Data




# Final Data Set Summary Statistics 

```{r Summary Statistics, echo = TRUE}

```

## Acknowledgements {.appendix}

All data cleaning was done using RStudio running **R** version 
`r R.version$major`.`r R.version$minor` "`r R.version$nickname`".



