---
title: "Step II: Data Visualization"
subtitle: "PACs and Small-dollar Donations"
author:
  - name: Nicholas R. Jenkins 
    affiliation: University of California, Riverside
    affiliation_url: https://www.ucr.edu
abstract: |
  This document shows all the code used to visualize the data for this project. 
  All graphs and figures were created using RStudio running R version 
  `r R.version$major`.`r R.version$minor` "`r R.version$nickname`". 
  
  Each step has been carefully documented and will replicate the graphs and
  figures used in the manuscript. The code for this document can be downloaded 
  using the button in the top right corner. For any questions about this code, 
  please contact Nick Jenkins at 
  [nicholas.jenkins@email.ucr.edu](mailto:nicholas.jenkins@email.ucr.edu).
date: "`r Sys.Date()`"
output: 
  html_notebook: 
    highlight: pygments
    theme: paper
    toc: yes
    code_folding: 
    toc_float: true
bibliography: /Users/nick/Documents/Research/References/BibTeX/biblatex.bib
editor_options: 
  chunk_output_type: inline
---

# Environment Preperation

This section clears the current working environment and loads the packages used to visualize the data. I also create the function `comma()` to format any in-line output values to have thousands separators and only two digits. 

```{r setup, warning = FALSE, message = FALSE, echo = TRUE, results = "hide"}
# Clear Environment -----------------------------------------------------------
rm(list = ls())

# Load Packages ---------------------------------------------------------------
packages <- c("tidyverse", "foreign", "stargazer", "maps", "mapdata", 
              "maptools", "ggmap", "DataExplorer", "ggpubr", "ggthemes", 
              "scales")
lapply(packages, require, character.only = TRUE)

# Inline Formatting -----------------------------------------------------------
comma <- function(x) format(x, digits = 2, big.mark = ",")

# Set Global Chunk Options ----------------------------------------------------
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  comment = "##",
  R.options = list(width = 70)
)
```

# Import Data

This section imports the data cleaned in the "Step I: Data Cleaning" document to begin visualizing the data. 

```{r Data Import}
load("Data/Clean Data/estimation_data.RDa")
```


# Data Visulization

```{r Visulization}
plot_intro(estimation.data)

plot_density(estimation.data)
```


# Plot Campaign Spending

```{r fig.width = 15}
ggplot(data = estimation.data, aes(x = no_corp_pacs, y = net_spent)) +
  geom_col() +
  scale_y_continuous(labels = dollar_format(), breaks = pretty_breaks(n = 8)) +
  theme_pubr()

plot.data <- 
  estimation.data %>%
  filter(candidate_contribs < 10000000) %>% # drop outlier
  select(no_corp_pacs, new_member, tot_pac_money, num_pac_contribs, 
         business_pacs, dir_business_pacs, in_kind_business_pacs, 
         ind_business_pacs, candidate_contribs, dir_pac_cand_committee, 
         dir_pac_party_committee, ik_pac_party_committee, 
         ind_pac_party_committee, ce_pac_party_committee, labor_pacs, 
         dir_pac_labor, ik_pac_labor, ind_pac_labor, ideological_pacs, 
         dir_pac_ideological, ik_pac_ideological, ind_pac_ideological, 
         ce_pac_ideological, leadership_pacs, net_indiv_total, large_indiv, 
         small_indiv, indiv_ideological, indiv_cand_committee, 
         indiv_party_committee, indiv_self_finance, indiv_biz, indiv_labor, 
         net_spent, net_receipts) %>%
  gather(tot_pac_money, num_pac_contribs, business_pacs, dir_business_pacs, 
         in_kind_business_pacs, ind_business_pacs, candidate_contribs, 
         dir_pac_cand_committee, dir_pac_party_committee, 
         ik_pac_party_committee, ind_pac_party_committee, 
         ce_pac_party_committee, labor_pacs, dir_pac_labor, ik_pac_labor, 
         ind_pac_labor, ideological_pacs, dir_pac_ideological, 
         ik_pac_ideological, ind_pac_ideological, ce_pac_ideological, 
         leadership_pacs, net_indiv_total, large_indiv, small_indiv, 
         indiv_ideological, indiv_cand_committee, indiv_party_committee, 
         indiv_self_finance, indiv_biz, indiv_labor, net_spent, net_receipts,
         key = "group", value = "value") %>%
  mutate(no_corp_pacs = factor(no_corp_pacs,
                               levels = c("NO", "YES"),
                               labels = c("Yes to Corporate PAC Donations", 
                                          "No to Corporate PAC Donations")),
         new_member = factor(new_member,
                             levels = c("NO", "YES"),
                             labels = c("Incumbent", "New Member")),
         group = factor(group,
                        levels = c("tot_pac_money", "num_pac_contribs", 
                                   "business_pacs", "dir_business_pacs", 
                                   "in_kind_business_pacs", "ind_business_pacs", 
                                   "candidate_contribs", "dir_pac_cand_committee", 
                                   "dir_pac_party_committee", 
                                   "ik_pac_party_committee", 
                                   "ind_pac_party_committee", 
                                   "ce_pac_party_committee", "labor_pacs", 
                                   "dir_pac_labor", "ik_pac_labor", 
                                   "ind_pac_labor", "ideological_pacs", 
                                   "dir_pac_ideological", 
                                   "ik_pac_ideological", "ind_pac_ideological", 
                                   "ce_pac_ideological", 
                                   "leadership_pacs", "net_indiv_total", 
                                   "large_indiv", "small_indiv", 
                                   "indiv_ideological", "indiv_cand_committee", 
                                   "indiv_party_committee", 
                                   "indiv_self_finance", "indiv_biz", 
                                   "indiv_labor", "net_spent", "net_receipts"),
                        labels = c("Total PAC Money", 
                                   "Number of PAC Contributors", "Business PACs",
                                   "Direct Business PACs", 
                                   "In-kind Business PACs", 
                                   "Indirect Business PACs", 
                                   "Candidate Contributions", 
                                   "Direct Candidate Committee Contributions",
                                   "Direct Party Contributions", 
                                   "In-kind Party Contributions", 
                                   "Indp. Party Expendatures",
                                   "Coordinated Party Exp.",
                                   "Labor PACs", "Direct Labor PACs",
                                   "In-kind Labor PACs",
                                   "Indp. Labor PAC Exp.",
                                   "Ideological PACs", 
                                   "Direct Ideological PACs",
                                   "In-kind Ideological PACs",
                                   "Indp. Ideological PA C Exp.",
                                   "Coordinated Ideological PAC Exp.",
                                   "Leadership PACs", "Total Individual",
                                   "Large Individual", "Small Individual",
                                   "Ideological Individual", 
                                   "Candidate Individual",
                                   "Party Individual", "Self-finance",
                                   "Business Individual", "Labor Individual",
                                   "Net Spent", "Net Receipts"))) %>%
  group_by(group, no_corp_pacs, new_member) %>%
  summarise(sum = mean(value))

# Business PAC plot
plot.data %>%
  filter(str_detect(group, pattern = "Business PACs")) %>%
ggplot(aes(x = reorder(group, sum), y = sum)) +
  geom_col() +
  geom_text(aes(label = comma(round(sum, digits = 0))),
            vjust = -1) +
  facet_wrap(new_member ~ no_corp_pacs) + 
  scale_y_continuous(labels = dollar_format(), 
                     breaks = pretty_breaks(n = 5),
                     limits = c(0, 550000)) +
  labs(x = "", y = "") +
  theme_pubr() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
ggsave("Figures/biz_contribs.pdf", width = 15, height = 8)

# Ideological PAC plot
plot.data %>%
  filter(str_detect(group, pattern = "Ideological") & 
           str_detect(group, pattern = "Individual", negate = TRUE)) %>%
ggplot(aes(x = reorder(group, sum), y = sum)) +
  geom_col() +
  geom_text(aes(label = comma(round(sum, digits = 0))),
            vjust = -1) +
  facet_wrap(new_member ~ no_corp_pacs) + 
  scale_y_continuous(labels = dollar_format(), 
                     breaks = pretty_breaks(n = 5),
                     limits = c(0, 180000)) +
  labs(x = "", y = "") +
  theme_pubr() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
ggsave("Figures/ideo_contribs.pdf", width = 15, height = 8)

# Labor PAC plot
plot.data %>%
  filter(str_detect(group, pattern = "Labor") &
           str_detect(group, pattern = "Individual", negate = TRUE)) %>%
ggplot(aes(x = reorder(group, sum), y = sum)) +
  geom_col() +
  geom_text(aes(label = comma(round(sum, digits = 0))),
            vjust = -1) +
  facet_wrap(new_member ~ no_corp_pacs) + 
  scale_y_continuous(labels = dollar_format(), 
                     breaks = pretty_breaks(n = 6),
                     limits = c(0, 140000)) +
  labs(x = "", y = "") +
  theme_pubr() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
ggsave("Figures/labor_contribs.pdf", width = 15, height = 8)

# Party PAC plot
plot.data %>%
  filter((str_detect(group, pattern = "Party") | 
           str_detect(group, pattern = "Leadership") |
           str_detect(group, pattern = "Candidate")) &
           str_detect(group, pattern = "Individual", negate = TRUE)) %>%
ggplot(aes(x = reorder(group, sum), y = sum)) +
  geom_col() +
  geom_text(aes(label = comma(round(sum, digits = 0))),
            vjust = -1) +
  facet_wrap(new_member ~ no_corp_pacs) + 
  scale_y_continuous(labels = dollar_format(), 
                     breaks = pretty_breaks(n = 5),
                     limits = c(0, 500000)) +
  labs(x = "", y = "") +
  theme_pubr() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
ggsave("Figures/party_contribs.pdf", width = 15, height = 8)

# Individual Contributions plot
plot.data %>%
  filter(str_detect(group, pattern = "Individual") | 
           str_detect(group, pattern = "Self-finance")) %>%
ggplot(aes(x = reorder(group, sum), y = sum)) +
  geom_col() +
  geom_text(aes(label = comma(round(sum, digits = 0))),
            vjust = -1) +
  facet_wrap(new_member ~ no_corp_pacs) + 
  scale_y_continuous(labels = dollar_format(), 
                     breaks = pretty_breaks(n = 6),
                     limits = c(0, 3800000)) +
  labs(x = "", y = "") +
  theme_pubr() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
ggsave("Figures/indiv_contribs.pdf", width = 15, height = 8)
```

