---
title: "Step II: Data Visualization"
subtitle: "Project.title"
author:
  - Nicholas R. Jenkins^[University of California, Riverside]
abstract: |
  This document shows all the code used to visualize the data for this project. 
  All graphs and figures were created using RStudio running **R** version 
  `r R.version$major`.`r R.version$minor` "`r R.version$nickname`". 
  
  Each step has been carefully documented and will replicate the graphs and
  figures used in the manuscript. The code for this document can be downloaded 
  using the button in the top right corner. For any questions about this code, 
  please contact Nick Jenkins at 
  [nicholas.jenkins@email.ucr.edu](mailto:nicholas.jenkins@email.ucr.edu).
output:
  html_notebook: 
    highlight: monochrome
    theme: simplex
    toc: yes
    code_folding: 
  html_document:
    highlight: monochrome
    theme: simplex
    toc: yes
    code_folding:
  pdf_document:
    toc: yes
  github_document:
    toc: yes
date: "`r format(Sys.time(), '%B %d, %Y')`"
bibliography: /Users/nick/Documents/Research/Articles/biblatex.bib
---

# Environment Preperation

This section clears the current working environment and loads the packages used to visualize the data. I also create the function `comma()` to format any in-line output values to have thousands separators and only two digits. 

```{r setup, warning = FALSE, message = FALSE, results = FALSE}
# Clear Environment -----------------------------------------------------------
rm(list = ls())

# Load Packages ---------------------------------------------------------------
packages <- c("tidyverse", "foreign", "stargazer", "maps", "mapdata", 
              "maptools", "ggmap", "DataExplorer", "ggpubr", "ggthemes", 
              "scales")
lapply(packages, require, character.only = TRUE)

# Inline Formatting -----------------------------------------------------------
comma <- function(x) format(x, digits = 2, big.mark = ",")
```

# Import Data

This section imports the data cleaned in the "Step I: Data Cleaning" document to begin visualizing the data. 

```{r Data Import}
load("Data/Clean Data/estimation_data.RDa")
load("Data/Clean Data/contribution_data.Rda")
```


# Data Visulization

```{r Visulization}
plot_intro(estimation.data)

plot_density(estimation.data)
```


# Plot Campaign Spending

```{r fig.width = 7}
ggplot(data = estimation.data, aes(x = no_corp_pacs, y = net_spent)) +
  geom_col() +
  scale_y_continuous(labels = dollar_format(), breaks = pretty_breaks(n = 8)) +
  theme_pubr()

estimation.data %>%
  select(no_corp_pacs, new_member, tot_pac_money, business_pacs,
         dir_business_pacs, in_kind_business_pacs, ind_business_pacs, 
         dir_pac_cand_committee, dir_pac_party_committee, 
         ik_pac_party_committee, ind_pac_party_committee, 
         ce_pac_party_committee, dir_pac_labor, ik_pac_labor, ind_pac_labor,
         dir_pac_ideological, ik_pac_ideological, ind_pac_ideological, 
         ce_pac_ideological, ideological_pacs, labor_pacs, leadership_pacs,
         net_indiv_total, large_indiv, small_indiv, candidate_contribs, 
         indiv_ideological, indiv_cand_committee, indiv_jnt_cand_committee, 
         indiv_party_committee, indiv_self_finance) %>%
  gather(tot_pac_money, business_pacs,
         dir_business_pacs, in_kind_business_pacs, ind_business_pacs, 
         dir_pac_cand_committee, dir_pac_party_committee, 
         ik_pac_party_committee, ind_pac_party_committee, 
         ce_pac_party_committee, dir_pac_labor, ik_pac_labor, ind_pac_labor,
         dir_pac_ideological, ik_pac_ideological, ind_pac_ideological, 
         ce_pac_ideological, ideological_pacs, labor_pacs, leadership_pacs,
         net_indiv_total, large_indiv, small_indiv, candidate_contribs, 
         indiv_ideological, indiv_cand_committee, indiv_jnt_cand_committee, 
         indiv_party_committee, indiv_self_finance,
         key = "group", value = "value") %>%
  mutate(no_corp_pacs = factor(no_corp_pacs,
                               levels = c("NO", "YES"),
                               labels = c("Yes to Corporate PAC Donations", 
                                          "No to Corporate PAC Donations"))) %>%
  group_by(group, no_corp_pacs) %>%
  summarise(sum = sum(value)) %>%
ggplot(aes(x = group, y = sum)) +
  geom_col() +
  facet_wrap(~ no_corp_pacs) + 
  scale_y_continuous(labels = dollar_format(), 
                     breaks = pretty_breaks(n = 5),
                     limits = c(0, 150000000)) +
  labs(x = "", y = "") +
  theme_pubr() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
ggsave("Figures/contribs.pdf", width = 15, height = 8)
```

