---
title: "Step II: Data Visualization"
subtitle: "PACs and Small-dollar Donations"
author:
  - name: Nicholas R. Jenkins 
    affiliation: University of California, Riverside
    affiliation_url: https://www.ucr.edu
abstract: |
  This document shows all the code used to visualize the data for this project. 
  All graphs and figures were created using RStudio running R version 
  `r R.version$major`.`r R.version$minor` "`r R.version$nickname`". 
  
  Each step has been carefully documented and will replicate the graphs and
  figures used in the manuscript. The code for this document can be downloaded 
  using the button in the top right corner. For any questions about this code, 
  please contact Nick Jenkins at 
  [nicholas.jenkins@email.ucr.edu](mailto:nicholas.jenkins@email.ucr.edu).
date: "`r Sys.Date()`"
output: 
  html_notebook: 
    highlight: pygments
    theme: paper
    toc: yes
    code_folding: 
    toc_float: true
bibliography: /Users/nick/Documents/Research/References/BibTeX/biblatex.bib
editor_options: 
  chunk_output_type: inline
---

# Environment Preperation

This section clears the current working environment and loads the packages used to visualize the data. I also create the function `comma()` to format any in-line output values to have thousands separators and only two digits. 

```{r setup, warning = FALSE, message = FALSE, echo = TRUE, results = "hide"}
# Clear Environment -----------------------------------------------------------
rm(list = ls())

# Load Packages ---------------------------------------------------------------
packages <- c("tidyverse", "foreign", "stargazer", "maps", "mapdata", 
              "maptools", "ggmap", "DataExplorer", "ggpubr", "ggthemes", 
              "scales")
lapply(packages, require, character.only = TRUE)

# Inline Formatting -----------------------------------------------------------
comma <- function(x) format(x, digits = 2, big.mark = ",")

# Set Global Chunk Options ----------------------------------------------------
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  comment = "##",
  R.options = list(width = 70)
)
```

# Import Data

This section imports the data cleaned in the "Step I: Data Cleaning" document to begin visualizing the data. 

```{r Data Import}
load("Data/Clean Data/estimation_data.RDa")

estimation.data <- 
  estimation.data %>%
  mutate(chamber = str_sub(district, start = -2L, end = -1L),
         chamber = ifelse(str_detect(chamber, pattern = "S"), "Senate", "House"),
         vote_margin = vote_pct - 50) %>% 
  filter(chamber == "House")
```


# Data Visualization

```{r Visulization}
plot_intro(estimation.data)

plot_density(estimation.data)
```


# Plot Campaign Spending

```{r}
plot.data <- 
  estimation.data %>%
  select(no_corp_pacs, new_member, business_pacs, small_indiv, biz_contribs, 
         out_of_dist_biz_contrib, net_spent, net_receipts) %>%
  pivot_longer(cols = c(business_pacs, small_indiv, biz_contribs, 
                        out_of_dist_biz_contrib, net_spent, net_receipts),
               names_to = "group", values_to = "value") %>%
  mutate(group = factor(group,
                        levels = c("business_pacs", "small_indiv", 
                                   "biz_contribs", "out_of_dist_biz_contrib",
                                   "net_spent", "net_receipts"),
                        labels = c("Business PAC $", 
                                   "Small Indiv. $", "Business Indiv. $", 
                                   "Out-of-District Business Indiv. $",
                                   "Net Spent", "Net Receipts"))) %>%
  group_by(group, no_corp_pacs) %>%
  summarise(sum = mean(value, na.rm = TRUE))

ggplot(data = plot.data %>% 
         filter(group != "Net Spent" & group != "Net Receipts"), 
       aes(x = fct_reorder2(group, no_corp_pacs, sum), 
           y = sum, 
           color = no_corp_pacs)) +
  geom_linerange(aes(x = fct_reorder2(group, no_corp_pacs, sum), 
                     ymin = 0, ymax = sum), 
                 color = "grey65", 
                 size = 0.65,
                 position = position_dodge2(width = 0.7)) +
  geom_point(size = 6, position = position_dodge2(width = 0.7)) +
  #facet_wrap(~ fct_rev(no_corp_pacs)) +
  coord_flip() +
  scale_color_manual(values = c("grey71", "black"),
                     labels = c("No to Corporate PACs", 
                                "Yes to Corporate PACs")) +
  labs(x = "", y = "Mean Contributions", color = "") +
  #guides(fill = FALSE, color = FALSE, linetype = FALSE, shape = FALSE)+
  scale_y_continuous(labels = dollar_format(), breaks = pretty_breaks(n = 8)) +
  theme_pubr()
ggsave("Figures/all_candy.pdf", height = 4, width = 12)

# Spending and Receipts Plot
ggplot(data = plot.data %>% 
         filter(group == "Net Spent" | group == "Net Receipts"), 
       aes(x = fct_reorder2(group, no_corp_pacs, sum), 
           y = sum, 
           color = no_corp_pacs)) +
  geom_linerange(aes(x = fct_reorder2(group, no_corp_pacs, sum), 
                     ymin = 0, ymax = sum), 
                 color = "grey65", 
                 size = 0.65,
                 position = position_dodge2(width = 0.5)) +
  geom_point(size = 6, position = position_dodge2(width = 0.5)) +
  #facet_wrap(~ fct_rev(no_corp_pacs)) +
  coord_flip() +
  scale_color_manual(values = c("grey71", "black"),
                     labels = c("No to Corporate PACs", 
                                "Yes to Corporate PACs")) +
  labs(x = "", y = "Mean Contributions", color = "") +
  #guides(fill = FALSE, color = FALSE, linetype = FALSE, shape = FALSE)+
  scale_y_continuous(labels = dollar_format()) +
  theme_pubr()
ggsave("Figures/spending_candy.pdf", height = 3, width = 12)

# Color Figures ---------------------------------------------------------------
plot.data <- 
  estimation.data %>%
  select(no_corp_pacs, new_member, business_pacs, small_indiv, biz_contribs, 
         out_of_dist_biz_contrib, net_spent, net_receipts) %>%
  pivot_longer(cols = c(business_pacs, small_indiv, biz_contribs, 
                        out_of_dist_biz_contrib, net_spent, net_receipts),
               names_to = "group", values_to = "value") %>%
  mutate(group = factor(group,
                        levels = c("business_pacs", "small_indiv", 
                                   "biz_contribs", "out_of_dist_biz_contrib",
                                   "net_spent", "net_receipts"),
                        labels = c("Business PAC $", 
                                   "Small Indiv. $", "Business Indiv. $", 
                                   "Out-of-District $",
                                   "Net Spent", "Net Receipts"))) %>%
  group_by(group, no_corp_pacs) %>%
  summarise(sum = mean(value, na.rm = TRUE))

ggplot(data = plot.data %>% 
         filter(group != "Net Spent" & group != "Net Receipts") %>% 
         mutate(group = factor(group, 
                               levels = c("Small Indiv. $", 
                                          "Business PAC $",
                                          "Business Indiv. $",
                                          "Out-of-District $")),
                sum_f = round(sum, 0)), 
       aes(x = fct_rev(group), 
           y = sum, 
           color = no_corp_pacs,
           shape = no_corp_pacs,
           label = dollar(sum_f))) +
  geom_linerange(aes(x = group, 
                     ymin = 0, ymax = sum), 
                 color = "lightgray", 
                 size = 2,
                 position = position_dodge2(width = 0.7)) +
  geom_point(size = 7, position = position_dodge2(width = 0.7)) +
  geom_label(position = position_dodge(width = 2.2),
             aes(x = group, y = sum, fill = no_corp_pacs),
             color = "white", fontface = "bold") +
  coord_flip() +
  scale_color_manual(values = c("#00AFBB", "#E7B800"),
                     labels = c("Yes to Corporate PACs",
                                "No to Corporate PACs")) +
  scale_fill_manual(values = c("#00AFBB", "#E7B800"),
                    labels = c("Yes to Corporate PACs",
                                "No to Corporate PACs")) +
  scale_shape_manual(values = c("NO" = 15, "YES" = 16),
                     labels = c("Yes to Corporate PACs",
                                "No to Corporate PACs")) +
  labs(x = "", y = "Average Amount of Money Received", color = "", shape = "") +
  guides(fill = FALSE, linetype = FALSE) +
  scale_y_continuous(labels = dollar_format(), breaks = pretty_breaks(n = 8)) +
  theme_pubclean(flip = TRUE)
ggsave("Figures/all_candy_color_2.pdf", height = 5, width = 12)

# Spending and Receipts Plot
ggplot(data = plot.data %>% 
         filter(group == "Net Spent" | group == "Net Receipts") %>% 
         mutate(sum_f = round(sum, 0)), 
       aes(x = fct_rev(group), 
           y = sum, 
           color = no_corp_pacs,
           shape = no_corp_pacs,
           label = dollar(sum_f))) +
  geom_linerange(aes(x = fct_reorder2(group, no_corp_pacs, sum), 
                     ymin = 0, ymax = sum), 
                 color = "lightgray", 
                 size = 2,
                 position = position_dodge2(width = 0.7)) +
  geom_point(size = 6, position = position_dodge2(width = 0.7)) +
  geom_label(position = position_dodge(width = 2.2),
             aes(x = group, y = sum, fill = no_corp_pacs),
             color = "white", fontface = "bold") +
  coord_flip() +
  scale_color_manual(values = c("#00AFBB", "#E7B800"),
                     labels = c("Yes to Corporate PACs",
                                "No to Corporate PACs")) +
  scale_fill_manual(values = c("#00AFBB", "#E7B800"),
                    labels = c("Yes to Corporate PACs",
                                "No to Corporate PACs")) +
  scale_shape_manual(values = c("NO" = 15, "YES" = 16),
                     labels = c("Yes to Corporate PACs",
                                "No to Corporate PACs")) +
  labs(x = "", y = "Mean Contributions", color = "", shape = "") +
  guides(fill = FALSE, linetype = FALSE) +
  scale_y_continuous(labels = dollar_format(), breaks = pretty_breaks(n = 8)) +
  theme_pubclean(flip = TRUE)
ggsave("Figures/spending_candy_color.pdf", height = 3, width = 12)
```

# Other Descriptives

```{r}
summary(estimation.data$no_corp_pacs)
```


# Plot Zeros

```{r}
zeros <- 
  estimation.data %>% 
  select(business_pacs, small_indiv, biz_contribs, out_of_dist_biz_contrib) %>%
  mutate(out_of_dist_biz_contrib = ifelse(is.na(out_of_dist_biz_contrib), 0, 
                                          out_of_dist_biz_contrib)) %>%
  summarise(business_pacs = sum(business_pacs == 0),
            small_indiv = sum(small_indiv == 0),
            biz_contribs = sum(biz_contribs == 0),
            out_of_dist_biz_contrib = sum(out_of_dist_biz_contrib == 0)) %>%
  mutate_at(vars(business_pacs:out_of_dist_biz_contrib), ~ . / nrow(estimation.data)) %>%
  pivot_longer(cols = c(business_pacs, small_indiv, biz_contribs, 
                        out_of_dist_biz_contrib),
               names_to = "model", values_to = "zeros")

ggdotchart(data = zeros, 
           x = "model", 
           y = "zeros",
           sorting = "descending",
           add = "segments", 
           rotate = TRUE,
           dot.size = 6,
           label = round((zeros$zeros) * 100),
           font.label = list(color = "white", size = 9, 
                             vjust = 0.5),
           color = "black",
           ggtheme = theme_pubr()) +
  scale_y_continuous(labels = percent_format()) +
  scale_x_discrete(labels = c("Small Indiv. $", "Business Indiv. $", 
                              "Business PAC $", 
                              "Out-of-District Business Indv. $")) +
  labs(y = "Percantage of Zeros", x = "")
ggsave("Figures/zero_candy.pdf", height = 3, width = 8)
```


# Nominate Scores

```{r}
nominate.data <- read_csv("Data/Raw Data/HSall_members.csv")

nominate.data <- 
  nominate.data %>%
  filter(congress == 116) %>%
  filter(party_code == 100) %>% 
  select(state_abbrev, district_code, nominate_dim1, nominate_dim2) %>% 
  mutate(district_code = str_pad(district_code, pad = 0, side = "left", 
                                 width = 2),
         district = str_c(state_abbrev, district_code, sep = "")) %>% 
  filter(str_detect(district, "00", negate = TRUE))

nominate.data %>% 
  group_by(district) %>% 
  summarise(n = n()) %>% 
  arrange(desc(n))

estimation.data <- 
  left_join(estimation.data,
            nominate.data,
            by = "district")

nominate.data %>%
  group_by(party_code) %>%
  summarise(d1_min = min(nominate_dim1, na.rm = T),
            d1_max = max(nominate_dim1, na.rm = T),
            d2_min = min(nominate_dim2, na.rm = T),
            d2_max = max(nominate_dim2, na.rm = T))

estimation.data %>%
  group_by(no_corp_pacs) %>%
  summarise(dim1_mean = mean(nominate_dim1, na.rm = T),
            dim2_mean = mean(nominate_dim2, na.rm = T))

estimation.data %>%
  mutate(`Candidate Accepts Corporate PAC Money?` = factor(no_corp_pacs,
                                                           levels = c("NO", "YES"),
                                                           labels = c("Yes", "No"))) %>%
  ggplot(aes(x = nominate_dim1, y = nominate_dim2, 
             shape = `Candidate Accepts Corporate PAC Money?`, 
             color = `Candidate Accepts Corporate PAC Money?`)) +
  geom_point(size = 2, fill = "black") +
  annotate("text", x = 0.35, y = -0.6, label = "D1 Means", fontface = 2) +
  annotate("text", x = 0.35, y = -0.72, label = "Acceptors: -0.38") +
  annotate("text", x = 0.35, y = -0.82, label = "Rejectors: -0.30") +
  annotate("text", x = -0.90, y = 0.95, label = "D2 Means", fontface = 2) +
  annotate("text", x = -0.90, y = 0.85, label = "Acceptors: -0.02") +
  annotate("text", x = -0.90, y = 0.75, label = "Rejectors: 0.11") +
  labs(x = "DW-Nominate Dimension 1: Economic/Redistributive Issues",
       y = "DW-Nominate Dimension 2: Social/Lifestyle Issues") +
  scale_x_continuous(limits = c(-1, 0.5)) +
  scale_y_continuous(limits = c(-1, 1)) +
  scale_color_manual(values = c("grey71", "black")) +
  scale_shape_manual(values = c(20, 24)) +
  theme_pubr()
ggsave("Figures/nominate_plot.pdf", plot = last_plot(), width = 7, height = 5)

estimation.data %>%
  mutate(`Candidate Accepts Corporate PAC Money?` = factor(no_corp_pacs,
                                                           levels = c("NO", "YES"),
                                                           labels = c("Yes", "No"))) %>%
  ggplot(aes(x = nominate_dim1, y = nominate_dim2, 
             shape = `Candidate Accepts Corporate PAC Money?`, 
             color = `Candidate Accepts Corporate PAC Money?`,
             fill = `Candidate Accepts Corporate PAC Money?`)) +
  geom_point(size = 5, alpha = 0.7, 
             position = position_jitterdodge(jitter.width = 0.2, dodge.width = 0.2)) +
  geom_hline(yintercept = 0, linetype = 2) +
  geom_vline(xintercept = 0, linetype = 2) +
  annotate("text", x = 0.35, y = -0.65, label = "Mean Economic Scores", fontface = 2) +
  annotate("text", x = 0.35, y = -0.77, label = "Acceptors: -0.38") +
  annotate("text", x = 0.35, y = -0.87, label = "Rejectors: -0.30") +
  annotate("text", x = -0.85, y = 0.90, label = "Mean Social Scores", fontface = 2) +
  annotate("text", x = -0.85, y = 0.80, label = "Acceptors: -0.02") +
  annotate("text", x = -0.85, y = 0.70, label = "Rejectors: 0.11") +
  labs(x = "Economically Liberal                                  Economically Conservative",
       y = "Socially Liberal        Socially Conservative",
       caption = "Data points are 1st and 2nd Dimention DW-NOMINATE scores.") +
  scale_x_continuous(limits = c(-1, 0.5)) +
  scale_y_continuous(limits = c(-1, 1)) +
  scale_color_manual(values = c("#00AFBB", "#E7B800"),
                     labels = c("Yes", "No")) +
  scale_fill_manual(values = c("#00AFBB", "#E7B800"),
                    labels = c("Yes", "No")) +
  scale_shape_manual(values = c(21, 24),
                     labels = c("Yes", "No")) +
  theme_pubr() +
  theme(axis.line.x = element_line(arrow = grid::arrow(length = unit(0.5, "cm"), 
                                                       ends = "both",
                                                       type = "closed")),
        axis.title.x = element_text(angle = 0),
        axis.line.y = element_line(arrow = grid::arrow(length = unit(0.5, "cm"), 
                                                       ends = "both",
                                                       type = "closed")),
        axis.title.y = element_text(angle = 90),
        axis.text = element_blank(),
        axis.ticks = element_blank())
ggsave("Figures/nominate_plot_color.pdf", 
       plot = last_plot(), width = 7, height = 5)
```