---
title: "Step III: Data Analysis"
subtitle: 'PACs and Small-dollar Donations'
author:
  - name: Nicholas R. Jenkins 
    affiliation: University of California, Riverside
    affiliation_url: https://www.ucr.edu
abstract: |
  This document shows all the code used to analyze the data for this project. 
  All analyses were done with R version `r R.version$major`.`r R.version$minor` 
  "`r R.version$nickname`" and Stan version `r stan_version()` in RStudio. 
  
  Each step has been carefully documented and will replicate the results in the 
  manuscript. The code for this document can be downloaded using the button 
  in the top right corner. For any questions about this code, please contact 
  Nick Jenkins at 
  [nicholas.jenkins@email.ucr.edu](mailto:nicholas.jenkins@email.ucr.edu).
date: "`r Sys.Date()`"
output: 
  html_notebook: 
    highlight: pygments
    theme: paper
    toc: yes
    code_folding: 
    toc_float: true
bibliography: /Users/nick/Documents/Research/References/BibTeX/biblatex.bib
editor_options: 
  chunk_output_type: inline
---

# Environment Preperation

This section clears the current working environment and loads the packages used to visualize the data. I also create the function `comma()` to format any in-line output values to have thousands separators and only two digits. 

```{r setup, warning = FALSE, message = FALSE, echo = TRUE, results = "hide"}
# Clear Environment -----------------------------------------------------------
rm(list = ls())

# Load Packages ---------------------------------------------------------------
packages <- c("tidyverse", "foreign", "stargazer", "lme4", "multcomp", 
              "lmerTest", "ggmcmc", "ggridges", "rstan", "rstanarm", "brms",
              "rethinking", "patchwork", "tidybayes", "sjstats", "sjPlot",
              "bayesplot", "sjmisc", "ggpubr", "broom", "scales", "ggthemes",
              "ggrepel", "ggpubr")
lapply(packages, require, character.only = TRUE)

# Functions -------------------------------------------------------------------
# Inline Formatting
comma <- function(x) format(x, digits = 2, big.mark = ",")

# Inverse Hyperbolic Sin Transformation Function
ihs <- function(x) {
    y <- log(x + sqrt(x ^ 2 + 1))
    return(y)
}

# Set Global Chunk Options ----------------------------------------------------
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  comment = "##",
  R.options = list(width = 70)
)
```


# Import Data

This section imports the data cleaned in the "Step I: Data Cleaning" document to begin analyzing the data. 

```{r Data Import}
load("Data/Clean Data/estimation_data.RDa")
#load("E:/Project/Data/Clean Data/estimation_data.RDa")

#psych::describeBy(estimation.data, group = estimation.data$no_corp_pacs)
zeros <- 
   estimation.data %>% 
   dplyr::select(num_pac_contribs, tot_pac_money, business_pacs, ideological_pacs, 
          labor_pacs, dir_pac_cand_committee, dir_pac_party_committee,
          leadership_pacs, small_indiv, large_indiv, indiv_ideological,
          indiv_biz, indiv_labor) %>%
   summarise(num_pac = sum(num_pac_contribs == 0),
             tot_pac_money = sum(tot_pac_money == 0),
             business_pacs = sum(business_pacs == 0),
             ideological_pacs = sum(ideological_pacs == 0),
             labor_pacs = sum(labor_pacs == 0),
             dir_pac_cand_committee = sum(dir_pac_cand_committee == 0),
             dir_pac_party_committee = sum(dir_pac_party_committee == 0),
             leadership_pacs = sum(leadership_pacs == 0),
             small_indiv = sum(small_indiv == 0),
             large_indiv = sum(large_indiv == 0),
             indiv_ideological = sum(indiv_ideological == 0),
             indiv_biz = sum(indiv_biz == 0),
             indiv_labor = sum(indiv_labor == 0))
```


# Vote Models

## Model of Vote Share

### Simulating Priors

```{r}
# likelihood simulation
ggdensity(as_tibble(rgamma(1e4, shape = 5, rate = 1)), 
          x = "value",
          fill = "#00AFBB",
          palette = c("#00AFBB", "#E7B800"))

ggplot() +
  geom_density(data = as_tibble(rgamma(1e4, shape = 20, rate = 100)), 
               aes(x = value)) +
  theme_classic() +
  labs(x = "Mean and SD of Slope Parameters") +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) +
  color_palette("jco") +
  theme_light()

# prior simulation
## Intercept
ggplot() +
  geom_density(data = as_tibble(rnorm(1e4, exp(4), exp(3))),
               aes(x = value, fill = "Normal")) +
  theme_classic() +
  labs(x = "Mean and SD of Intercept") +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))

## Slope Parameters
ggplot() +
  geom_density(data = as_tibble(rnorm(1e4, exp(0), exp(4))),
               aes(x = value, fill = "normal")) +
  theme_classic() +
  labs(x = "Mean and SD of Slope Parameters") +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) +
  xlim(-200, 200)

## Scale Parameter
ggplot() +
  geom_density(data = as_tibble(rexp(1e4, 1)), 
               aes(x = value, fill = "rate=1"),
               alpha = 0.5) +
  geom_density(data = as_tibble(rexp(1e4, 2)), 
               aes(x = value, fill = "rate=2"), 
               alpha = 0.5) +
  fill_palette(palette = "jco") +
  theme_light() +
  labs(x = "Mean and SD of Scale Parameter")

## Probability Parameter
ggplot() +
  geom_density(data = as_tibble(runif(1e4, 0, 1)), 
               aes(x = value, fill = "uniform")) +
  geom_density(data = as_tibble(rbeta(1e4, 2, 2)), 
               aes(x = value, fill = "beta 2"), 
               alpha = 0.5) +
    geom_density(data = as_tibble(rbeta(1e4, 1.5, 1.5)), 
               aes(x = value, fill = "beta 1.5"), 
               alpha = 0.7) +
  fill_palette(palette = "jco") +
  theme_light() +
  labs(x = "Mean and SD of Probability Parameter")
```

### Model

```{stan output.var = "vote.model"}
data {
  int n;
  real vote_pct[n];
  real no_corp_pacs[n];
  real new_member[n];
  real pct_white[n];
  real pct_black[n];
  real pct_latino[n];
  real pct_asian[n];
  real pct_bachelors[n];
  real pct_clinton_16[n];
  real pct_dem_house_16[n];
  real log_tot_voting_age[n];
  real log_median_hh_income[n];
}

parameters {
  real a;
  real b_np;
  real b_new;
  real b_white;
  real b_black;
  real b_latino;
  real b_asian;
  real b_bach;
  real b_clint;
  real b_house;
  real b_vpop;
  real b_mhh;
  real<lower = 0> scale;
  real prob;
}

model {
  vector[n] mu;
  
  // linear model
  for (i in 1:n) {
    mu[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] + 
      b_white * pct_white[i] + b_black * pct_black[i] + 
      b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
      b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
      b_house * pct_dem_house_16[i] + b_vpop * log_tot_voting_age[i] +
      b_mhh * log_median_hh_income[i];
    mu[i] = exp(mu[i]); // inverse link function
  }
  
  // priors
  a ~ normal(4, 3);
  b_np ~ normal(0, 3.5);
  b_new ~ normal(0, 3.5);
  b_white ~ normal(0, 3.5);
  b_black ~ normal(0, 3.5);
  b_latino ~ normal(0, 3.5);
  b_asian ~ normal(0, 3.5);
  b_bach ~ normal(0, 3.5);
  b_clint ~ normal(0, 3.5);
  b_house ~ normal(0, 3.5);
  b_vpop ~ normal(0, 3.5);
  b_mhh ~ normal(0, 3.5);
  scale ~ exponential(1);
  prob ~ beta(1.5, 1.5);
  
  // likelihood
  for ( i in 1:n) {
    if (vote_pct[i] == 0)
      target += (bernoulli_lpmf(1| prob));
    else
      target += (bernoulli_lpmf(0| prob) + gamma_lpdf(vote_pct[i]| mu[i]/scale, 1/scale));
    }//i 
}

generated quantities {
  vector[n] mu;
  for (i in 1:n) {
    mu[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] + 
      b_white * pct_white[i] + b_black * pct_black[i] + 
      b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
      b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
      b_house * pct_dem_house_16[i] + b_vpop * log_tot_voting_age[i] +
      b_mhh * log_median_hh_income[i];
    mu[i] = exp(mu[i]); // inverse link function
  }
}
```

### Estimation

```{r Estimating Vote Share}
# compose data
stan.data <- 
  estimation.data %>%
  dplyr::select(vote_pct, no_corp_pacs, new_member, pct_white, pct_black, 
                pct_latino, pct_asian, pct_bachelors, pct_clinton_16,
                pct_dem_house_16, log_tot_voting_age, log_median_hh_income) %>%
  mutate(no_corp_pacs = ifelse(no_corp_pacs == "YES", 1, 0),
         new_member = ifelse(new_member == "YES", 1, 0)) %>%
  #filter(vote_pct != 0) %>%
  mutate_at(.vars = vars(pct_white:log_median_hh_income), .funs = center) %>%
  compose_data()

# model estimation ------------------------------------------------------------
vote.01 <- glm(vote_pct ~ no_corp_pacs + new_member + pct_white + pct_black + pct_latino + pct_asian + pct_bachelors + pct_clinton_16 + pct_dem_house_16 + log_median_hh_income + log_tot_voting_age,
               family = Gamma(link = "log"),
               data = as.data.frame(stan.data) %>% filter(vote_pct != 0) %>% mutate_at(.vars = vars(pct_white:log_median_hh_income), .funs = center))

voting.fit <- sampling(vote.model,
                       chains = 4,
                       cores = 4,
                       iter = 8000,
                       warmup = 3000,
                       data = stan.data)

traceplot(voting.fit, 
          inc_warmup = TRUE, 
          pars = c("a", "b_np", "b_new", "b_white", "b_black", "b_latino", 
                   "b_asian", "b_bach", "b_clint", "b_house", "b_vpop", 
                   "b_mhh", "scale"))

tidy(vote.01, conf.int = TRUE, conf.level = 0.89)
precis(voting.fit, digits = 3, prob = 0.89, depth = 2)

post <- spread_draws(voting.fit, mu[i]) %>% median_hdi()
ggplot(data = estimation.data, aes(x = vote_pct)) +
  geom_density(fill = "gray") +
  geom_density(data = post, aes(x = mu), fill = "skyblue", alpha = 0.7)
```


## Model of Turnout

### Simulating Priors

```{r}
# likelihood simulation
ggplot() +
  geom_density(data = as_tibble(rgamma(1e4, shape = 20, rate = 100)), 
               aes(x = value)) +
  theme_classic() +
  labs(x = "Mean and SD of Slope Parameters") +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) 

# prior simulation
## Intercept
ggplot() +
  geom_density(data = as_tibble(rnorm(1e4, exp(4), exp(3.5))),
               aes(x = value, fill = "Normal")) +
  theme_classic() +
  labs(x = "Mean and SD of Intercept") +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)) +
  xlim(-200, 200)

## Slope Parameters
ggplot() +
  geom_density(data = as_tibble(rnorm(1e4, exp(0), exp(4))),
               aes(x = value, fill = "normal")) +
  theme_classic() +
  labs(x = "Mean and SD of Slope Parameters") +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) +
  xlim(-200, 200)

## Scale Parameter
ggplot() +
  geom_density(data = as_tibble(rexp(1e4, 1)), 
               aes(x = value, fill = "rate=1")) +
  geom_density(data = as_tibble(rexp(1e4, 2)), 
               aes(x = value, fill = "rate=2"), 
               alpha = 0.5) +
  theme_classic() +
  labs(x = "Mean and SD of Scale Parameter")

## Probability Parameter
ggplot() +
  geom_density(data = as_tibble(runif(1e4, 0, 1)), 
               aes(x = value, fill = "uniform")) +
  geom_density(data = as_tibble(rbeta(1e4, 2, 2)), 
               aes(x = value, fill = "beta 2"), 
               alpha = 0.5) +
    geom_density(data = as_tibble(rbeta(1e4, 1.5, 1.5)), 
               aes(x = value, fill = "beta 1.5"), 
               alpha = 0.7) +
  theme_classic() +
  labs(x = "Mean and SD of Probability Parameter")
```

### Model

```{stan output.var = "turnout.model"}
data {
  int<lower = 1> n;
  real vap_turnout[n];
  real no_corp_pacs[n];
  real new_member[n];
  real pct_white[n];
  real pct_black[n];
  real pct_latino[n];
  real pct_asian[n];
  real pct_bachelors[n];
  real pct_clinton_16[n];
  real pct_dem_house_16[n];
  real log_median_hh_income[n];
  real log_tot_voting_age[n];
}

parameters {
  real<lower = 0> a;
  real b_np;
  real b_new;
  real b_white;
  real b_black;
  real b_latino;
  real b_asian;
  real b_bach;
  real b_mhh;
  real b_clint;
  real b_house;
  real b_vpop;
  real<lower = 0> scale;
  real prob;
}

model {
  // linear model
  vector[n] mu;
  for (i in 1:n) {
    mu[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] + 
      b_white * pct_white[i] + b_black * pct_black[i] + 
      b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
      b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
      b_house * pct_dem_house_16[i] + b_mhh * log_median_hh_income[i] +
      b_vpop * log_tot_voting_age[i];
    mu[i] = exp(mu[i]); // inverse link function
  }
  
  // priors
  a ~ normal(3.5, 3);
  b_np ~ normal(0, 3.5);
  b_new ~ normal(0, 3.5);
  b_white ~ normal(0, 3.5);
  b_black ~ normal(0, 3.5);
  b_latino ~ normal(0, 3.5);
  b_asian ~ normal(0, 3.5);
  b_bach ~ normal(0, 3.5);
  b_clint ~ normal(0, 3.5);
  b_house ~ normal(0, 3.5);
  b_vpop ~ normal(0, 3.5);
  b_mhh ~ normal(0, 3.5);
  prob ~ beta(1.5, 1.5);
  
  // likelihood
  for ( i in 1:n) {
    if (vap_turnout[i] == 0)
      target += (bernoulli_lpmf(1| prob));
    else
      target += (bernoulli_lpmf(0| prob) + gamma_lpdf(vap_turnout[i]| mu[i]/scale, 1/scale));
    }//i
}

generated quantities {
  vector[n] mu;
  
  for (i in 1:n) {
  mu[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] + 
      b_white * pct_white[i] + b_black * pct_black[i] + 
      b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
      b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
      b_house * pct_dem_house_16[i] + b_mhh * log_median_hh_income[i] +
      b_vpop * log_tot_voting_age[i];
  mu[i] = exp(mu[i]); // inverse link function
  }
}
```

### Estimation

```{r Estimating Turnout}
# compose data
stan.data <- 
  estimation.data %>%
  dplyr::select(vap_turnout, no_corp_pacs, new_member, pct_white, pct_black, 
                pct_latino, pct_asian, pct_bachelors, pct_clinton_16,
                pct_dem_house_16, log_tot_voting_age, log_median_hh_income) %>%
  filter(!is.na(vap_turnout)) %>%
  mutate(no_corp_pacs = ifelse(no_corp_pacs == "YES", 1, 0),
         new_member = ifelse(new_member == "YES", 1, 0)) %>%
  mutate_at(.vars = vars(pct_white:log_median_hh_income), .funs = center) %>%
  compose_data()

# model estimation ------------------------------------------------------------
turnout.1 <- glm(vap_turnout ~ no_corp_pacs + new_member + pct_white + pct_black + pct_latino + pct_asian + pct_bachelors + pct_clinton_16 + pct_dem_house_16 + log_median_hh_income + log_tot_voting_age,
                 family = Gamma(link = "log"),
                  data = as.data.frame(stan.data))

turnout.fit <- sampling(turnout.model,
                        chains = 4,
                        cores = 4,
                        iter = 8000,
                        warmup = 3000,
                        data = stan.data)

traceplot(turnout.fit, 
          inc_warmup = TRUE, 
          pars = c("a", "b_np", "b_new", "b_white", "b_black", "b_latino", 
                   "b_asian", "b_bach", "b_clint", "b_house", "b_vpop", 
                   "b_mhh", "scale"))

tidy(turnout.1, conf.int = TRUE, conf.level = 0.89)
precis(turnout.fit, prob = 0.89)

post <- spread_draws(turnout.fit, mu[i]) %>% median_hdi()
ggplot(data = estimation.data, aes(x = vap_turnout)) +
  geom_density(fill = "gray") +
  geom_density(data = post, aes(x = mu), fill = "skyblue", alpha = 0.7)
```

# PAC Models

## Model of Total PAC Contributions

### Simulating Priors

```{r}
# likelihood simulation
ggplot() +
  geom_density(data = as_tibble(rgamma(1e4, shape = 20, rate = 100)), 
               aes(x = value)) +
  theme_classic() +
  labs(x = "Mean and SD of Slope Parameters") +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) 

# prior simulation
## Intercept
ggplot() +
  geom_density(data = as_tibble(rnorm(1e4, exp(13), exp(15))),
               aes(x = value, fill = "Normal")) +
  theme_classic() +
  labs(x = "Mean and SD of Intercept") +
  scale_x_continuous(labels = dollar_format()) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))

ggplot() +
  geom_density(data = as_tibble(rnorm(1e4, logistic(0), logistic(1))),
               aes(x = value, fill = "Normal")) +
  theme_classic() +
  labs(x = "Mean and SD of Intercept") +
  scale_x_continuous(labels = dollar_format()) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))

## Slope Parameters
ggplot() +
  geom_density(data = as_tibble(rnorm(1e4, exp(0), exp(14))),
               aes(x = value, fill = "normal")) +
  theme_classic() +
  labs(x = "Mean and SD of Slope Parameters") +
  scale_x_continuous(labels = dollar_format()) 

## Scale Parameter
ggplot() +
  geom_density(data = as_tibble(rexp(1e4, 1)), 
               aes(x = value, fill = "rate=1")) +
  geom_density(data = as_tibble(rexp(1e4, 2)), 
               aes(x = value, fill = "rate=2"), 
               alpha = 0.5) +
  theme_classic() +
  labs(x = "Mean and SD of Scale Parameter")

## Probability Parameter
ggplot() +
  geom_density(data = as_tibble(runif(1e4, 0, 1)), 
               aes(x = value, fill = "uniform")) +
  geom_density(data = as_tibble(rbeta(1e4, 2, 2)), 
               aes(x = value, fill = "beta 2"), 
               alpha = 0.5) +
    geom_density(data = as_tibble(rbeta(1e4, 1.5, 1.5)), 
               aes(x = value, fill = "beta 1.5"), 
               alpha = 0.7) +
  theme_classic() +
  labs(x = "Mean and SD of Probability Parameter")
```

### Model 

```{stan output.var = "totpac.model"}
data {
  int<lower = 1> n;
  real tot_pac_money[n];
  int no_corp_pacs[n];
  int new_member[n];
  real pct_white[n];
  real pct_black[n];
  real pct_latino[n];
  real pct_asian[n];
  real pct_bachelors[n];
  real pct_clinton_16[n];
  real pct_dem_house_16[n];
  real log_median_hh_income[n];
  real log_tot_voting_age[n];
}

parameters {
  real p;
  real p_np;
  real p_new;
  real<lower = 0> a;
  real b_np;
  real b_new;
  real b_white;
  real b_black;
  real b_latino;
  real b_asian;
  real b_bach;
  real b_mhh;
  real b_clint;
  real b_house;
  real b_vpop;
  real<lower = 0> scale;
}

model {
  vector[n] prob;
  vector[n] mu;
  
  for (i in 1:n) {
    // linear model
    prob[i] = p + p_np * no_corp_pacs[i] + p_new * new_member[i]; 
    prob[i] = inv_logit(prob[i]); // inverse link function
  }
  
  for (i in 1:n) {
    // linear model
    mu[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] + 
      b_white * pct_white[i] + b_black * pct_black[i] + 
      b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
      b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
      b_house * pct_dem_house_16[i] + b_mhh * log_median_hh_income[i] +
      b_vpop * log_tot_voting_age[i];
    mu[i] = exp(mu[i]); // inverse link function
  }
  
  // priors
  
  // Binomial model
  p ~ normal(0, 1);
  p_np ~ normal(0, 1);
  p_new ~ normal(0, 1);
  
  // Gamma model
  a ~ normal(13, 15);
  b_np ~ normal(0, 14);
  b_new ~ normal(0, 14);
  b_white ~ normal(0, 14);
  b_black ~ normal(0, 14);
  b_latino ~ normal(0, 14);
  b_asian ~ normal(0, 14);
  b_bach ~ normal(0, 14);
  b_clint ~ normal(0, 14);
  b_house ~ normal(0, 14);
  b_vpop ~ normal(0, 14);
  b_mhh ~ normal(0, 14);
  scale ~ exponential(2);
  
  // likelihood
  for ( i in 1:n) {
    if (tot_pac_money[i] == 0)
      target += (bernoulli_lpmf(1 | prob[i]));
    else
      target += (bernoulli_lpmf(0 | prob[i]) + gamma_lpdf(tot_pac_money[i]| mu[i]/scale, 1/scale));
    }//i
}

generated quantities {
  vector[n] prob;
  vector[n] mu;
  
  for (i in 1:n) {
        prob[i] = p + p_np * no_corp_pacs[i] + p_new * new_member[i];
        prob[i] = inv_logit(prob[i]);
    }
    
  for (i in 1:n) {
  mu[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] + 
      b_white * pct_white[i] + b_black * pct_black[i] + 
      b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
      b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
      b_house * pct_dem_house_16[i] + b_mhh * log_median_hh_income[i] +
      b_vpop * log_tot_voting_age[i];
  mu[i] = exp(mu[i]); // inverse link function
  }
}
```

### Estimation

```{r}
# compose data
stan.data <- 
  estimation.data %>%
  dplyr::select(tot_pac_money, no_corp_pacs, new_member, pct_white, pct_black, 
                pct_latino, pct_asian, pct_bachelors, pct_clinton_16,
                pct_dem_house_16, log_tot_voting_age, log_median_hh_income) %>%
  mutate(no_corp_pacs = ifelse(no_corp_pacs == "YES", 1, 0),
         new_member = ifelse(new_member == "YES", 1, 0)) %>%
  mutate_at(.vars = vars(pct_white:log_median_hh_income), .funs = center) %>%
  compose_data()

# model estimation ------------------------------------------------------------
## Frequentist
pac.money.01 <- glm(tot_pac_money ~ no_corp_pacs + new_member + pct_white + pct_black + pct_latino + pct_asian + pct_bachelors + pct_clinton_16 + pct_dem_house_16 + log_median_hh_income + log_tot_voting_age,
                    family = Gamma(link = "log"),
                   data = as.data.frame(stan.data) %>% filter(tot_pac_money != 0) %>% mutate_at(.vars = vars(pct_white:log_median_hh_income), .funs = center))

## Bayesian
totpac.fit <- sampling(totpac.model,
                       chains = 4,
                       cores = 4,
                       iter = 10000,
                       warmup = 5000,
                       data = stan.data)

traceplot(totpac.fit, 
          inc_warmup = TRUE, 
          pars = c("a", "b_np", "b_new", "b_white", "b_black", "b_latino", 
                   "b_asian", "b_bach", "b_clint", "b_house", "b_vpop", 
                   "b_mhh", "scale"))

tidy(pac.money.01, conf.int = TRUE, conf.level = 0.89, digits = 3)
precis(totpac.fit, prob = 0.89, digits = 3)

post <- spread_draws(totpac.fit, mu[i]) %>% median_hdi()
ggplot(data = estimation.data, aes(x = tot_pac_money)) +
  geom_density(fill = "gray") +
  geom_density(data = post, aes(x = mu), fill = "skyblue", alpha = 0.7)

test <- map2stan(
  alist(tot_pac_money ~ dzagamma2(prob, mu, scale),
        log(mu) <- a + b_np * no_corp_pacs,
        logit(prob) <- p + p_np * no_corp_pacs,
        a ~ dnorm(0, 100),
        b_np ~ dnorm(0, 100),
        p ~ dnorm(0, 100),
        p_np ~ dnorm(0, 100),
        scale ~ dexp(2)),
  data = stan.data
)
```


## Model of Number of PAC Contributions

### Simulating Priors

```{r}
# likelihood simulation
ggplot() +
  geom_density(data = as_tibble(rgamma(1e4, shape = 20, rate = 100)), 
               aes(x = value)) +
  theme_classic() +
  labs(x = "Mean and SD of Slope Parameters") +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) 

# prior simulation
## Intercept
ggplot() +
  geom_density(data = as_tibble(rnorm(1e4, exp(6), exp(12))),
               aes(x = value, fill = "Normal")) +
  theme_classic() +
  labs(x = "Mean and SD of Intercept") +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))

## Slope Parameters
ggplot() +
  geom_density(data = as_tibble(rnorm(1e4, exp(0), exp(12))),
               aes(x = value, fill = "normal")) +
  theme_classic() +
  labs(x = "Mean and SD of Slope Parameters") +
  scale_x_continuous(labels = dollar_format()) 

## Scale Parameter
ggplot() +
  geom_density(data = as_tibble(rexp(1e4, 1)), 
               aes(x = value, fill = "rate=1")) +
  geom_density(data = as_tibble(rexp(1e4, 2)), 
               aes(x = value, fill = "rate=2"), 
               alpha = 0.5) +
  theme_classic() +
  labs(x = "Mean and SD of Scale Parameter")

## Probability Parameter
ggplot() +
  geom_density(data = as_tibble(runif(1e4, 0, 1)), 
               aes(x = value, fill = "uniform")) +
  geom_density(data = as_tibble(rbeta(1e4, 2, 2)), 
               aes(x = value, fill = "beta 2"), 
               alpha = 0.5) +
    geom_density(data = as_tibble(rbeta(1e4, 1.5, 1.5)), 
               aes(x = value, fill = "beta 1.5"), 
               alpha = 0.7) +
  theme_classic() +
  labs(x = "Mean and SD of Probability Parameter")
```

### Model 

```{stan output.var = "numpac.model"}
data {
  int<lower = 1> n;
  int num_pac_contribs[n];
  int no_corp_pacs[n];
  int new_member[n];
  real pct_white[n];
  real pct_black[n];
  real pct_latino[n];
  real pct_asian[n];
  real pct_bachelors[n];
  real pct_clinton_16[n];
  real pct_dem_house_16[n];
  real log_median_hh_income[n];
  real log_tot_voting_age[n];
}

parameters {
  real<lower = 0> a;
  real b_np;
  real b_new;
  real b_white;
  real b_black;
  real b_latino;
  real b_asian;
  real b_bach;
  real b_mhh;
  real b_clint;
  real b_house;
  real b_vpop;
}

model {
  // linear model
  vector[n] lambda;
  
  for (i in 1:n) {
    lambda[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] + 
      b_white * pct_white[i] + b_black * pct_black[i] + 
      b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
      b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
      b_house * pct_dem_house_16[i] + b_mhh * log_median_hh_income[i] +
      b_vpop * log_tot_voting_age[i];
    lambda[i] = exp(lambda[i]); // inverse log-link
  }
  
  // priors
  // Poisson model
  a ~ normal(6, 12);
  b_np ~ normal(0, 12);
  b_new ~ normal(0, 12);
  b_white ~ normal(0, 12);
  b_black ~ normal(0, 12);
  b_latino ~ normal(0, 12);
  b_asian ~ normal(0, 12);
  b_bach ~ normal(0, 12);
  b_clint ~ normal(0, 12);
  b_house ~ normal(0, 12);
  b_vpop ~ normal(0, 12);
  b_mhh ~ normal(0, 12);
  
  // likelihood
  for (i in 1:n) {
    num_pac_contribs[i] ~ poisson(lambda[i]);
    }
}


generated quantities {
  vector[n] lambda;
  
  for (i in 1:n) {
  lambda[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] + 
      b_white * pct_white[i] + b_black * pct_black[i] + 
      b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
      b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
      b_house * pct_dem_house_16[i] + b_mhh * log_median_hh_income[i] +
      b_vpop * log_tot_voting_age[i];
  lambda[i] = exp(lambda[i]); // inverse log-link
  }
}
```

### Estimation

```{r}
# compose data
stan.data <- 
  estimation.data %>%
  dplyr::select(num_pac_contribs, no_corp_pacs, new_member, pct_white, pct_black, 
                pct_latino, pct_asian, pct_bachelors, pct_clinton_16,
                pct_dem_house_16, log_tot_voting_age, log_median_hh_income) %>%
  mutate(no_corp_pacs = ifelse(no_corp_pacs == "YES", 1, 0),
         new_member = ifelse(new_member == "YES", 1, 0)) %>%
  drop_na() %>%
  mutate_at(.vars = vars(pct_white:log_median_hh_income), .funs = center) %>%
  compose_data()

# model estimation ------------------------------------------------------------
## Frequentist
num.pacs.01 <- glm(num_pac_contribs ~ no_corp_pacs + new_member + pct_white + pct_black + pct_latino + pct_asian + pct_bachelors + log_median_hh_income + pct_clinton_16 + pct_dem_house_16 + log_tot_voting_age,
                   family = quasipoisson(link = "log"),
                  data = as.data.frame(stan.data))

## Bayesian
numpac.fit <- sampling(numpac.model,
                       chains = 4,
                       cores = 4,
                       iter = 10000,
                       warmup = 5000,
                       data = stan.data)

traceplot(numpac.fit, 
          inc_warmup = TRUE, 
          pars = c("a", "b_np", "b_new", "b_white", "b_black", "b_latino", 
                   "b_asian", "b_bach", "b_clint", "b_house", "b_vpop", 
                   "b_mhh"))

tidy(num.pacs.01, conf.int = TRUE, conf.level = 0.89, digits = 3)
precis(numpac.fit, prob = 0.89, digits = 3)

post <- spread_draws(numpac.fit, lambda[i]) %>% median_hdi()
ggplot(data = estimation.data, aes(x = num_pac_contribs)) +
  geom_density(fill = "gray") +
  geom_density(data = post, aes(x = lambda), fill = "skyblue", alpha = 0.7)
```


## Model of Business PAC Contributions

### Simulating Priors

```{r}
# likelihood simulation
ggplot() +
  geom_density(data = as_tibble(rgamma(1e4, shape = 20, rate = 100)), 
               aes(x = value)) +
  theme_classic() +
  labs(x = "Mean and SD of Slope Parameters") +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) 

# prior simulation
## Intercept
ggplot() +
  geom_density(data = as_tibble(rnorm(1e4, exp(12.5), exp(14))),
               aes(x = value, fill = "Normal")) +
  theme_classic() +
  labs(x = "Mean and SD of Intercept") +
  scale_x_continuous(labels = dollar_format()) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))

## Slope Parameters
ggplot() +
  geom_density(data = as_tibble(rnorm(1e4, exp(0), exp(13))),
               aes(x = value, fill = "normal")) +
  theme_classic() +
  labs(x = "Mean and SD of Slope Parameters") +
  scale_x_continuous(labels = dollar_format()) 

## Scale Parameter
ggplot() +
  geom_density(data = as_tibble(rexp(1e4, 1)), 
               aes(x = value, fill = "rate=1")) +
  geom_density(data = as_tibble(rexp(1e4, 2)), 
               aes(x = value, fill = "rate=2"), 
               alpha = 0.5) +
  theme_classic() +
  labs(x = "Mean and SD of Scale Parameter")

## Probability Parameter
ggplot() +
  geom_density(data = as_tibble(runif(1e4, 0, 1)), 
               aes(x = value, fill = "uniform")) +
  geom_density(data = as_tibble(rbeta(1e4, 2, 2)), 
               aes(x = value, fill = "beta 2"), 
               alpha = 0.5) +
    geom_density(data = as_tibble(rbeta(1e4, 1.5, 1.5)), 
               aes(x = value, fill = "beta 1.5"), 
               alpha = 0.7) +
  theme_classic() +
  labs(x = "Mean and SD of Probability Parameter")
```

### Model 

```{stan output.var = "bizpac.model"}
data {
  int<lower = 1> n;
  real business_pacs[n];
  int no_corp_pacs[n];
  int new_member[n];
  real pct_white[n];
  real pct_black[n];
  real pct_latino[n];
  real pct_asian[n];
  real pct_bachelors[n];
  real pct_clinton_16[n];
  real pct_dem_house_16[n];
  real log_median_hh_income[n];
  real log_tot_voting_age[n];
}

parameters {
  real p;
  real p_np;
  real p_new;
  real<lower = 0> a;
  real b_np;
  real b_new;
  real b_white;
  real b_black;
  real b_latino;
  real b_asian;
  real b_bach;
  real b_mhh;
  real b_clint;
  real b_house;
  real b_vpop;
  real<lower = 0> scale;
}

model {
  vector[n] prob;
  vector[n] mu;
  
  for (i in 1:n) {
    // linear model
    prob[i] = p + p_np * no_corp_pacs[i] + p_new * new_member[i]; 
    prob[i] = inv_logit(prob[i]); // inverse link function
  }
  
  for (i in 1:n) {
    // linear model
    mu[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] + 
      b_white * pct_white[i] + b_black * pct_black[i] + 
      b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
      b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
      b_house * pct_dem_house_16[i] + b_mhh * log_median_hh_income[i] +
      b_vpop * log_tot_voting_age[i];
    mu[i] = exp(mu[i]); // inverse link function
  }
  
  // priors
  
  // Binomial model
  p ~ normal(0, 1);
  p_np ~ normal(0, 1);
  p_new ~ normal(0, 1);
  
  // Gamma model
  a ~ normal(12.5, 14);
  b_np ~ normal(0, 13);
  b_new ~ normal(0, 13);
  b_white ~ normal(0, 13);
  b_black ~ normal(0, 13);
  b_latino ~ normal(0, 13);
  b_asian ~ normal(0, 13);
  b_bach ~ normal(0, 13);
  b_clint ~ normal(0, 13);
  b_house ~ normal(0, 13);
  b_vpop ~ normal(0, 13);
  b_mhh ~ normal(0, 13);
  scale ~ exponential(2);
  
  // likelihood
  for ( i in 1:n) {
    if (business_pacs[i] == 0)
      target += (bernoulli_lpmf(1| prob[i]));
    else
      target += (bernoulli_lpmf(0| prob[i]) + gamma_lpdf(business_pacs[i]| mu[i]/scale, 1/scale));
    }//i
}

generated quantities {
  vector[n] prob;
  vector[n] mu;
  
  for (i in 1:n) {
    // linear model
    prob[i] = p + p_np * no_corp_pacs[i] + p_new * new_member[i]; 
    prob[i] = inv_logit(prob[i]); // inverse link function
  }
  
  for (i in 1:n) {
  mu[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] + 
      b_white * pct_white[i] + b_black * pct_black[i] + 
      b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
      b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
      b_house * pct_dem_house_16[i] + b_mhh * log_median_hh_income[i] +
      b_vpop * log_tot_voting_age[i];
  mu[i] = exp(mu[i]); // inverse link function
  }
}
```

### Estimation

```{r}
# compose data
stan.data <- 
  estimation.data %>%
  dplyr::select(business_pacs, no_corp_pacs, new_member, pct_white, pct_black, 
                pct_latino, pct_asian, pct_bachelors, pct_clinton_16,
                pct_dem_house_16, log_tot_voting_age, log_median_hh_income) %>%
  mutate(no_corp_pacs = ifelse(no_corp_pacs == "YES", 1, 0),
         new_member = ifelse(new_member == "YES", 1, 0)) %>%
  drop_na() %>%
  mutate_at(.vars = vars(pct_white:log_median_hh_income), .funs = center) %>%
  compose_data()

# model estimation ------------------------------------------------------------
## Frequentist
biz.pacs.01 <- glm(business_pacs ~ no_corp_pacs + new_member + pct_white + pct_black + pct_latino + pct_asian + pct_bachelors + pct_clinton_16 + pct_dem_house_16 + log_median_hh_income + log_tot_voting_age,
                   family = Gamma(link = "log"),
                   data = as.data.frame(stan.data) %>% filter(business_pacs != 0) %>% mutate_at(.vars = vars(pct_white:log_median_hh_income), .funs = center))

## Bayesian
bizpac.fit <- sampling(bizpac.model,
                       chains = 4,
                       cores = 4,
                       iter = 10000,
                       warmup = 5000,
                       data = stan.data)

traceplot(bizpac.fit, 
          inc_warmup = TRUE, 
          pars = c("a", "b_np", "b_new", "b_white", "b_black", "b_latino", 
                   "b_asian", "b_bach", "b_clint", "b_house", "b_vpop", 
                   "b_mhh", "scale"))

tidy(biz.pacs.01, conf.int = TRUE, conf.level = 0.89, digits = 3)
precis(bizpac.fit, prob = 0.89, digits = 3)

post <- spread_draws(bizpac.fit, mu[i]) %>% median_hdi()
ggplot(data = estimation.data, aes(x = business_pacs)) +
  geom_density(fill = "gray") +
  geom_density(data = post, aes(x = mu), fill = "skyblue", alpha = 0.7)
```


# Ideological PAC Models

## Model of Ideological PAC Contributions

### Simulating Priors

```{r}
# likelihood simulation
ggplot() +
  geom_density(data = as_tibble(rgamma(1e4, shape = 20, rate = 100)), 
               aes(x = value)) +
  theme_classic() +
  labs(x = "Mean and SD of Slope Parameters") +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) 

# prior simulation
## Intercept
ggplot() +
  geom_density(data = as_tibble(rnorm(1e4, exp(10.5), exp(13))),
               aes(x = value, fill = "Normal")) +
  theme_classic() +
  labs(x = "Mean and SD of Intercept") +
  scale_x_continuous(labels = dollar_format()) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))

## Slope Parameters
ggplot() +
  geom_density(data = as_tibble(rnorm(1e4, exp(0), exp(12))),
               aes(x = value, fill = "normal")) +
  theme_classic() +
  labs(x = "Mean and SD of Slope Parameters") +
  scale_x_continuous(labels = dollar_format()) 

## Scale Parameter
ggplot() +
  geom_density(data = as_tibble(rexp(1e4, 1)), 
               aes(x = value, fill = "rate=1")) +
  geom_density(data = as_tibble(rexp(1e4, 2)), 
               aes(x = value, fill = "rate=2"), 
               alpha = 0.5) +
  theme_classic() +
  labs(x = "Mean and SD of Scale Parameter")

## Probability Parameter
ggplot() +
  geom_density(data = as_tibble(runif(1e4, 0, 1)), 
               aes(x = value, fill = "uniform")) +
  geom_density(data = as_tibble(rbeta(1e4, 2, 2)), 
               aes(x = value, fill = "beta 2"), 
               alpha = 0.5) +
    geom_density(data = as_tibble(rbeta(1e4, 1.5, 1.5)), 
               aes(x = value, fill = "beta 1.5"), 
               alpha = 0.7) +
  theme_classic() +
  labs(x = "Mean and SD of Probability Parameter")
```

### Model 

```{stan output.var = "ideopac.model"}
data {
  int<lower = 1> n;
  real ideological_pacs[n];
  int no_corp_pacs[n];
  int new_member[n];
  real pct_white[n];
  real pct_black[n];
  real pct_latino[n];
  real pct_asian[n];
  real pct_bachelors[n];
  real pct_clinton_16[n];
  real pct_dem_house_16[n];
  real log_median_hh_income[n];
  real log_tot_voting_age[n];
}

parameters {
  real p;
  real p_np;
  real p_new;
  real<lower = 0> a;
  real b_np;
  real b_new;
  real b_white;
  real b_black;
  real b_latino;
  real b_asian;
  real b_bach;
  real b_mhh;
  real b_clint;
  real b_house;
  real b_vpop;
  real<lower = 0> scale;
}

model {
  vector[n] prob;
  vector[n] mu;
  
  for (i in 1:n) {
    // linear model
    prob[i] = p + p_np * no_corp_pacs[i] + p_new * new_member[i]; 
    prob[i] = inv_logit(prob[i]); // inverse link function
  }
  
  for (i in 1:n) {
    // linear model
    mu[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] + 
      b_white * pct_white[i] + b_black * pct_black[i] + 
      b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
      b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
      b_house * pct_dem_house_16[i] + b_mhh * log_median_hh_income[i] +
      b_vpop * log_tot_voting_age[i];
    mu[i] = exp(mu[i]); // inverse link function
  }
  
  // priors
  
  // Binomial model
  p ~ normal(0, 1);
  p_np ~ normal(0, 1);
  p_new ~ normal(0, 1);
  
  // Gamma model
  a ~ normal(10.5, 13);
  b_np ~ normal(0, 12);
  b_new ~ normal(0, 12);
  b_white ~ normal(0, 12);
  b_black ~ normal(0, 12);
  b_latino ~ normal(0, 12);
  b_asian ~ normal(0, 12);
  b_bach ~ normal(0, 12);
  b_clint ~ normal(0, 12);
  b_house ~ normal(0, 12);
  b_vpop ~ normal(0, 12);
  b_mhh ~ normal(0, 12);
  scale ~ exponential(2);
  
  // likelihood
  for ( i in 1:n) {
    if (ideological_pacs[i] == 0)
      target += (bernoulli_lpmf(1| prob[i]));
    else
      target += (bernoulli_lpmf(0| prob[i]) + gamma_lpdf(ideological_pacs[i]| mu[i]/scale, 1/scale));
    }//i
}

generated quantities {
  vector[n] prob;
  vector[n] mu;
  
  for (i in 1:n) {
    // linear model
    prob[i] = p + p_np * no_corp_pacs[i] + p_new * new_member[i]; 
    prob[i] = inv_logit(prob[i]); // inverse link function
  }
  
  for (i in 1:n) {
  mu[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] + 
      b_white * pct_white[i] + b_black * pct_black[i] + 
      b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
      b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
      b_house * pct_dem_house_16[i] + b_mhh * log_median_hh_income[i] +
      b_vpop * log_tot_voting_age[i];
  mu[i] = exp(mu[i]); // inverse link function
  }
}
```

### Estimation

```{r}
# compose data
stan.data <- 
  estimation.data %>%
  dplyr::select(ideological_pacs, no_corp_pacs, new_member, pct_white, pct_black, 
                pct_latino, pct_asian, pct_bachelors, pct_clinton_16,
                pct_dem_house_16, log_tot_voting_age, log_median_hh_income) %>%
  mutate(no_corp_pacs = ifelse(no_corp_pacs == "YES", 1, 0),
         new_member = ifelse(new_member == "YES", 1, 0)) %>%
  drop_na() %>%
  mutate_at(.vars = vars(pct_white:log_median_hh_income), .funs = center) %>%
  compose_data()

# model estimation ------------------------------------------------------------
## Frequentist
ideol.pacs.01 <- glm(ideological_pacs ~ no_corp_pacs + new_member + pct_white + pct_black + pct_latino + pct_asian + pct_bachelors + pct_clinton_16 + pct_dem_house_16 + log_median_hh_income + log_tot_voting_age,
                     family = Gamma(link = "log"),
                     data = as.data.frame(stan.data) %>% filter(ideological_pacs != 0) %>% mutate_at(.vars = vars(pct_white:log_median_hh_income), .funs = center))

## Bayesian
ideopac.fit <- sampling(ideopac.model,
                        chains = 4,
                        cores = 4,
                        iter = 10000,
                        warmup = 5000,
                        data = stan.data)

traceplot(ideopac.fit, 
          inc_warmup = TRUE, 
          pars = c("a", "b_np", "b_new", "b_white", "b_black", "b_latino", 
                   "b_asian", "b_bach", "b_clint", "b_house", "b_vpop", 
                   "b_mhh", "scale"))

tidy(ideol.pacs.01, conf.int = TRUE, conf.level = 0.89, digits = 3)
precis(ideopac.fit, prob = 0.89, digits = 3)

post <- spread_draws(ideopac.fit, mu[i]) %>% median_hdi()
ggplot(data = estimation.data, aes(x = ideological_pacs)) +
  geom_density(fill = "gray") +
  geom_density(data = post, aes(x = mu), fill = "skyblue", alpha = 0.7)
```


# Labor PAC Models

## Model of Labor PAC Contributions

### Simulating Priors

```{r}
# likelihood simulation
ggplot() +
  geom_density(data = as_tibble(rgamma(1e4, shape = 20, rate = 100)), 
               aes(x = value)) +
  theme_classic() +
  labs(x = "Mean and SD of Slope Parameters") +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) 

# prior simulation
## Intercept
ggplot() +
  geom_density(data = as_tibble(rnorm(1e4, exp(10.5), exp(13))),
               aes(x = value, fill = "Normal")) +
  theme_classic() +
  labs(x = "Mean and SD of Intercept") +
  scale_x_continuous(labels = dollar_format()) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))

## Slope Parameters
ggplot() +
  geom_density(data = as_tibble(rnorm(1e4, exp(0), exp(12))),
               aes(x = value, fill = "normal")) +
  theme_classic() +
  labs(x = "Mean and SD of Slope Parameters") +
  scale_x_continuous(labels = dollar_format()) 

## Scale Parameter
ggplot() +
  geom_density(data = as_tibble(rexp(1e4, 1)), 
               aes(x = value, fill = "rate=1")) +
  geom_density(data = as_tibble(rexp(1e4, 2)), 
               aes(x = value, fill = "rate=2"), 
               alpha = 0.5) +
  theme_classic() +
  labs(x = "Mean and SD of Scale Parameter")

## Probability Parameter
ggplot() +
  geom_density(data = as_tibble(runif(1e4, 0, 1)), 
               aes(x = value, fill = "uniform")) +
  geom_density(data = as_tibble(rbeta(1e4, 2, 2)), 
               aes(x = value, fill = "beta 2"), 
               alpha = 0.5) +
    geom_density(data = as_tibble(rbeta(1e4, 1.5, 1.5)), 
               aes(x = value, fill = "beta 1.5"), 
               alpha = 0.7) +
  theme_classic() +
  labs(x = "Mean and SD of Probability Parameter")
```

### Model 

```{stan output.var = "laborpac.model"}
data {
  int<lower = 1> n;
  real labor_pacs[n];
  int no_corp_pacs[n];
  int new_member[n];
  real pct_white[n];
  real pct_black[n];
  real pct_latino[n];
  real pct_asian[n];
  real pct_bachelors[n];
  real pct_clinton_16[n];
  real pct_dem_house_16[n];
  real log_median_hh_income[n];
  real log_tot_voting_age[n];
}

parameters {
  real p;
  real p_np;
  real p_new;
  real<lower = 0> a;
  real b_np;
  real b_new;
  real b_white;
  real b_black;
  real b_latino;
  real b_asian;
  real b_bach;
  real b_mhh;
  real b_clint;
  real b_house;
  real b_vpop;
  real<lower = 0> scale;
}

model {
  vector[n] prob;
  vector[n] mu;
  
  for (i in 1:n) {
    // linear model
    prob[i] = p + p_np * no_corp_pacs[i] + p_new * new_member[i]; 
    prob[i] = inv_logit(prob[i]); // inverse link function
  }
  
  for (i in 1:n) {
    // linear model
    mu[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] + 
      b_white * pct_white[i] + b_black * pct_black[i] + 
      b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
      b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
      b_house * pct_dem_house_16[i] + b_mhh * log_median_hh_income[i] +
      b_vpop * log_tot_voting_age[i];
    mu[i] = exp(mu[i]); // inverse link function
  }
  
  // priors
  
  // Probability model
  p ~ normal(0, 1);
  p_np ~ normal(0, 1);
  p_new ~ normal(0, 1);
  
  // Gamma model
  a ~ normal(10.5, 13);
  b_np ~ normal(0, 12);
  b_new ~ normal(0, 12);
  b_white ~ normal(0, 12);
  b_black ~ normal(0, 12);
  b_latino ~ normal(0, 12);
  b_asian ~ normal(0, 12);
  b_bach ~ normal(0, 12);
  b_clint ~ normal(0, 12);
  b_house ~ normal(0, 12);
  b_vpop ~ normal(0, 12);
  b_mhh ~ normal(0, 12);
  scale ~ exponential(2);
  
  // likelihood
  for ( i in 1:n) {
    if (labor_pacs[i] == 0)
      target += (bernoulli_lpmf(1| prob));
    else
      target += (bernoulli_lpmf(0| prob) + gamma_lpdf(labor_pacs[i]| mu[i]/scale, 1/scale));
    }//i
}

generated quantities {
  vector[n] mu;
  
  for (i in 1:n) {
  mu[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] + 
      b_white * pct_white[i] + b_black * pct_black[i] + 
      b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
      b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
      b_house * pct_dem_house_16[i] + b_mhh * log_median_hh_income[i] +
      b_vpop * log_tot_voting_age[i];
  mu[i] = exp(mu[i]); // inverse link function
  }
}
```

### Estimation

```{r}
# compose data
stan.data <- 
  estimation.data %>%
  dplyr::select(labor_pacs, no_corp_pacs, new_member, pct_white, pct_black, 
                pct_latino, pct_asian, pct_bachelors, pct_clinton_16,
                pct_dem_house_16, log_tot_voting_age, log_median_hh_income) %>%
  mutate(no_corp_pacs = ifelse(no_corp_pacs == "YES", 1, 0),
         new_member = ifelse(new_member == "YES", 1, 0)) %>%
  drop_na() %>%
  mutate_at(.vars = vars(pct_white:log_median_hh_income), .funs = center) %>%
  compose_data()

# model estimation ------------------------------------------------------------
## Frequentist
labor.pacs.01 <- glm(labor_pacs ~ no_corp_pacs + new_member + pct_white + pct_black + pct_latino + pct_asian + pct_bachelors + pct_clinton_16 + pct_dem_house_16 + log_median_hh_income + log_tot_voting_age,
                     family = Gamma(link = "log"),
                     data = as.data.frame(stan.data) %>% filter(labor_pacs != 0) %>% mutate_at(.vars = vars(pct_white:log_median_hh_income), .funs = center))

## Bayesian
laborpac.fit <- sampling(laborpac.model,
                         chains = 4,
                         cores = 4,
                         iter = 10000,
                         warmup = 5000,
                         data = stan.data)

traceplot(laborpac.fit, 
          inc_warmup = TRUE, 
          pars = c("a", "b_np", "b_new", "b_white", "b_black", "b_latino", 
                   "b_asian", "b_bach", "b_clint", "b_house", "b_vpop", 
                   "b_mhh", "scale"))

tidy(labor.pacs.01, conf.int = TRUE, conf.level = 0.89, digits = 3)
precis(laborpac.fit, prob = 0.89, digits = 3)

post <- spread_draws(laborpac.fit, mu[i]) %>% median_hdi()
ggplot(data = estimation.data, aes(x = labor_pacs)) +
  geom_density(fill = "gray") +
  geom_density(data = post, aes(x = mu), fill = "skyblue", alpha = 0.7)
```


# Party Models

## Model of Leadership PAC Contributions

### Simulating Priors

```{r}
# likelihood simulation
ggplot() +
  geom_density(data = as_tibble(rgamma(1e4, shape = 20, rate = 100)), 
               aes(x = value)) +
  theme_classic() +
  labs(x = "Mean and SD of Slope Parameters") +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) 

# prior simulation
## Intercept
ggplot() +
  geom_density(data = as_tibble(rnorm(1e4, exp(10.5), exp(13))),
               aes(x = value, fill = "Normal")) +
  theme_classic() +
  labs(x = "Mean and SD of Intercept") +
  scale_x_continuous(labels = dollar_format()) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))

## Slope Parameters
ggplot() +
  geom_density(data = as_tibble(rnorm(1e4, exp(0), exp(12))),
               aes(x = value, fill = "normal")) +
  theme_classic() +
  labs(x = "Mean and SD of Slope Parameters") +
  scale_x_continuous(labels = dollar_format()) 

## Scale Parameter
ggplot() +
  geom_density(data = as_tibble(rexp(1e4, 1)), 
               aes(x = value, fill = "rate=1")) +
  geom_density(data = as_tibble(rexp(1e4, 2)), 
               aes(x = value, fill = "rate=2"), 
               alpha = 0.5) +
  theme_classic() +
  labs(x = "Mean and SD of Scale Parameter")

## Probability Parameter
ggplot() +
  geom_density(data = as_tibble(runif(1e4, 0, 1)), 
               aes(x = value, fill = "uniform")) +
  geom_density(data = as_tibble(rbeta(1e4, 2, 2)), 
               aes(x = value, fill = "beta 2"), 
               alpha = 0.5) +
    geom_density(data = as_tibble(rbeta(1e4, 1.5, 1.5)), 
               aes(x = value, fill = "beta 1.5"), 
               alpha = 0.7) +
  theme_classic() +
  labs(x = "Mean and SD of Probability Parameter")
```

### Model 

```{stan output.var = "ldrpac.model"}
data {
  int<lower = 1> n;
  real leadership_pacs[n];
  int no_corp_pacs[n];
  int new_member[n];
  real pct_white[n];
  real pct_black[n];
  real pct_latino[n];
  real pct_asian[n];
  real pct_bachelors[n];
  real pct_clinton_16[n];
  real pct_dem_house_16[n];
  real log_median_hh_income[n];
  real log_tot_voting_age[n];
}

parameters {
  real p;
  real p_np;
  real p_new;
  real<lower = 0> a;
  real b_np;
  real b_new;
  real b_white;
  real b_black;
  real b_latino;
  real b_asian;
  real b_bach;
  real b_mhh;
  real b_clint;
  real b_house;
  real b_vpop;
  real<lower = 0> scale;
}

model {
  vector[n] prob;
  vector[n] mu;
  
  for (i in 1:n) {
    // linear model
    prob[i] = p + p_np * no_corp_pacs[i] + p_new * new_member[i]; 
    prob[i] = inv_logit(prob[i]); // inverse link function
  }
  
  for (i in 1:n) {
    // linear model
    mu[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] + 
      b_white * pct_white[i] + b_black * pct_black[i] + 
      b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
      b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
      b_house * pct_dem_house_16[i] + b_mhh * log_median_hh_income[i] +
      b_vpop * log_tot_voting_age[i];
    mu[i] = exp(mu[i]); // inverse link function
  }
  
  // priors
  
  // Probability model
  p ~ normal(0, 1);
  p_np ~ normal(0, 1);
  p_new ~ normal(0, 1);
  
  // Gamma model
  a ~ normal(10.5, 13);
  b_np ~ normal(0, 12);
  b_new ~ normal(0, 12);
  b_white ~ normal(0, 12);
  b_black ~ normal(0, 12);
  b_latino ~ normal(0, 12);
  b_asian ~ normal(0, 12);
  b_bach ~ normal(0, 12);
  b_clint ~ normal(0, 12);
  b_house ~ normal(0, 12);
  b_vpop ~ normal(0, 12);
  b_mhh ~ normal(0, 12);
  scale ~ exponential(2);
  
  // likelihood
  for ( i in 1:n) {
    if (leadership_pacs[i] == 0)
      target += (bernoulli_lpmf(1| prob[i]));
    else
      target += (bernoulli_lpmf(0| prob[i]) + gamma_lpdf(leadership_pacs[i]| mu[i]/scale, 1/scale));
    }
}

generated quantities {
  vector[n] prob;
  vector[n] mu;
  
  for (i in 1:n) {
    // linear model
    prob[i] = p + p_np * no_corp_pacs[i] + p_new * new_member[i]; 
    prob[i] = inv_logit(prob[i]); // inverse link function
  }
  
  for (i in 1:n) {
  mu[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] + 
      b_white * pct_white[i] + b_black * pct_black[i] + 
      b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
      b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
      b_house * pct_dem_house_16[i] + b_mhh * log_median_hh_income[i] +
      b_vpop * log_tot_voting_age[i];
  mu[i] = exp(mu[i]); // inverse link function
  }
}
```

### Estimation

```{r}
# compose data
stan.data <- 
  estimation.data %>%
  dplyr::select(leadership_pacs, no_corp_pacs, new_member, pct_white, pct_black, 
                pct_latino, pct_asian, pct_bachelors, pct_clinton_16,
                pct_dem_house_16, log_tot_voting_age, log_median_hh_income) %>%
  mutate(no_corp_pacs = ifelse(no_corp_pacs == "YES", 1, 0),
         new_member = ifelse(new_member == "YES", 1, 0)) %>%
  drop_na() %>%
  mutate_at(.vars = vars(pct_white:log_median_hh_income), .funs = center) %>%
  compose_data()

# model estimation ------------------------------------------------------------
## Frequentist
ldr.pacs.01 <- glm(leadership_pacs ~ no_corp_pacs + new_member + pct_white + pct_black + pct_latino + pct_asian + pct_bachelors + pct_clinton_16 + pct_dem_house_16 + log_median_hh_income + log_tot_voting_age,
                   family = Gamma(link = "log"),
                   data = as.data.frame(stan.data) %>% filter(leadership_pacs != 0) %>% mutate_at(.vars = vars(pct_white:log_median_hh_income), .funs = center))

## Bayesian
ldrpac.fit <- sampling(ldrpac.model,
                       chains = 4,
                       cores = 4,
                       iter = 10000,
                       warmup = 5000,
                       data = stan.data)

traceplot(ldrpac.fit, 
          inc_warmup = TRUE, 
          pars = c("a", "b_np", "b_new", "b_white", "b_black", "b_latino", 
                   "b_asian", "b_bach", "b_clint", "b_house", "b_vpop", 
                   "b_mhh", "scale"))

tidy(ldr.pacs.01, conf.int = TRUE, conf.level = 0.89, digits = 3)
precis(ldrpac.fit, prob = 0.89, digits = 3)

post <- spread_draws(ldrpac.fit, mu[i]) %>% median_hdi()
ggplot(data = estimation.data, aes(x = leadership_pacs)) +
  geom_density(fill = "gray") +
  geom_density(data = post, aes(x = mu), fill = "skyblue", alpha = 0.7)
```


## Model of Committee PAC Contributions

### Simulating Priors

```{r}
# likelihood simulation
ggplot() +
  geom_density(data = as_tibble(rgamma(1e4, shape = 20, rate = 100)), 
               aes(x = value)) +
  theme_classic() +
  labs(x = "Mean and SD of Slope Parameters") +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) 

# prior simulation
## Intercept
ggplot() +
  geom_density(data = as_tibble(rnorm(1e4, exp(10.5), exp(13))),
               aes(x = value, fill = "Normal")) +
  theme_classic() +
  labs(x = "Mean and SD of Intercept") +
  scale_x_continuous(labels = dollar_format()) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))

## Slope Parameters
ggplot() +
  geom_density(data = as_tibble(rnorm(1e4, exp(0), exp(12))),
               aes(x = value, fill = "normal")) +
  theme_classic() +
  labs(x = "Mean and SD of Slope Parameters") +
  scale_x_continuous(labels = dollar_format()) 

## Scale Parameter
ggplot() +
  geom_density(data = as_tibble(rexp(1e4, 1)), 
               aes(x = value, fill = "rate=1")) +
  geom_density(data = as_tibble(rexp(1e4, 2)), 
               aes(x = value, fill = "rate=2"), 
               alpha = 0.5) +
  theme_classic() +
  labs(x = "Mean and SD of Scale Parameter")

## Probability Parameter
ggplot() +
  geom_density(data = as_tibble(runif(1e4, 0, 1)), 
               aes(x = value, fill = "uniform")) +
  geom_density(data = as_tibble(rbeta(1e4, 2, 2)), 
               aes(x = value, fill = "beta 2"), 
               alpha = 0.5) +
    geom_density(data = as_tibble(rbeta(1e4, 1.5, 1.5)), 
               aes(x = value, fill = "beta 1.5"), 
               alpha = 0.7) +
  theme_classic() +
  labs(x = "Mean and SD of Probability Parameter")
```

### Model 

```{stan output.var = "cmtpac.model"}
data {
  int<lower = 1> n;
  real dir_pac_cand_committee[n];
  int no_corp_pacs[n];
  int new_member[n];
  real pct_white[n];
  real pct_black[n];
  real pct_latino[n];
  real pct_asian[n];
  real pct_bachelors[n];
  real pct_clinton_16[n];
  real pct_dem_house_16[n];
  real log_median_hh_income[n];
  real log_tot_voting_age[n];
}

parameters {
  real p;
  real p_np;
  real p_new;
  real<lower = 0> a;
  real b_np;
  real b_new;
  real b_white;
  real b_black;
  real b_latino;
  real b_asian;
  real b_bach;
  real b_mhh;
  real b_clint;
  real b_house;
  real b_vpop;
  real<lower = 0> scale;
}

model {
  vector[n] prob;
  vector[n] mu;
  
  for (i in 1:n) {
    // linear model
    prob[i] = p + p_np * no_corp_pacs[i] + p_new * new_member[i]; 
    prob[i] = inv_logit(prob[i]); // inverse link function
  }
  
  for (i in 1:n) {
    // linear model
    mu[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] + 
      b_white * pct_white[i] + b_black * pct_black[i] + 
      b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
      b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
      b_house * pct_dem_house_16[i] + b_mhh * log_median_hh_income[i] +
      b_vpop * log_tot_voting_age[i];
    mu[i] = exp(mu[i]); // inverse link function
  }
  
  // priors
  
  // Binomial model
  p ~ normal(0, 1);
  p_np ~ normal(0, 1);
  p_new ~ normal(0, 1);
  
  // Gamma model
  a ~ normal(10.5, 13);
  b_np ~ normal(0, 12);
  b_new ~ normal(0, 12);
  b_white ~ normal(0, 12);
  b_black ~ normal(0, 12);
  b_latino ~ normal(0, 12);
  b_asian ~ normal(0, 12);
  b_bach ~ normal(0, 12);
  b_clint ~ normal(0, 12);
  b_house ~ normal(0, 12);
  b_vpop ~ normal(0, 12);
  b_mhh ~ normal(0, 12);
  scale ~ exponential(2);
  
  // likelihood
  for ( i in 1:n) {
    if (dir_pac_cand_committee[i] == 0)
      target += (bernoulli_lpmf(1| prob[i]));
    else
      target += (bernoulli_lpmf(0| prob[i]) + gamma_lpdf(dir_pac_cand_committee[i]| mu[i]/scale, 1/scale));
    }//i
}

generated quantities {
  vector[n] prob;
  vector[n] mu;
  
  for (i in 1:n) {
    // linear model
    prob[i] = p + p_np * no_corp_pacs[i] + p_new * new_member[i]; 
    prob[i] = inv_logit(prob[i]); // inverse link function
  }
  
  for (i in 1:n) {
  mu[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] + 
      b_white * pct_white[i] + b_black * pct_black[i] + 
      b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
      b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
      b_house * pct_dem_house_16[i] + b_mhh * log_median_hh_income[i] +
      b_vpop * log_tot_voting_age[i];
  mu[i] = exp(mu[i]); // inverse link function
  }
}
```

### Estimation

```{r}
# compose data
stan.data <- 
  estimation.data %>%
  dplyr::select(dir_pac_cand_committee, no_corp_pacs, new_member, pct_white, pct_black, 
                pct_latino, pct_asian, pct_bachelors, pct_clinton_16,
                pct_dem_house_16, log_tot_voting_age, log_median_hh_income) %>%
  mutate(no_corp_pacs = ifelse(no_corp_pacs == "YES", 1, 0),
         new_member = ifelse(new_member == "YES", 1, 0)) %>%
  drop_na() %>%
  mutate_at(.vars = vars(pct_white:log_median_hh_income), .funs = center) %>%
  compose_data()

# model estimation ------------------------------------------------------------
## Frequentist
cmte.pacs.01 <- glm(dir_pac_cand_committee ~ no_corp_pacs + new_member + pct_white + pct_black + pct_latino + pct_asian + pct_bachelors + pct_clinton_16 + pct_dem_house_16 + log_median_hh_income + log_tot_voting_age,
                     family = Gamma(link = "log"),
                     data = as.data.frame(stan.data) %>% filter(dir_pac_cand_committee != 0) %>% mutate_at(.vars = vars(pct_white:log_median_hh_income), .funs = center))

## Bayesian
cmtpac.fit <- sampling(cmtpac.model,
                       chains = 4,
                       cores = 4,
                       iter = 10000,
                       warmup = 5000,
                       data = stan.data)

traceplot(cmtpac.fit, 
          inc_warmup = TRUE, 
          pars = c("a", "b_np", "b_new", "b_white", "b_black", "b_latino", 
                   "b_asian", "b_bach", "b_clint", "b_house", "b_vpop", 
                   "b_mhh", "scale"))

tidy(cmte.pacs.01, conf.int = TRUE, conf.level = 0.89, digits = 3)
precis(cmtpac.fit, prob = 0.89, digits = 3)

post <- spread_draws(cmtpac.fit, mu[i]) %>% median_hdi()
ggplot(data = estimation.data, aes(x = dir_pac_cand_committee)) +
  geom_density(fill = "gray") +
  geom_density(data = post, aes(x = mu), fill = "skyblue", alpha = 0.7)
```

## Model of Direct Party Contributions

### Simulating Priors

```{r}
# likelihood simulation
ggplot() +
  geom_density(data = as_tibble(rgamma(1e4, shape = 20, rate = 100)), 
               aes(x = value)) +
  theme_classic() +
  labs(x = "Mean and SD of Slope Parameters") +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) 

# prior simulation
## Intercept
ggplot() +
  geom_density(data = as_tibble(rnorm(1e4, exp(12), exp(14))),
               aes(x = value, fill = "Normal")) +
  theme_classic() +
  labs(x = "Mean and SD of Intercept") +
  scale_x_continuous(labels = dollar_format()) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))

## Slope Parameters
ggplot() +
  geom_density(data = as_tibble(rnorm(1e4, exp(0), exp(13))),
               aes(x = value, fill = "normal")) +
  theme_classic() +
  labs(x = "Mean and SD of Slope Parameters") +
  scale_x_continuous(labels = dollar_format()) 

## Scale Parameter
ggplot() +
  geom_density(data = as_tibble(rexp(1e4, 1)), 
               aes(x = value, fill = "rate=1")) +
  geom_density(data = as_tibble(rexp(1e4, 2)), 
               aes(x = value, fill = "rate=2"), 
               alpha = 0.5) +
  theme_classic() +
  labs(x = "Mean and SD of Scale Parameter")

## Probability Parameter
ggplot() +
  geom_density(data = as_tibble(runif(1e4, 0, 1)), 
               aes(x = value, fill = "uniform")) +
  geom_density(data = as_tibble(rbeta(1e4, 2, 2)), 
               aes(x = value, fill = "beta 2"), 
               alpha = 0.5) +
    geom_density(data = as_tibble(rbeta(1e4, 1.5, 1.5)), 
               aes(x = value, fill = "beta 1.5"), 
               alpha = 0.7) +
  theme_classic() +
  labs(x = "Mean and SD of Probability Parameter")
```

### Models

```{stan output.var = "prtypac.model"}
data {
  int<lower = 1> n;
  real dir_pac_party_committee[n];
  int no_corp_pacs[n];
  int new_member[n];
  real pct_white[n];
  real pct_black[n];
  real pct_latino[n];
  real pct_asian[n];
  real pct_bachelors[n];
  real pct_clinton_16[n];
  real pct_dem_house_16[n];
  real log_median_hh_income[n];
  real log_tot_voting_age[n];
}

parameters {
  real p;
  real p_np;
  real p_new;
  real<lower = 0> a;
  real b_np;
  real b_new;
  real b_white;
  real b_black;
  real b_latino;
  real b_asian;
  real b_bach;
  real b_mhh;
  real b_clint;
  real b_house;
  real b_vpop;
  real<lower = 0> scale;
}

model {
  vector[n] prob;
  vector[n] mu;
  
  for (i in 1:n) {
    // linear model
    prob[i] = p + p_np * no_corp_pacs[i] + p_new * new_member[i]; 
    prob[i] = inv_logit(prob[i]); // inverse link function
  }
  
  for (i in 1:n) {
    // linear model
    mu[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] + 
      b_white * pct_white[i] + b_black * pct_black[i] + 
      b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
      b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
      b_house * pct_dem_house_16[i] + b_mhh * log_median_hh_income[i] +
      b_vpop * log_tot_voting_age[i];
    mu[i] = exp(mu[i]); // inverse link function
  }
  
  // priors
  
  // Binomial model
  p ~ normal(0, 1);
  p_np ~ normal(0, 1);
  p_new ~ normal(0, 1);
  
  // Gamma model
  a ~ normal(12, 14);
  b_np ~ normal(0, 13);
  b_new ~ normal(0, 13);
  b_white ~ normal(0, 13);
  b_black ~ normal(0, 13);
  b_latino ~ normal(0, 13);
  b_asian ~ normal(0, 13);
  b_bach ~ normal(0, 13);
  b_clint ~ normal(0, 13);
  b_house ~ normal(0, 13);
  b_vpop ~ normal(0, 13);
  b_mhh ~ normal(0, 13);
  scale ~ exponential(2);
  
  // likelihood
  for ( i in 1:n) {
    if (dir_pac_party_committee[i] == 0)
      target += (bernoulli_lpmf(1| prob[i]));
    else
      target += (bernoulli_lpmf(0| prob[i]) + gamma_lpdf(dir_pac_party_committee[i]| mu[i]/scale, 1/scale));
    }//i
}

generated quantities {
  vector[n] prob;
  vector[n] mu;
  
  for (i in 1:n) {
    // linear model
    prob[i] = p + p_np * no_corp_pacs[i] + p_new * new_member[i]; 
    prob[i] = inv_logit(prob[i]); // inverse link function
  }
  
  for (i in 1:n) {
  mu[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] + 
      b_white * pct_white[i] + b_black * pct_black[i] + 
      b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
      b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
      b_house * pct_dem_house_16[i] + b_mhh * log_median_hh_income[i] +
      b_vpop * log_tot_voting_age[i];
  mu[i] = exp(mu[i]); // inverse link function
  }
}
```

### Estimation

```{r}
# compose data
stan.data <- 
  estimation.data %>%
  dplyr::select(dir_pac_party_committee, no_corp_pacs, new_member, pct_white, pct_black, 
                pct_latino, pct_asian, pct_bachelors, pct_clinton_16,
                pct_dem_house_16, log_tot_voting_age, log_median_hh_income) %>%
  mutate(no_corp_pacs = ifelse(no_corp_pacs == "YES", 1, 0),
         new_member = ifelse(new_member == "YES", 1, 0)) %>%
  drop_na() %>%
  mutate_at(.vars = vars(pct_white:log_median_hh_income), .funs = center) %>%
  compose_data()

# model estimation ------------------------------------------------------------
## Frequentist
party.contribs.01 <- glm(dir_pac_party_committee ~ no_corp_pacs + new_member + pct_white + pct_black + pct_latino + pct_asian + pct_bachelors + pct_clinton_16 + pct_dem_house_16 + log_median_hh_income + log_tot_voting_age,
                     family = Gamma(link = "log"),
                     data = as.data.frame(stan.data) %>% filter(dir_pac_party_committee != 0) %>% mutate_at(.vars = vars(pct_white:log_median_hh_income), .funs = center))

## Bayesian
prtypac.fit <- sampling(prtypac.model,
                        chains = 4,
                        cores = 4,
                        iter = 10000,
                        warmup = 5000,
                        data = stan.data)

traceplot(prtypac.fit, 
          inc_warmup = TRUE, 
          pars = c("a", "b_np", "b_new", "b_white", "b_black", "b_latino", 
                   "b_asian", "b_bach", "b_clint", "b_house", "b_vpop", 
                   "b_mhh", "scale"))

tidy(party.contribs.01, conf.int = TRUE, conf.level = 0.89, digits = 3)
precis(prtypac.fit, prob = 0.89, digits = 3)

post <- spread_draws(prtypac.fit, mu[i]) %>% median_hdi()
ggplot(data = estimation.data, aes(x = dir_pac_party_committee)) +
  geom_density(fill = "gray") +
  geom_density(data = post, aes(x = mu), fill = "skyblue", alpha = 0.7)
```


# Individual Models

## Model of Small Individual Contributions

### Simulating Priors

```{r}
# likelihood simulation
ggplot() +
  geom_density(data = as_tibble(rgamma(1e4, shape = 20, rate = 100)), 
               aes(x = value)) +
  theme_classic() +
  labs(x = "Mean and SD of Slope Parameters") +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) 

# prior simulation
## Intercept
ggplot() +
  geom_density(data = as_tibble(rnorm(1e4, exp(10), exp(14))),
               aes(x = value, fill = "Normal")) +
  theme_classic() +
  labs(x = "Mean and SD of Intercept") +
  scale_x_continuous(labels = dollar_format()) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))

## Slope Parameters
ggplot() +
  geom_density(data = as_tibble(rnorm(1e4, exp(0), exp(13))),
               aes(x = value, fill = "normal")) +
  theme_classic() +
  labs(x = "Mean and SD of Slope Parameters") +
  scale_x_continuous(labels = dollar_format()) 

## Scale Parameter
ggplot() +
  geom_density(data = as_tibble(rexp(1e4, 1)), 
               aes(x = value, fill = "rate=1")) +
  geom_density(data = as_tibble(rexp(1e4, 2)), 
               aes(x = value, fill = "rate=2"), 
               alpha = 0.5) +
  theme_classic() +
  labs(x = "Mean and SD of Scale Parameter")

## Probability Parameter
ggplot() +
  geom_density(data = as_tibble(runif(1e4, 0, 1)), 
               aes(x = value, fill = "uniform")) +
  geom_density(data = as_tibble(rbeta(1e4, 2, 2)), 
               aes(x = value, fill = "beta 2"), 
               alpha = 0.5) +
    geom_density(data = as_tibble(rbeta(1e4, 1.5, 1.5)), 
               aes(x = value, fill = "beta 1.5"), 
               alpha = 0.7) +
  theme_classic() +
  labs(x = "Mean and SD of Probability Parameter")
```

### Model 

```{stan output.var = "smlindv.model"}
data {
  int<lower = 1> n;
  real small_indiv[n];
  int no_corp_pacs[n];
  int new_member[n];
  real pct_white[n];
  real pct_black[n];
  real pct_latino[n];
  real pct_asian[n];
  real pct_bachelors[n];
  real pct_clinton_16[n];
  real pct_dem_house_16[n];
  real log_median_hh_income[n];
  real log_tot_voting_age[n];
}

parameters {
  real<lower = 0> a;
  real b_np;
  real b_new;
  real b_white;
  real b_black;
  real b_latino;
  real b_asian;
  real b_bach;
  real b_mhh;
  real b_clint;
  real b_house;
  real b_vpop;
  real<lower = 0> scale;
}

model {
  vector[n] mu;
  
  for (i in 1:n) {
    // linear model
    mu[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] + 
      b_white * pct_white[i] + b_black * pct_black[i] + 
      b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
      b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
      b_house * pct_dem_house_16[i] + b_mhh * log_median_hh_income[i] +
      b_vpop * log_tot_voting_age[i];
    mu[i] = exp(mu[i]); // inverse link function
  }
  
  // priors
  // Gamma model
  a ~ normal(10, 14);
  b_np ~ normal(0, 13);
  b_new ~ normal(0, 13);
  b_white ~ normal(0, 13);
  b_black ~ normal(0, 13);
  b_latino ~ normal(0, 13);
  b_asian ~ normal(0, 13);
  b_bach ~ normal(0, 13);
  b_clint ~ normal(0, 13);
  b_house ~ normal(0, 13);
  b_vpop ~ normal(0, 13);
  b_mhh ~ normal(0, 13);
  scale ~ exponential(2);
  
  // likelihood
  for ( i in 1:n) {
    small_indiv[i] ~ gamma(mu[i]/scale, 1/scale);
    }
}

generated quantities {
  vector[n] mu;
  
  for (i in 1:n) {
  mu[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] + 
      b_white * pct_white[i] + b_black * pct_black[i] + 
      b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
      b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
      b_house * pct_dem_house_16[i] + b_mhh * log_median_hh_income[i] +
      b_vpop * log_tot_voting_age[i];
  mu[i] = exp(mu[i]); // inverse link function
  }
}
```

### Estimation

```{r}
# compose data
stan.data <- 
  estimation.data %>%
  dplyr::select(small_indiv, no_corp_pacs, new_member, pct_white, pct_black, 
                pct_latino, pct_asian, pct_bachelors, pct_clinton_16,
                pct_dem_house_16, log_tot_voting_age, log_median_hh_income) %>%
  mutate(no_corp_pacs = ifelse(no_corp_pacs == "YES", 1, 0),
         new_member = ifelse(new_member == "YES", 1, 0)) %>%
  drop_na() %>%
  mutate_at(.vars = vars(pct_white:log_median_hh_income), .funs = center) %>%
  compose_data()

# model estimation ------------------------------------------------------------
## Frequentist
small.01 <- glm(small_indiv ~ no_corp_pacs + new_member + pct_white + pct_black + pct_latino + pct_asian + pct_bachelors + pct_clinton_16 + pct_dem_house_16 + log_median_hh_income + log_tot_voting_age,
                     family = Gamma(link = "log"),
                     data = as.data.frame(stan.data) %>% filter(small_indiv != 0) %>% mutate_at(.vars = vars(pct_white:log_median_hh_income), .funs = center))

## Bayesian
smlindv.fit <- sampling(smlindv.model,
                        chains = 4,
                        cores = 4,
                        iter = 10000,
                        warmup = 5000,
                        data = stan.data)

traceplot(smlindv.fit, 
          inc_warmup = TRUE, 
          pars = c("a", "b_np", "b_new", "b_white", "b_black", "b_latino", 
                   "b_asian", "b_bach", "b_clint", "b_house", "b_vpop", 
                   "b_mhh", "scale"))

tidy(small.01, conf.int = TRUE, conf.level = 0.89, digits = 3)
precis(smlindv.fit, prob = 0.89, digits = 3)

post <- spread_draws(smlindv.fit, mu[i]) %>% median_hdi()
ggplot(data = estimation.data, aes(x = small_indiv)) +
  geom_density(fill = "gray") +
  geom_density(data = post, aes(x = mu), fill = "skyblue", alpha = 0.7)
```


## Model of Large Individual Contributions

### Simulating Priors

```{r}
# likelihood simulation
ggplot() +
  geom_density(data = as_tibble(rgamma(1e4, shape = 20, rate = 100)), 
               aes(x = value)) +
  theme_classic() +
  labs(x = "Mean and SD of Slope Parameters") +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) 

# prior simulation
## Intercept
ggplot() +
  geom_density(data = as_tibble(rnorm(1e4, exp(11), exp(14))),
               aes(x = value, fill = "Normal")) +
  theme_classic() +
  labs(x = "Mean and SD of Intercept") +
  scale_x_continuous(labels = dollar_format()) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))

## Slope Parameters
ggplot() +
  geom_density(data = as_tibble(rnorm(1e4, exp(0), exp(13))),
               aes(x = value, fill = "normal")) +
  theme_classic() +
  labs(x = "Mean and SD of Slope Parameters") +
  scale_x_continuous(labels = dollar_format()) 

## Scale Parameter
ggplot() +
  geom_density(data = as_tibble(rexp(1e4, 1)), 
               aes(x = value, fill = "rate=1")) +
  geom_density(data = as_tibble(rexp(1e4, 2)), 
               aes(x = value, fill = "rate=2"), 
               alpha = 0.5) +
  theme_classic() +
  labs(x = "Mean and SD of Scale Parameter")

## Probability Parameter
ggplot() +
  geom_density(data = as_tibble(runif(1e4, 0, 1)), 
               aes(x = value, fill = "uniform")) +
  geom_density(data = as_tibble(rbeta(1e4, 2, 2)), 
               aes(x = value, fill = "beta 2"), 
               alpha = 0.5) +
    geom_density(data = as_tibble(rbeta(1e4, 1.5, 1.5)), 
               aes(x = value, fill = "beta 1.5"), 
               alpha = 0.7) +
  theme_classic() +
  labs(x = "Mean and SD of Probability Parameter")
```

### Model 

```{stan output.var = "lrgindv.model"}
data {
  int<lower = 1> n;
  real large_indiv[n];
  int no_corp_pacs[n];
  int new_member[n];
  real pct_white[n];
  real pct_black[n];
  real pct_latino[n];
  real pct_asian[n];
  real pct_bachelors[n];
  real pct_clinton_16[n];
  real pct_dem_house_16[n];
  real log_median_hh_income[n];
  real log_tot_voting_age[n];
}

parameters {
  real<lower = 0> a;
  real b_np;
  real b_new;
  real b_white;
  real b_black;
  real b_latino;
  real b_asian;
  real b_bach;
  real b_mhh;
  real b_clint;
  real b_house;
  real b_vpop;
  real<lower = 0> scale;
}

model {
  vector[n] mu;
  
  for (i in 1:n) {
    // linear model
    mu[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] + 
      b_white * pct_white[i] + b_black * pct_black[i] + 
      b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
      b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
      b_house * pct_dem_house_16[i] + b_mhh * log_median_hh_income[i] +
      b_vpop * log_tot_voting_age[i];
    mu[i] = exp(mu[i]); // inverse link function
  }
  
  // priors
  // Gamma model
  a ~ normal(11, 14);
  b_np ~ normal(0, 13);
  b_new ~ normal(0, 13);
  b_white ~ normal(0, 13);
  b_black ~ normal(0, 13);
  b_latino ~ normal(0, 13);
  b_asian ~ normal(0, 13);
  b_bach ~ normal(0, 13);
  b_clint ~ normal(0, 13);
  b_house ~ normal(0, 13);
  b_vpop ~ normal(0, 13);
  b_mhh ~ normal(0, 13);
  scale ~ exponential(2);
  
  // likelihood
  for ( i in 1:n) {
    large_indiv[i] ~ gamma(mu[i]/scale, 1/scale);
    }//i
}

generated quantities {
  vector[n] mu;
  
  for (i in 1:n) {
  mu[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] + 
      b_white * pct_white[i] + b_black * pct_black[i] + 
      b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
      b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
      b_house * pct_dem_house_16[i] + b_mhh * log_median_hh_income[i] +
      b_vpop * log_tot_voting_age[i];
  mu[i] = exp(mu[i]); // inverse link function
  }
}
```

### Estimation

```{r}
# compose data
stan.data <- 
  estimation.data %>%
  dplyr::select(large_indiv, no_corp_pacs, new_member, pct_white, pct_black, 
                pct_latino, pct_asian, pct_bachelors, pct_clinton_16,
                pct_dem_house_16, log_tot_voting_age, log_median_hh_income) %>%
  mutate(no_corp_pacs = ifelse(no_corp_pacs == "YES", 1, 0),
         new_member = ifelse(new_member == "YES", 1, 0)) %>%
  drop_na() %>%
  mutate_at(.vars = vars(pct_white:log_median_hh_income), .funs = center) %>%
  compose_data()

# model estimation ------------------------------------------------------------
## Frequentist
large.01 <- glm(large_indiv ~ no_corp_pacs + new_member + pct_white + pct_black + pct_latino + pct_asian + pct_bachelors + pct_clinton_16 + pct_dem_house_16 + log_median_hh_income + log_tot_voting_age,
                     family = Gamma(link = "log"),
                     data = as.data.frame(stan.data) %>% filter(large_indiv != 0) %>% mutate_at(.vars = vars(pct_white:log_median_hh_income), .funs = center))

## Bayesian
lrgindv.fit <- sampling(lrgindv.model,
                        chains = 4,
                        cores = 4,
                        iter = 10000,
                        warmup = 5000,
                        data = stan.data)

traceplot(lrgindv.fit, 
          inc_warmup = TRUE, 
          pars = c("a", "b_np", "b_new", "b_white", "b_black", "b_latino", 
                   "b_asian", "b_bach", "b_clint", "b_house", "b_vpop", 
                   "b_mhh", "scale"))

tidy(large.01, conf.int = TRUE, conf.level = 0.89, digits = 3)
precis(lrgindv.fit, prob = 0.89, digits = 3)

post <- spread_draws(lrgindv.fit, mu[i]) %>% median_hdi()
ggplot(data = estimation.data, aes(x = large_indiv)) +
  geom_density(fill = "gray") +
  geom_density(data = post, aes(x = mu), fill = "skyblue", alpha = 0.7)
```

## Model of Total Individual Contributions

### Simulating Priors

```{r}
# likelihood simulation
ggplot() +
  geom_density(data = as_tibble(rgamma(1e4, shape = 20, rate = 100)), 
               aes(x = value)) +
  theme_classic() +
  labs(x = "Mean and SD of Slope Parameters") +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) 

# prior simulation
## Intercept
ggplot() +
  geom_density(data = as_tibble(rnorm(1e4, exp(12), exp(14))),
               aes(x = value, fill = "Normal")) +
  theme_classic() +
  labs(x = "Mean and SD of Intercept") +
  scale_x_continuous(labels = dollar_format()) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))

## Slope Parameters
ggplot() +
  geom_density(data = as_tibble(rnorm(1e4, exp(0), exp(14))),
               aes(x = value, fill = "normal")) +
  theme_classic() +
  labs(x = "Mean and SD of Slope Parameters") +
  scale_x_continuous(labels = dollar_format()) 

## Scale Parameter
ggplot() +
  geom_density(data = as_tibble(rexp(1e4, 1)), 
               aes(x = value, fill = "rate=1")) +
  geom_density(data = as_tibble(rexp(1e4, 2)), 
               aes(x = value, fill = "rate=2"), 
               alpha = 0.5) +
  theme_classic() +
  labs(x = "Mean and SD of Scale Parameter")

## Probability Parameter
ggplot() +
  geom_density(data = as_tibble(runif(1e4, 0, 1)), 
               aes(x = value, fill = "uniform")) +
  geom_density(data = as_tibble(rbeta(1e4, 2, 2)), 
               aes(x = value, fill = "beta 2"), 
               alpha = 0.5) +
    geom_density(data = as_tibble(rbeta(1e4, 1.5, 1.5)), 
               aes(x = value, fill = "beta 1.5"), 
               alpha = 0.7) +
  theme_classic() +
  labs(x = "Mean and SD of Probability Parameter")
```

### Model 

```{stan output.var = "totindv.model"}
data {
  int<lower = 1> n;
  real net_indiv_total[n];
  int no_corp_pacs[n];
  int new_member[n];
  real pct_white[n];
  real pct_black[n];
  real pct_latino[n];
  real pct_asian[n];
  real pct_bachelors[n];
  real pct_clinton_16[n];
  real pct_dem_house_16[n];
  real log_median_hh_income[n];
  real log_tot_voting_age[n];
}

parameters {
  real<lower = 0> a;
  real b_np;
  real b_new;
  real b_white;
  real b_black;
  real b_latino;
  real b_asian;
  real b_bach;
  real b_mhh;
  real b_clint;
  real b_house;
  real b_vpop;
  real<lower = 0> scale;
}

model {
  vector[n] mu;
  
  for (i in 1:n) {
    // linear model
    mu[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] + 
      b_white * pct_white[i] + b_black * pct_black[i] + 
      b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
      b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
      b_house * pct_dem_house_16[i] + b_mhh * log_median_hh_income[i] +
      b_vpop * log_tot_voting_age[i];
    mu[i] = exp(mu[i]); // inverse link function
  }
  
  // priors
  // Gamma model
  a ~ normal(12, 14);
  b_np ~ normal(0, 14);
  b_new ~ normal(0, 14);
  b_white ~ normal(0, 14);
  b_black ~ normal(0, 14);
  b_latino ~ normal(0, 14);
  b_asian ~ normal(0, 14);
  b_bach ~ normal(0, 14);
  b_clint ~ normal(0, 14);
  b_house ~ normal(0, 14);
  b_vpop ~ normal(0, 14);
  b_mhh ~ normal(0, 14);
  scale ~ exponential(2);
  
  // likelihood
  for ( i in 1:n) {
    net_indiv_total[i] ~ gamma(mu[i]/scale, 1/scale);
    }//i
}

generated quantities {
  vector[n] mu;
  
  for (i in 1:n) {
  mu[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] + 
      b_white * pct_white[i] + b_black * pct_black[i] + 
      b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
      b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
      b_house * pct_dem_house_16[i] + b_mhh * log_median_hh_income[i] +
      b_vpop * log_tot_voting_age[i];
  mu[i] = exp(mu[i]); // inverse link function
  }
}
```

### Estimation

```{r}
# compose data
stan.data <- 
  estimation.data %>%
  dplyr::select(net_indiv_total, no_corp_pacs, new_member, pct_white, pct_black, 
                pct_latino, pct_asian, pct_bachelors, pct_clinton_16,
                pct_dem_house_16, log_tot_voting_age, log_median_hh_income) %>%
  mutate(no_corp_pacs = ifelse(no_corp_pacs == "YES", 1, 0),
         new_member = ifelse(new_member == "YES", 1, 0)) %>%
  drop_na() %>%
  mutate_at(.vars = vars(pct_white:log_median_hh_income), .funs = center) %>%
  compose_data()

# model estimation ------------------------------------------------------------
## Frequentist
indiv.tot.01 <- glm(net_indiv_total ~ no_corp_pacs + new_member + pct_white + pct_black + pct_latino + pct_asian + pct_bachelors + pct_clinton_16 + pct_dem_house_16 + log_median_hh_income + log_tot_voting_age,
                     family = Gamma(link = "log"),
                     data = as.data.frame(stan.data) %>% filter(net_indiv_total != 0) %>% mutate_at(.vars = vars(pct_white:log_median_hh_income), .funs = center))

## Bayesian
totindv.fit <- sampling(totindv.model,
                        chains = 4,
                        cores = 4,
                        iter = 10000,
                        warmup = 5000,
                        data = stan.data)

traceplot(totindv.fit, 
          inc_warmup = TRUE, 
          pars = c("a", "b_np", "b_new", "b_white", "b_black", "b_latino", 
                   "b_asian", "b_bach", "b_clint", "b_house", "b_vpop", 
                   "b_mhh", "scale"))

tidy(indiv.tot.01, conf.int = TRUE, conf.level = 0.89, digits = 3)
precis(totindv.fit, prob = 0.89, digits = 3)

post <- spread_draws(totindv.fit, mu[i]) %>% median_hdi()
ggplot(data = estimation.data, aes(x = net_indiv_total)) +
  geom_density(fill = "gray") +
  geom_density(data = post, aes(x = mu), fill = "skyblue", alpha = 0.7)
```


## Model of Individual Ideological PAC Contributions

### Simulating Priors

```{r}
# likelihood simulation
ggplot() +
  geom_density(data = as_tibble(rgamma(1e4, shape = 20, rate = 100)), 
               aes(x = value)) +
  theme_classic() +
  labs(x = "Mean and SD of Slope Parameters") +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) 

# prior simulation
## Intercept
ggplot() +
  geom_density(data = as_tibble(rnorm(1e4, exp(10.5), exp(13))),
               aes(x = value, fill = "Normal")) +
  theme_classic() +
  labs(x = "Mean and SD of Intercept") +
  scale_x_continuous(labels = dollar_format()) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))

## Slope Parameters
ggplot() +
  geom_density(data = as_tibble(rnorm(1e4, exp(0), exp(12))),
               aes(x = value, fill = "normal")) +
  theme_classic() +
  labs(x = "Mean and SD of Slope Parameters") +
  scale_x_continuous(labels = dollar_format()) 

## Scale Parameter
ggplot() +
  geom_density(data = as_tibble(rexp(1e4, 1)), 
               aes(x = value, fill = "rate=1")) +
  geom_density(data = as_tibble(rexp(1e4, 2)), 
               aes(x = value, fill = "rate=2"), 
               alpha = 0.5) +
  theme_classic() +
  labs(x = "Mean and SD of Scale Parameter")

## Probability Parameter
ggplot() +
  geom_density(data = as_tibble(runif(1e4, 0, 1)), 
               aes(x = value, fill = "uniform")) +
  geom_density(data = as_tibble(rbeta(1e4, 2, 2)), 
               aes(x = value, fill = "beta 2"), 
               alpha = 0.5) +
    geom_density(data = as_tibble(rbeta(1e4, 1.5, 1.5)), 
               aes(x = value, fill = "beta 1.5"), 
               alpha = 0.7) +
  theme_classic() +
  labs(x = "Mean and SD of Probability Parameter")
```

### Model 

```{stan output.var = "individeopac.model"}
data {
  int<lower = 1> n;
  real indiv_ideological[n];
  int no_corp_pacs[n];
  int new_member[n];
  real pct_white[n];
  real pct_black[n];
  real pct_latino[n];
  real pct_asian[n];
  real pct_bachelors[n];
  real pct_clinton_16[n];
  real pct_dem_house_16[n];
  real log_median_hh_income[n];
  real log_tot_voting_age[n];
}

parameters {
  real p;
  real p_np;
  real p_new;
  real<lower = 0> a;
  real b_np;
  real b_new;
  real b_white;
  real b_black;
  real b_latino;
  real b_asian;
  real b_bach;
  real b_mhh;
  real b_clint;
  real b_house;
  real b_vpop;
  real<lower = 0> scale;
}

model {
  vector[n] prob;
  vector[n] mu;
  
  for (i in 1:n) {
    // linear model
    prob[i] = p + p_np * no_corp_pacs[i] + p_new * new_member[i]; 
    prob[i] = inv_logit(prob[i]); // inverse link function
  }
  
  for (i in 1:n) {
    // linear model
    mu[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] + 
      b_white * pct_white[i] + b_black * pct_black[i] + 
      b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
      b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
      b_house * pct_dem_house_16[i] + b_mhh * log_median_hh_income[i] +
      b_vpop * log_tot_voting_age[i];
    mu[i] = exp(mu[i]); // inverse link function
  }
  
  // priors
  
  // Binomial model
  p ~ normal(0, 1);
  p_np ~ normal(0, 1);
  p_new ~ normal(0, 1);
  
  // Gamma model
  a ~ normal(10.5, 13);
  b_np ~ normal(0, 12);
  b_new ~ normal(0, 12);
  b_white ~ normal(0, 12);
  b_black ~ normal(0, 12);
  b_latino ~ normal(0, 12);
  b_asian ~ normal(0, 12);
  b_bach ~ normal(0, 12);
  b_clint ~ normal(0, 12);
  b_house ~ normal(0, 12);
  b_vpop ~ normal(0, 12);
  b_mhh ~ normal(0, 12);
  scale ~ exponential(2);
  
  // likelihood
  for ( i in 1:n) {
    if (indiv_ideological[i] == 0)
      target += (bernoulli_lpmf(1| prob[i]));
    else
      target += (bernoulli_lpmf(0| prob[i]) + gamma_lpdf(indiv_ideological[i]| mu[i]/scale, 1/scale));
    }//i
}

generated quantities {
  vector[n] prob;
  vector[n] mu;
  
  for (i in 1:n) {
    // linear model
    prob[i] = p + p_np * no_corp_pacs[i] + p_new * new_member[i]; 
    prob[i] = inv_logit(prob[i]); // inverse link function
  }
  
  for (i in 1:n) {
  mu[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] + 
      b_white * pct_white[i] + b_black * pct_black[i] + 
      b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
      b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
      b_house * pct_dem_house_16[i] + b_mhh * log_median_hh_income[i] +
      b_vpop * log_tot_voting_age[i];
  mu[i] = exp(mu[i]); // inverse link function
  }
}
```

### Estimation

```{r}
# compose data
stan.data <- 
  estimation.data %>%
  dplyr::select(indiv_ideological, no_corp_pacs, new_member, pct_white, pct_black, 
                pct_latino, pct_asian, pct_bachelors, pct_clinton_16,
                pct_dem_house_16, log_tot_voting_age, log_median_hh_income) %>%
  mutate(no_corp_pacs = ifelse(no_corp_pacs == "YES", 1, 0),
         new_member = ifelse(new_member == "YES", 1, 0)) %>%
  drop_na() %>%
  mutate_at(.vars = vars(pct_white:log_median_hh_income), .funs = center) %>%
  compose_data()

# model estimation ------------------------------------------------------------
## Frequentist
individeol.pacs.01 <- glm(indiv_ideological ~ no_corp_pacs + new_member + pct_white + pct_black + pct_latino + pct_asian + pct_bachelors + pct_clinton_16 + pct_dem_house_16 + log_median_hh_income + log_tot_voting_age,
                     family = Gamma(link = "log"),
                     data = as.data.frame(stan.data) %>% filter(indiv_ideological != 0) %>% mutate_at(.vars = vars(pct_white:log_median_hh_income), .funs = center))

## Bayesian
individeopac.fit <- sampling(individeopac.model,
                        chains = 4,
                        cores = 4,
                        iter = 10000,
                        warmup = 5000,
                        data = stan.data)

traceplot(ideopac.fit, 
          inc_warmup = TRUE, 
          pars = c("a", "b_np", "b_new", "b_white", "b_black", "b_latino", 
                   "b_asian", "b_bach", "b_clint", "b_house", "b_vpop", 
                   "b_mhh", "scale"))

tidy(individeol.pacs.01, conf.int = TRUE, conf.level = 0.89, digits = 3)
precis(individeopac.fit, prob = 0.89, digits = 3)

post <- spread_draws(individeopac.fit, mu[i]) %>% median_hdi()
ggplot(data = estimation.data, aes(x = indiv_ideological)) +
  geom_density(fill = "gray") +
  geom_density(data = post, aes(x = mu), fill = "skyblue", alpha = 0.7)
```

## Model of Business Individual Contributions

### Simulating Priors

```{r}
# likelihood simulation
ggplot() +
  geom_density(data = as_tibble(rgamma(1e4, shape = 20, rate = 100)), 
               aes(x = value)) +
  theme_classic() +
  labs(x = "Mean and SD of Slope Parameters") +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) 

# prior simulation
## Intercept
ggplot() +
  geom_density(data = as_tibble(rnorm(1e4, exp(11), exp(14))),
               aes(x = value, fill = "Normal")) +
  theme_classic() +
  labs(x = "Mean and SD of Intercept") +
  scale_x_continuous(labels = dollar_format()) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))

## Slope Parameters
ggplot() +
  geom_density(data = as_tibble(rnorm(1e4, exp(0), exp(13))),
               aes(x = value, fill = "normal")) +
  theme_classic() +
  labs(x = "Mean and SD of Slope Parameters") +
  scale_x_continuous(labels = dollar_format()) 

## Scale Parameter
ggplot() +
  geom_density(data = as_tibble(rexp(1e4, 1)), 
               aes(x = value, fill = "rate=1")) +
  geom_density(data = as_tibble(rexp(1e4, 2)), 
               aes(x = value, fill = "rate=2"), 
               alpha = 0.5) +
  theme_classic() +
  labs(x = "Mean and SD of Scale Parameter")

## Probability Parameter
ggplot() +
  geom_density(data = as_tibble(runif(1e4, 0, 1)), 
               aes(x = value, fill = "uniform")) +
  geom_density(data = as_tibble(rbeta(1e4, 2, 2)), 
               aes(x = value, fill = "beta 2"), 
               alpha = 0.5) +
    geom_density(data = as_tibble(rbeta(1e4, 1.5, 1.5)), 
               aes(x = value, fill = "beta 1.5"), 
               alpha = 0.7) +
  theme_classic() +
  labs(x = "Mean and SD of Probability Parameter")
```

### Model 

```{stan output.var = "bizindv.model"}
data {
  int<lower = 1> n;
  real indiv_biz[n];
  int no_corp_pacs[n];
  int new_member[n];
  real pct_white[n];
  real pct_black[n];
  real pct_latino[n];
  real pct_asian[n];
  real pct_bachelors[n];
  real pct_clinton_16[n];
  real pct_dem_house_16[n];
  real log_median_hh_income[n];
  real log_tot_voting_age[n];
}

parameters {
  real<lower = 0> a;
  real b_np;
  real b_new;
  real b_white;
  real b_black;
  real b_latino;
  real b_asian;
  real b_bach;
  real b_mhh;
  real b_clint;
  real b_house;
  real b_vpop;
  real<lower = 0> scale;
}

model {
  vector[n] mu;
  
  for (i in 1:n) {
    // linear model
    mu[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] + 
      b_white * pct_white[i] + b_black * pct_black[i] + 
      b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
      b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
      b_house * pct_dem_house_16[i] + b_mhh * log_median_hh_income[i] +
      b_vpop * log_tot_voting_age[i];
    mu[i] = exp(mu[i]); // inverse link function
  }
  
  // priors
  // Gamma model
  a ~ normal(11, 14);
  b_np ~ normal(0, 13);
  b_new ~ normal(0, 13);
  b_white ~ normal(0, 13);
  b_black ~ normal(0, 13);
  b_latino ~ normal(0, 13);
  b_asian ~ normal(0, 13);
  b_bach ~ normal(0, 13);
  b_clint ~ normal(0, 13);
  b_house ~ normal(0, 13);
  b_vpop ~ normal(0, 13);
  b_mhh ~ normal(0, 13);
  scale ~ exponential(2);
  
  // likelihood
  for ( i in 1:n) {
    indiv_biz[i] ~ gamma(mu[i]/scale, 1/scale);
    }
}

generated quantities {
  vector[n] mu;
  
  for (i in 1:n) {
  mu[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] + 
      b_white * pct_white[i] + b_black * pct_black[i] + 
      b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
      b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
      b_house * pct_dem_house_16[i] + b_mhh * log_median_hh_income[i] +
      b_vpop * log_tot_voting_age[i];
  mu[i] = exp(mu[i]); // inverse link function
  }
}
```

### Estimation

```{r}
# compose data
stan.data <- 
  estimation.data %>%
  dplyr::select(indiv_biz, no_corp_pacs, new_member, pct_white, pct_black, 
                pct_latino, pct_asian, pct_bachelors, pct_clinton_16,
                pct_dem_house_16, log_tot_voting_age, log_median_hh_income) %>%
  mutate(no_corp_pacs = ifelse(no_corp_pacs == "YES", 1, 0),
         new_member = ifelse(new_member == "YES", 1, 0)) %>%
  drop_na() %>%
  mutate_at(.vars = vars(pct_white:log_median_hh_income), .funs = center) %>%
  compose_data()

# model estimation ------------------------------------------------------------
## Frequentist
indivbiz.01 <- glm(indiv_biz ~ no_corp_pacs + new_member + pct_white + pct_black + pct_latino + pct_asian + pct_bachelors + pct_clinton_16 + pct_dem_house_16 + log_median_hh_income + log_tot_voting_age,
                   family = Gamma(link = "log"),
                   data = as.data.frame(stan.data) %>% filter(indiv_biz != 0) %>% mutate_at(.vars = vars(pct_white:log_median_hh_income), .funs = center))

## Bayesian
bizindv.fit <- sampling(bizindv.model,
                        chains = 4,
                        cores = 4,
                        iter = 10000,
                        warmup = 5000,
                        data = stan.data)

traceplot(bizindv.fit, 
          inc_warmup = TRUE, 
          pars = c("a", "b_np", "b_new", "b_white", "b_black", "b_latino", 
                   "b_asian", "b_bach", "b_clint", "b_house", "b_vpop", 
                   "b_mhh", "scale"))

tidy(indivbiz.01, conf.int = TRUE, conf.level = 0.89, digits = 3)
precis(bizindv.fit, prob = 0.89, digits = 3)

post <- spread_draws(bizindv.fit, mu[i]) %>% median_hdi()
ggplot(data = estimation.data, aes(x = indiv_biz)) +
  geom_density(fill = "gray") +
  geom_density(data = post, aes(x = mu), fill = "skyblue", alpha = 0.7)
```

## Model of Labor Individual Contributions

### Simulating Priors

```{r}
# likelihood simulation
ggplot() +
  geom_density(data = as_tibble(rgamma(1e4, shape = 20, rate = 100)), 
               aes(x = value)) +
  theme_classic() +
  labs(x = "Mean and SD of Slope Parameters") +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) 

# prior simulation
## Intercept
ggplot() +
  geom_density(data = as_tibble(rnorm(1e4, exp(11), exp(14))),
               aes(x = value, fill = "Normal")) +
  theme_classic() +
  labs(x = "Mean and SD of Intercept") +
  scale_x_continuous(labels = dollar_format()) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))

## Slope Parameters
ggplot() +
  geom_density(data = as_tibble(rnorm(1e4, exp(0), exp(13))),
               aes(x = value, fill = "normal")) +
  theme_classic() +
  labs(x = "Mean and SD of Slope Parameters") +
  scale_x_continuous(labels = dollar_format()) 

## Scale Parameter
ggplot() +
  geom_density(data = as_tibble(rexp(1e4, 1)), 
               aes(x = value, fill = "rate=1")) +
  geom_density(data = as_tibble(rexp(1e4, 2)), 
               aes(x = value, fill = "rate=2"), 
               alpha = 0.5) +
  theme_classic() +
  labs(x = "Mean and SD of Scale Parameter")

## Probability Parameter
ggplot() +
  geom_density(data = as_tibble(runif(1e4, 0, 1)), 
               aes(x = value, fill = "uniform")) +
  geom_density(data = as_tibble(rbeta(1e4, 2, 2)), 
               aes(x = value, fill = "beta 2"), 
               alpha = 0.5) +
    geom_density(data = as_tibble(rbeta(1e4, 1.5, 1.5)), 
               aes(x = value, fill = "beta 1.5"), 
               alpha = 0.7) +
  theme_classic() +
  labs(x = "Mean and SD of Probability Parameter")
```

### Model 

```{stan output.var = "laborindv.model"}
data {
  int<lower = 1> n;
  real indiv_labor[n];
  int no_corp_pacs[n];
  int new_member[n];
  real pct_white[n];
  real pct_black[n];
  real pct_latino[n];
  real pct_asian[n];
  real pct_bachelors[n];
  real pct_clinton_16[n];
  real pct_dem_house_16[n];
  real log_median_hh_income[n];
  real log_tot_voting_age[n];
}

parameters {
  real p;
  real p_np;
  real p_new;
  real<lower = 0> a;
  real b_np;
  real b_new;
  real b_white;
  real b_black;
  real b_latino;
  real b_asian;
  real b_bach;
  real b_mhh;
  real b_clint;
  real b_house;
  real b_vpop;
  real<lower = 0> scale;
}

model {
  vector[n] prob;
  vector[n] mu;
  
  for (i in 1:n) {
    // linear model
    prob[i] = p + p_np * no_corp_pacs[i] + p_new * new_member[i]; 
    prob[i] = inv_logit(prob[i]); // inverse link function
  }
  
  for (i in 1:n) {
    // linear model
    mu[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] + 
      b_white * pct_white[i] + b_black * pct_black[i] + 
      b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
      b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
      b_house * pct_dem_house_16[i] + b_mhh * log_median_hh_income[i] +
      b_vpop * log_tot_voting_age[i];
    mu[i] = exp(mu[i]); // inverse link function
  }
  
  // priors
  
  // Binomial model
  p ~ normal(0, 1);
  p_np ~ normal(0, 1);
  p_new ~ normal(0, 1);
  
  // Gamma model
  a ~ normal(11, 14);
  b_np ~ normal(0, 13);
  b_new ~ normal(0, 13);
  b_white ~ normal(0, 13);
  b_black ~ normal(0, 13);
  b_latino ~ normal(0, 13);
  b_asian ~ normal(0, 13);
  b_bach ~ normal(0, 13);
  b_clint ~ normal(0, 13);
  b_house ~ normal(0, 13);
  b_vpop ~ normal(0, 13);
  b_mhh ~ normal(0, 13);
  scale ~ exponential(2);
  
  // likelihood
  for ( i in 1:n) {
    if (indiv_labor[i] == 0)
      target += (bernoulli_lpmf(1| prob[i]));
    else
      target += (bernoulli_lpmf(0| prob[i]) + gamma_lpdf(indiv_labor[i]| mu[i]/scale, 1/scale));
    }//i
}

generated quantities {
  vector[n] prob;
  vector[n] mu;
  
  for (i in 1:n) {
    // linear model
    prob[i] = p + p_np * no_corp_pacs[i] + p_new * new_member[i]; 
    prob[i] = inv_logit(prob[i]); // inverse link function
  }
  
  for (i in 1:n) {
  mu[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] + 
      b_white * pct_white[i] + b_black * pct_black[i] + 
      b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
      b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
      b_house * pct_dem_house_16[i] + b_mhh * log_median_hh_income[i] +
      b_vpop * log_tot_voting_age[i];
  mu[i] = exp(mu[i]); // inverse link function
  }
}
```

### Estimation

```{r}
# compose data
stan.data <- 
  estimation.data %>%
  dplyr::select(indiv_labor, no_corp_pacs, new_member, pct_white, pct_black, 
                pct_latino, pct_asian, pct_bachelors, pct_clinton_16,
                pct_dem_house_16, log_tot_voting_age, log_median_hh_income) %>%
  mutate(no_corp_pacs = ifelse(no_corp_pacs == "YES", 1, 0),
         new_member = ifelse(new_member == "YES", 1, 0)) %>%
  drop_na() %>%
  mutate_at(.vars = vars(pct_white:log_median_hh_income), .funs = center) %>%
  compose_data()

# model estimation ------------------------------------------------------------
## Frequentist
indivlabor.01 <- glm(indiv_labor ~ no_corp_pacs + new_member + pct_white + pct_black + pct_latino + pct_asian + pct_bachelors + pct_clinton_16 + pct_dem_house_16 + log_median_hh_income + log_tot_voting_age,
                     family = Gamma(link = "log"),
                     data = as.data.frame(stan.data) %>% filter(indiv_labor != 0) %>% mutate_at(.vars = vars(pct_white:log_median_hh_income), .funs = center))

## Bayesian
laborindv.fit <- sampling(laborindv.model,
                          chains = 4,
                          cores = 2,
                          iter = 10000,
                          warmup = 5000,
                          data = stan.data)

traceplot(laborindv.fit, 
          inc_warmup = TRUE, 
          pars = c("a", "b_np", "b_new", "b_white", "b_black", "b_latino", 
                   "b_asian", "b_bach", "b_clint", "b_house", "b_vpop", 
                   "b_mhh", "scale"))

tidy(indivlabor.01, conf.int = TRUE, conf.level = 0.89, digits = 3)
precis(laborindv.fit, prob = 0.89, digits = 3)

post <- spread_draws(laborindv.fit, mu[i]) %>% median_hdi()
ggplot(data = estimation.data, aes(x = indiv_labor)) +
  geom_density(fill = "gray") +
  geom_density(data = post, aes(x = mu), fill = "skyblue", alpha = 0.7)
```


# Results Summary

## Load Models and Extract Posteriors 

```{r}
# Save models
## Business
# save(totpac.fit, file = "E:/Project/totpac_fit.Rda")
# save(numpac.fit, file = "E:/Project/numpac_fit.Rda")
# save(bizpac.fit, file = "E:/Project/bizpac_fit.Rda")
# 
# ## Ideological
# save(ideopac.fit, file = "E:/Project/ideopac_fit.Rda")
# 
# ## Labor
# save(laborpac.fit, file = "E:/Project/labor_fit.Rda")
# 
# ## Party
# save(ldrpac.fit, file = "E:/Project/ldrpac_fit.Rda")
# save(cmtpac.fit, file = "E:/Project/cmtpac_fit.Rda")
# save(prtypac.fit, file = "E:/Project/prtypac_fit.Rda")
# 
# ## Individual
# save(smlindv.fit, file = "E:/Project/smlindv_fit.Rda")
# save(lrgindv.fit, file = "E:/Project/lrgindv_fit.Rda")
# save(totindv.fit, file = "E:/Project/totindiv_fit.Rda")
# save(individeopac.fit, file = "E:/Project/individeopac_fit.Rda")
# save(bizindv.fit, file = "E:/Project/bizindv_fit.Rda")
# save(laborindv.fit, file = "E:/Project/laborindv_fit.Rda")
# 
# ## Voting
# save(voting.fit, file = "E:/Project/voting_fit.Rda")
# save(turnout.fit, file = "E:/Project/turnout_fit.Rda")

# load models
## Business
load(file = "Models/totpac_fit.Rda")
load(file = "Models/numpac_fit.Rda")
load(file = "Models/bizpac_fit.Rda")

## Ideological
load(file = "Models/ideopac_fit.Rda")

## Labor
load(file = "Models/labor_fit.Rda")

## Party
load(file = "Models/ldrpac_fit.Rda")
load(file = "Models/cmtpac_fit.Rda")
load(file = "Models/prtypac_fit.Rda")

## Individual
load(file = "Models/smlindv_fit.Rda")
load(file = "Models/lrgindv_fit.Rda")
load(file = "Models/totindiv_fit.Rda")
load(file = "Models/individeopac_fit.Rda")
load(file = "Models/bizindv_fit.Rda")
load(file = "Models/laborindv_fit.Rda")

## Voting
load(file = "Models/voting_fit.Rda")
load(file = "Models/turnout_fit.Rda")
```

## PAC Results

```{r}
# PAC results -----------------------------------------------------------------
# extract posterior predictions
pac.models <- c(totpac.fit, numpac.fit, bizpac.fit, ideopac.fit, laborpac.fit) 
names(pac.models) <- c("totpac.fit", "numpac.fit", "bizpac.fit", "ideopac.fit", 
                       "laborpac.fit")
post.pac <- 
  pac.models %>%
  map_dfr(~ spread_draws(., a, b_np, p, p_np), .id = "model")

## main effects
post.pac %>%
  mutate(b_np = exp(b_np) - 1) %>%
  ggplot() +
  stat_halfeyeh(aes(y = fct_reorder(model, b_np), x = b_np), 
                .width = c(0.89, 0.5), 
                point_interval = median_hdi,
                fill = "#0072B2",
                color = "black",
                alpha = 0.9) +
  geom_vline(aes(xintercept = 0), linetype = "dashed", color = "grey55") +
  scale_x_continuous(labels = percent_format(),
                     breaks = pretty_breaks(n = 6)) +
  scale_y_discrete(labels = c("Business PAC $", "Total PAC $", "Labor PAC $",
                              "# of PACs", "Ideological PAC $")) +
  labs(x = "% Change in Contributions (exp(Coefficient Estimate) - 1)", 
       y = "Outcome Variable") +
  theme_pubr() +
ggsave("Figures/Results/pac_coef.pdf", height = 4, width = 7) 

## predicted values
pred.pac <- 
  post.pac %>%
  group_by(model) %>%
  mutate(no_pac_pred = exp(a + b_np),
         pac_pred = exp(a)) %>%
  dplyr::select(model, no_pac_pred, pac_pred) %>%
  gather(no_pac_pred, pac_pred, 
         key = "type", value = "prediction") %>%
  group_by(model, type) %>%
  median_hdi(.width = 0.89)

ggplot(data = pred.pac, 
       aes(x = fct_reorder(model, prediction),
           y = prediction, 
           ymin = .lower, 
           ymax = .upper,
           color = type,
           label = comma(round(prediction, digits = 0)))) +
  geom_point(position = position_dodge(.1), size = 2) +
  geom_errorbar(position = position_dodge(), width = 0.1) +
  geom_text_repel(mapping = aes(group = type),
                  position = position_dodge(0.1),
                  alpha = 0.9,
                  segment.size = 0,
                  segment.alpha = 0,
                  show.legend = FALSE) +
  scale_y_continuous(labels = dollar_format(),
                     breaks = pretty_breaks(n = 6)) +
  scale_x_discrete(labels = c("# of PACs", "Ideological PAC $", 
                              "Labor PAC $", "Business PAC $", "Total PAC $")) +
  labs(x = "Outcome Variable", 
       y = "Predicted Contributions", 
       color = "Prediction:") +
  scale_color_manual(values = c("#0072B2", "#E69F00"),
                     labels = c("No to Corporate PACs", 
                                "Yes to Corporate PACs")) +
  theme_pubr() + 
ggsave("Figures/Results/pac_preds.pdf", height = 4, width = 8)

# Binomial model
post.pac %>%
  filter(model != "numpac.fit") %>%
  mutate(p_np = logistic(p_np),
         p = logistic(p)) %>%
  ggplot() +
  stat_halfeyeh(aes(y = fct_reorder(model, p_np), x = p_np), 
                .width = c(0.89, 0.5), 
                point_interval = median_hdi,
                fill = "#0072B2",
                color = "black",
                alpha = 0.9) +
  geom_vline(aes(xintercept = 0.5), linetype = "dashed", color = "grey55") +
  scale_x_continuous(labels = percent_format(),
                     breaks = pretty_breaks(n = 6)) +
  scale_y_discrete(labels = c("Ideological PAC $", "Labor PAC $", "Total PAC $",
                              "Business PAC $")) +
  labs(x = "Predicted Probability of Receiving Contributions", 
       y = "Outcome Variable") +
  theme_pubr() +
ggsave("Figures/Results/pac_probs.pdf", height = 4, width = 8)

# Tables ----------------------------------------------------------------------
sink(file = "Tables/pac_results.tex")
mcmcReg(list(numpac.fit, totpac.fit, bizpac.fit, ideopac.fit, laborpac.fit),
        pointest = "median",
        ci = 0.89,
        hpdi = TRUE,
        format = "latex",
        pars = c("a", "b_np", "b_new", "b_white", "b_black", "b_latino", 
                 "b_asian", "b_mhh", "b_clint", "b_house", "b_vpop", "scale",
                 "p", "p_np", "p_new"))
sink()
```

## Party Results

```{r}
# extract posterior predictions
party.models <- c(ldrpac.fit, cmtpac.fit, prtypac.fit)
names(party.models) <- c("ldrpac.fit", "cmtpac.fit", "prtypac.fit")

post.prty <- 
  party.models %>%
  map_dfr(~ spread_draws(., a, b_np, p, p_np), .id = "model")

## main effects
post.prty %>%
  mutate(b_np = exp(b_np) - 1) %>%
  ggplot() +
  stat_halfeyeh(aes(y = fct_reorder(model, b_np), x = b_np), 
                .width = c(0.89, 0.5), 
                point_interval = median_hdi,
                fill = "#0072B2",
                color = "black",
                alpha = 0.9) +
  geom_vline(aes(xintercept = 0), linetype = "dashed", color = "grey55") +
  scale_x_continuous(labels = percent_format(),
                     breaks = pretty_breaks(n = 5)) +
  scale_y_discrete(labels = c("Leadership PAC $", "Party Committee $", 
                              "Candidate Committee $")) +
  labs(x = "% Change in Contributions (exp(Coefficient Estimate) - 1)", 
       y = "Outcome Variable") +
  theme_pubr() +
ggsave("Figures/Results/party_coef.pdf", height = 4, width = 7)

## predicted values
pred.party <- 
  post.prty %>%
  group_by(model) %>%
  mutate(no_pac_pred = exp(a + b_np),
         pac_pred = exp(a)) %>%
  dplyr::select(model, no_pac_pred, pac_pred) %>%
  gather(no_pac_pred, pac_pred, 
         key = "type", value = "prediction") %>%
  group_by(model, type) %>%
  median_hdi(.width = 0.89)

## all predictions
ggplot(data = pred.party, 
       aes(x = fct_reorder(model, prediction),
           y = prediction, 
           ymin = .lower, 
           ymax = .upper,
           color = type,
           label = comma(round(prediction, digits = 0)))) +
  geom_point(position = position_dodge(.1), size = 2) +
  geom_errorbar(position = position_dodge(), width = 0.1) +
  geom_text_repel(mapping = aes(group = type),
                  position = position_dodge(0.1),
                  alpha = 0.9,
                  segment.size = 0,
                  segment.alpha = 0,
                  show.legend = FALSE) +
  scale_y_continuous(labels = dollar_format(),
                     breaks = pretty_breaks(n = 6)) +
  scale_x_discrete(labels = c("Party Committee $", "Candidate Committees $", 
                              "Leadership PAC $")) +
  labs(x = "Outcome Variable", 
       y = "Predicted Contributions", 
       color = "Prediction:") +
  scale_color_manual(values = c("#0072B2", "#E69F00"),
                     labels = c("No to Corporate PACs", 
                                "Yes to Corporate PACs")) +
  theme_pubr() +
ggsave("Figures/Results/party_preds.pdf", height = 4, width = 8)

# Binomial model
post.prty %>%
  mutate(p_np = logistic(p_np),
         p = logistic(p)) %>%
  ggplot() +
  stat_halfeyeh(aes(y = fct_reorder(model, p_np), x = p_np), 
                .width = c(0.89, 0.5), 
                point_interval = median_hdi,
                fill = "#0072B2",
                color = "black",
                alpha = 0.9) +
  geom_vline(aes(xintercept = 0.5), linetype = "dashed", color = "grey55") +
  scale_x_continuous(labels = percent_format(),
                     breaks = pretty_breaks(n = 6)) +
  scale_y_discrete(labels = c("Party Committee $", "Leadership PAC $", 
                              "Candidate Committees $")) +
  labs(x = "Predicted Probability of Receiving Contributions", 
       y = "Outcome Variable") +
  theme_pubr() +
ggsave("Figures/Results/prty_probs.pdf", height = 4, width = 8)

# Tables ----------------------------------------------------------------------
sink(file = "Tables/prty_results.tex")
mcmcReg(list(ldrpac.fit, cmtpac.fit, prtypac.fit),
        pointest = "median",
        ci = 0.89,
        hpdi = TRUE,
        format = "latex",
        pars = c("a", "b_np", "b_new", "b_white", "b_black", "b_latino", 
                 "b_asian", "b_mhh", "b_clint", "b_house", "b_vpop", "scale",
                 "p", "p_np", "p_new"))
sink()
```

## Individual Results 

```{r}
# extract posterior predictions
## individual contributions
indiv.models <- c(bizindv.fit, smlindv.fit, lrgindv.fit, totindv.fit, 
                  individeopac.fit)
names(indiv.models) <- c("bizindv.fit", "smlindv.fit", "lrgindv.fit", 
                         "totindv.fit", "individeopac.fit")
post.indiv <- 
  indiv.models %>%
  map_dfr(~ spread_draws(., a, b_np, p, p_np), .id = "model")

## main effects
post.indiv %>%
  mutate(b_np = exp(b_np) - 1) %>%
  ggplot() +
  stat_halfeyeh(aes(y = fct_reorder(model, b_np), x = b_np), 
                .width = c(0.89, 0.5), 
                point_interval = median_hdi,
                fill = "#0072B2",
                color = "black",
                alpha = 0.9) +
  geom_vline(aes(xintercept = 0), linetype = "dashed", color = "grey55") +
  scale_x_continuous(labels = percent_format(),
                     breaks = pretty_breaks(n = 6)) +
  scale_y_discrete(labels = c("Indiv. Business $", 
                              "Large Individual $",
                              "Indiv. Ideological $",
                              "Total Individual $",
                              "Small Individual $")) +
  labs(x = "% Change in Contributions (exp(Coefficient Estimate) - 1)", 
       y = "Outcome Variable") +
  theme_pubr() +
ggsave("Figures/Results/indv_coef.pdf", height = 4, width = 7)

## predicted values
pred.indv <- 
  post.indiv %>%
  group_by(model) %>%
  mutate(no_pac_pred = exp(a + b_np),
         pac_pred = exp(a)) %>%
  dplyr::select(model, no_pac_pred, pac_pred) %>%
  gather(no_pac_pred, pac_pred, 
         key = "type", value = "prediction") %>%
  group_by(model, type) %>%
  median_hdi(.width = 0.89)

ggplot(data = pred.indv, 
       aes(x = fct_reorder(model, prediction),
           y = prediction, 
           ymin = .lower, 
           ymax = .upper,
           color = type,
           label = comma(round(prediction, digits = 0)))) +
  geom_point(position = position_dodge(.1), size = 2) +
  geom_errorbar(position = position_dodge(), width = 0.1) +
  geom_text_repel(mapping = aes(group = type),
                  position = position_dodge(0.1),
                  alpha = 0.9,
                  segment.size = 0,
                  segment.alpha = 0,
                  show.legend = FALSE) +
  scale_y_continuous(labels = dollar_format(),
                     breaks = pretty_breaks(n = 6)) +
  scale_x_discrete(labels = c("Indiv. Ideological $","Small Individual $", 
                              "Indiv. Business $", "Large Individual $", 
                              "Total Individual $")) +
  labs(x = "Outcome Variable", 
       y = "Predicted Contributions", 
       color = "Prediction:") +
  scale_color_manual(values = c("#0072B2", "#E69F00"),
                     labels = c("No to Corporate PACs", 
                                "Yes to Corporate PACs")) +
  theme_pubr() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)) +
ggsave("Figures/Results/indv_preds.pdf", height = 4, width = 8)

# Binomial model
post.indiv %>%
  mutate(p_np = logistic(p_np),
         p = logistic(p)) %>%
  ggplot() +
  stat_halfeyeh(aes(y = fct_reorder(model, p_np), x = p_np), 
                .width = c(0.89, 0.5), 
                point_interval = median_hdi,
                fill = "#0072B2",
                color = "black",
                alpha = 0.9) +
  geom_vline(aes(xintercept = 0.5), linetype = "dashed", color = "grey55") +
  scale_x_continuous(labels = percent_format(),
                     breaks = pretty_breaks(n = 6)) +
  scale_y_discrete(labels = c("Party Committee $", "Leadership PAC $", 
                              "Candidate Committees $")) +
  labs(x = "Predicted Probability of Receiving Contributions", 
       y = "Outcome Variable") +
  theme_pubr() +
ggsave("Figures/Results/prty_probs.pdf", height = 4, width = 8)

# Tables ----------------------------------------------------------------------
sink(file = "Tables/indiv_results.tex")
mcmcReg(list(smlindv.fit, lrgindv.fit, totindv.fit, individeopac.fit,
                  bizindv.fit),
        pointest = "median",
        ci = 0.89,
        hpdi = TRUE,
        format = "latex",
        pars = c("a", "b_np", "b_new", "b_white", "b_black", "b_latino", 
                 "b_asian", "b_mhh", "b_clint", "b_house", "b_vpop", "scale",
                 "prob"))
sink()
```

## Vote Results

```{r}
# extract posterior predictions
## voting
vote.models <- c(voting.fit, turnout.fit)
names(vote.models) <- c("voting.fit", "turnout.fit")
post.vote <- 
  vote.models %>%
  map_dfr(~ spread_draws(., a, b_np), .id = "model")

## Coefficient plot
post.vote %>%
  mutate(b_np = exp(b_np) - 1) %>%
  ggplot() +
  stat_halfeyeh(aes(y = fct_reorder(model, b_np), x = b_np), 
                .width = c(0.89, 0.5), 
                point_interval = median_hdi,
                fill = "#2D6CC0",
                color = "black",
                alpha = 0.9) +
  geom_vline(aes(xintercept = 0), linetype = "dashed") +
  scale_x_continuous(labels = percent_format(),
                     breaks = pretty_breaks(n = 6)) +
  scale_y_discrete(labels = c("V.A.P. Turnout", "Vote Share")) +
  labs(x = "% Change in Contributions (exp(Coefficient Estimate) - 1)", 
       y = "Outcome Variable") +
  theme_pubr()
ggsave("Figures/Results/vote_coef.pdf", height = 4, width = 7)

## predicted values
pred.vote <- 
  post.vote %>%
  group_by(model) %>%
  mutate(no_pac_pred = exp(a + b_np),
         pac_pred = exp(a)) %>%
  dplyr::select(model, no_pac_pred, pac_pred) %>%
  gather(no_pac_pred, pac_pred, 
         key = "type", value = "prediction") %>%
  group_by(model, type) %>%
  median_hdi(.width = 0.89)

## all predictions
ggplot(data = pred.vote, 
       aes(x = fct_reorder(model, prediction),
           y = prediction, 
           ymin = .lower, 
           ymax = .upper,
           color = type,
           label = comma(round(prediction, digits = 2)))) +
  geom_point(position = position_dodge(.1), size = 2) +
  geom_errorbar(position = position_dodge(), width = 0.1) +
  geom_text_repel(mapping = aes(group = type),
                  position = position_dodge(0.1),
                  alpha = 0.9,
                  segment.size = 0,
                  segment.alpha = 0,
                  show.legend = FALSE) +
  scale_y_continuous(breaks = pretty_breaks(n = 6)) +
  scale_x_discrete(labels = c("V.A.P. Turnout", "Vote Share")) +
  labs(x = "Outcome Variable", 
       y = "Predicted %", 
       color = "Prediction:") +
  scale_color_manual(values = c("#2D6CC0", "#F1AB00"),
                     labels = c("No to Corporate PACs", 
                                "Yes to Corporate PACs")) +
  theme_pubr()
ggsave("Figures/Results/vote_preds.pdf", height = 4, width = 6)

# Tables ----------------------------------------------------------------------
sink(file = "Tables/vote_results.tex")
mcmcReg(list(voting.fit, turnout.fit),
        pointest = "median",
        ci = 0.89,
        hpdi = TRUE,
        format = "latex",
        pars = c("a", "b_np", "b_new", "b_white", "b_black", "b_latino", 
                 "b_asian", "b_mhh", "b_clint", "b_house", "b_vpop", "scale",
                 "prob"))
sink()
```