---
title: "Step III: Data Analysis"
subtitle: 'Project.title'
author:
  - Nicholas R. Jenkins^[University of California, Riverside]
abstract: |
  This document shows all the code used to analyze the data for this project. 
  All analyses were done using RStudio running **R** version 
  `r R.version$major`.`r R.version$minor` "`r R.version$nickname`". 
  
  Each step has been carefully documented and will replicate the results in the 
  manuscript. The code for this document can be downloaded using the button 
  in the top right corner. For any questions about this code, please contact 
  Nick Jenkins at 
  [nicholas.jenkins@email.ucr.edu](mailto:nicholas.jenkins@email.ucr.edu).
output:
  html_notebook: 
    highlight: monochrome
    theme: simplex
    toc: yes
    code_folding: 
  html_document:
    highlight: monochrome
    theme: simplex
    toc: yes
    code_folding:
  pdf_document:
    toc: yes
  github_document:
    toc: yes
date: "`r format(Sys.time(), '%B %d, %Y')`"
bibliography: /Users/nick/Documents/Research/Articles/biblatex.bib
editor_options: 
  chunk_output_type: console
---

# Environment Preperation

This section clears the current working environment and loads the packages used to visualize the data. I also create the function `comma()` to format any in-line output values to have thousands separators and only two digits. 

```{r setup, warning = FALSE, message = FALSE, echo = FALSE}
# Clear Environment -----------------------------------------------------------
rm(list = ls())

# Load Packages ---------------------------------------------------------------
packages <- c("tidyverse", "foreign", "stargazer", "lme4", "multcomp", 
              "lmerTest", "ggmcmc", "ggridges", "rstan", "rstanarm", "brms",
              "rethinking", "patchwork", "tidybayes", "sjstats", "sjPlot",
              "bayesplot", "sjmisc", "ggpubr", "broom", "scales")
lapply(packages, require, character.only = TRUE)

# Functions -------------------------------------------------------------------
# Inline Formatting
comma <- function(x) format(x, digits = 2, big.mark = ",")

# Inverse Hyperbolic Sin Transformation Function
ihs <- function(x) {
    y <- log(x + sqrt(x ^ 2 + 1))
    return(y)
}
```


# Import Data

This section imports the data cleaned in the "Step I: Data Cleaning" document to begin analyzing the data. 

```{r Data Import}
load("Data/Clean Data/estimation_data.RDa")

psych::describeBy(estimation.data, group = estimation.data$no_corp_pacs)
```


# Vote Models

## Model of Vote Share

### Simulating Priors

```{r}
# likelihood simulation
ggplot() +
  geom_density(data = as_tibble(rgamma(1e4, shape = 20, rate = 100)), 
               aes(x = value)) +
  theme_classic() +
  labs(x = "Mean and SD of Slope Parameters") +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) 

# prior simulation
## Intercept
ggplot() +
  geom_density(data = as_tibble(rnorm(1e4, exp(4), exp(3.5))),
               aes(x = value, fill = "Normal")) +
  theme_classic() +
  labs(x = "Mean and SD of Intercept") +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)) +
  xlim(-200, 200)

## Slope Parameters
ggplot() +
  geom_density(data = as_tibble(rnorm(1e4, exp(0), exp(4))),
               aes(x = value, fill = "normal")) +
  theme_classic() +
  labs(x = "Mean and SD of Slope Parameters") +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) +
  xlim(-200, 200)

## Scale Parameter
ggplot() +
  geom_density(data = as_tibble(rexp(1e4, 1)), 
               aes(x = value, fill = "rate=1")) +
  geom_density(data = as_tibble(rexp(1e4, 2)), 
               aes(x = value, fill = "rate=2"), 
               alpha = 0.5) +
  theme_classic() +
  labs(x = "Mean and SD of Scale Parameter")

## Probability Parameter
ggplot() +
  geom_density(data = as_tibble(runif(1e4, 0, 1)), 
               aes(x = value, fill = "uniform")) +
  geom_density(data = as_tibble(rbeta(1e4, 2, 2)), 
               aes(x = value, fill = "beta 2"), 
               alpha = 0.5) +
    geom_density(data = as_tibble(rbeta(1e4, 1.5, 1.5)), 
               aes(x = value, fill = "beta 1.5"), 
               alpha = 0.7) +
  theme_classic() +
  labs(x = "Mean and SD of Probability Parameter")
```

### Model

```{stan output.var = "vote.model"}
data {
  int n;
  real vote_pct[n];
  real no_corp_pacs[n];
  real new_member[n];
  real pct_white[n];
  real pct_black[n];
  real pct_latino[n];
  real pct_asian[n];
  real pct_bachelors[n];
  real pct_clinton_16[n];
  real pct_dem_house_16[n];
  real log_tot_voting_age[n];
  real log_median_hh_income[n];
}

parameters {
  real a;
  real b_np;
  real b_new;
  real b_white;
  real b_black;
  real b_latino;
  real b_asian;
  real b_bach;
  real b_clint;
  real b_house;
  real b_vpop;
  real b_mhh;
  real<lower = 0> scale;
  real prob;
}

model {
  vector[n] mu;
  
  // linear model
  for (i in 1:n) {
    mu[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] + 
      b_white * pct_white[i] + b_black * pct_black[i] + 
      b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
      b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
      b_house * pct_dem_house_16[i] + b_vpop * log_tot_voting_age[i] +
      b_mhh * log_median_hh_income[i];
    mu[i] = exp(mu[i]); // inverse link function
  }
  
  // priors
  a ~ normal(4, 3);
  b_np ~ normal(0, 3.5);
  b_new ~ normal(0, 3.5);
  b_white ~ normal(0, 3.5);
  b_black ~ normal(0, 3.5);
  b_latino ~ normal(0, 3.5);
  b_asian ~ normal(0, 3.5);
  b_bach ~ normal(0, 3.5);
  b_clint ~ normal(0, 3.5);
  b_house ~ normal(0, 3.5);
  b_vpop ~ normal(0, 3.5);
  b_mhh ~ normal(0, 3.5);
  scale ~ exponential(1);
  prob ~ beta(1.5, 1.5);
  
  // likelihood
  for ( i in 1:n) {
    if (vote_pct[i] == 0)
      target += (bernoulli_lpmf(1| prob));
    else
      target += (bernoulli_lpmf(0| prob) + gamma_lpdf(vote_pct[i]| mu[i]/scale, 1/scale));
    }//i 
}

generated quantities {
  vector[n] mu;
  for (i in 1:n) {
    mu[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] + 
      b_white * pct_white[i] + b_black * pct_black[i] + 
      b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
      b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
      b_house * pct_dem_house_16[i] + b_vpop * log_tot_voting_age[i] +
      b_mhh * log_median_hh_income[i];
    mu[i] = exp(mu[i]); // inverse link function
  }
}
```

### Estimation

```{r Estimating Vote Share}
# compose data
stan.data <- 
  estimation.data %>%
  dplyr::select(vote_pct, no_corp_pacs, new_member, pct_white, pct_black, 
                pct_latino, pct_asian, pct_bachelors, pct_clinton_16,
                pct_dem_house_16, log_tot_voting_age, log_median_hh_income) %>%
  mutate(no_corp_pacs = ifelse(no_corp_pacs == "YES", 1, 0),
         new_member = ifelse(new_member == "YES", 1, 0)) %>%
  #filter(vote_pct != 0) %>%
  mutate_at(.vars = vars(pct_white:log_median_hh_income), .funs = center) %>%
  compose_data()

# model estimation ------------------------------------------------------------
vote.01 <- glm(vote_pct ~ no_corp_pacs + new_member + pct_white + pct_black + pct_latino + pct_asian + pct_bachelors + pct_clinton_16 + pct_dem_house_16 + log_median_hh_income + log_tot_voting_age,
               family = Gamma(link = "log"),
               data = as.data.frame(stan.data) %>% filter(vote_pct != 0) %>% mutate_at(.vars = vars(pct_white:log_median_hh_income), .funs = center))

voting.fit <- sampling(vote.model,
                       chains = 4,
                       cores = 4,
                       iter = 8000,
                       warmup = 3000,
                       data = stan.data)

traceplot(voting.fit, 
          inc_warmup = TRUE, 
          pars = c("a", "b_np", "b_new", "b_white", "b_black", "b_latino", 
                   "b_asian", "b_bach", "b_clint", "b_house", "b_vpop", 
                   "b_mhh", "scale"))

tidy(vote.01, conf.int = TRUE, conf.level = 0.89)
precis(voting.fit, digits = 3, prob = 0.89, depth = 2)

post <- spread_draws(voting.fit, mu[i]) %>% median_hdi()
ggplot(data = estimation.data, aes(x = vote_pct)) +
  geom_density(fill = "gray") +
  geom_density(data = post, aes(x = mu), fill = "skyblue", alpha = 0.7)
```


## Model of Turnout

### Simulating Priors

```{r}
# likelihood simulation
ggplot() +
  geom_density(data = as_tibble(rgamma(1e4, shape = 20, rate = 100)), 
               aes(x = value)) +
  theme_classic() +
  labs(x = "Mean and SD of Slope Parameters") +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) 

# prior simulation
## Intercept
ggplot() +
  geom_density(data = as_tibble(rnorm(1e4, exp(4), exp(3.5))),
               aes(x = value, fill = "Normal")) +
  theme_classic() +
  labs(x = "Mean and SD of Intercept") +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)) +
  xlim(-200, 200)

## Slope Parameters
ggplot() +
  geom_density(data = as_tibble(rnorm(1e4, exp(0), exp(4))),
               aes(x = value, fill = "normal")) +
  theme_classic() +
  labs(x = "Mean and SD of Slope Parameters") +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) +
  xlim(-200, 200)

## Scale Parameter
ggplot() +
  geom_density(data = as_tibble(rexp(1e4, 1)), 
               aes(x = value, fill = "rate=1")) +
  geom_density(data = as_tibble(rexp(1e4, 2)), 
               aes(x = value, fill = "rate=2"), 
               alpha = 0.5) +
  theme_classic() +
  labs(x = "Mean and SD of Scale Parameter")

## Probability Parameter
ggplot() +
  geom_density(data = as_tibble(runif(1e4, 0, 1)), 
               aes(x = value, fill = "uniform")) +
  geom_density(data = as_tibble(rbeta(1e4, 2, 2)), 
               aes(x = value, fill = "beta 2"), 
               alpha = 0.5) +
    geom_density(data = as_tibble(rbeta(1e4, 1.5, 1.5)), 
               aes(x = value, fill = "beta 1.5"), 
               alpha = 0.7) +
  theme_classic() +
  labs(x = "Mean and SD of Probability Parameter")
```

### Model

```{stan output.var = "turnout.model"}
data {
  int<lower = 1> n;
  real vap_turnout[n];
  real no_corp_pacs[n];
  real new_member[n];
  real pct_white[n];
  real pct_black[n];
  real pct_latino[n];
  real pct_asian[n];
  real pct_bachelors[n];
  real pct_clinton_16[n];
  real pct_dem_house_16[n];
  real log_median_hh_income[n];
  real log_tot_voting_age[n];
}

parameters {
  real<lower = 0> a;
  real b_np;
  real b_new;
  real b_white;
  real b_black;
  real b_latino;
  real b_asian;
  real b_bach;
  real b_mhh;
  real b_clint;
  real b_house;
  real b_vpop;
  real<lower = 0> scale;
  real prob;
}

model {
  // linear model
  vector[n] mu;
  for (i in 1:n) {
    mu[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] + 
      b_white * pct_white[i] + b_black * pct_black[i] + 
      b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
      b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
      b_house * pct_dem_house_16[i] + b_mhh * log_median_hh_income[i] +
      b_vpop * log_tot_voting_age[i];
    mu[i] = exp(mu[i]); // inverse link function
  }
  
  // priors
  a ~ normal(3.5, 3);
  b_np ~ normal(0, 3.5);
  b_new ~ normal(0, 3.5);
  b_white ~ normal(0, 3.5);
  b_black ~ normal(0, 3.5);
  b_latino ~ normal(0, 3.5);
  b_asian ~ normal(0, 3.5);
  b_bach ~ normal(0, 3.5);
  b_clint ~ normal(0, 3.5);
  b_house ~ normal(0, 3.5);
  b_vpop ~ normal(0, 3.5);
  b_mhh ~ normal(0, 3.5);
  prob ~ beta(1.5, 1.5);
  
  // likelihood
  for ( i in 1:n) {
    if (vap_turnout[i] == 0)
      target += (bernoulli_lpmf(1| prob));
    else
      target += (bernoulli_lpmf(0| prob) + gamma_lpdf(vap_turnout[i]| mu[i]/scale, 1/scale));
    }//i
}

generated quantities {
  vector[n] mu;
  
  for (i in 1:n) {
  mu[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] + 
      b_white * pct_white[i] + b_black * pct_black[i] + 
      b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
      b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
      b_house * pct_dem_house_16[i] + b_mhh * log_median_hh_income[i] +
      b_vpop * log_tot_voting_age[i];
  mu[i] = exp(mu[i]); // inverse link function
  }
}
```

### Estimation

```{r Estimating Turnout}
# compose data
stan.data <- 
  estimation.data %>%
  dplyr::select(vap_turnout, no_corp_pacs, new_member, pct_white, pct_black, 
                pct_latino, pct_asian, pct_bachelors, pct_clinton_16,
                pct_dem_house_16, log_tot_voting_age, log_median_hh_income) %>%
  filter(!is.na(vap_turnout)) %>%
  mutate(no_corp_pacs = ifelse(no_corp_pacs == "YES", 1, 0),
         new_member = ifelse(new_member == "YES", 1, 0)) %>%
  mutate_at(.vars = vars(pct_white:log_median_hh_income), .funs = center) %>%
  compose_data()

# model estimation ------------------------------------------------------------
turnout.1 <- glm(vap_turnout ~ no_corp_pacs + new_member + pct_white + pct_black + pct_latino + pct_asian + pct_bachelors + pct_clinton_16 + pct_dem_house_16 + log_median_hh_income + log_tot_voting_age,
                 family = Gamma(link = "log"),
                  data = as.data.frame(stan.data))

turnout.fit <- sampling(turnout.model,
                        chains = 4,
                        cores = 4,
                        iter = 8000,
                        warmup = 3000,
                        data = stan.data)

traceplot(turnout.fit, 
          inc_warmup = TRUE, 
          pars = c("a", "b_np", "b_new", "b_white", "b_black", "b_latino", 
                   "b_asian", "b_bach", "b_clint", "b_house", "b_vpop", 
                   "b_mhh", "scale"))

tidy(turnout.1, conf.int = TRUE, conf.level = 0.89)
precis(turnout.fit, prob = 0.89)

post <- spread_draws(turnout.fit, mu[i]) %>% median_hdi()
ggplot(data = estimation.data, aes(x = vap_turnout)) +
  geom_density(fill = "gray") +
  geom_density(data = post, aes(x = mu), fill = "skyblue", alpha = 0.7)
```

# PAC Models

## Model of Total PAC Contributions

### Simulating Priors

```{r}
# likelihood simulation
ggplot() +
  geom_density(data = as_tibble(rgamma(1e4, shape = 20, rate = 100)), 
               aes(x = value)) +
  theme_classic() +
  labs(x = "Mean and SD of Slope Parameters") +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) 

# prior simulation
## Intercept
ggplot() +
  geom_density(data = as_tibble(rnorm(1e4, exp(13), exp(15))),
               aes(x = value, fill = "Normal")) +
  theme_classic() +
  labs(x = "Mean and SD of Intercept") +
  scale_x_continuous(labels = dollar_format()) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))

## Slope Parameters
ggplot() +
  geom_density(data = as_tibble(rnorm(1e4, exp(0), exp(14))),
               aes(x = value, fill = "normal")) +
  theme_classic() +
  labs(x = "Mean and SD of Slope Parameters") +
  scale_x_continuous(labels = dollar_format()) 

## Scale Parameter
ggplot() +
  geom_density(data = as_tibble(rexp(1e4, 1)), 
               aes(x = value, fill = "rate=1")) +
  geom_density(data = as_tibble(rexp(1e4, 2)), 
               aes(x = value, fill = "rate=2"), 
               alpha = 0.5) +
  theme_classic() +
  labs(x = "Mean and SD of Scale Parameter")

## Probability Parameter
ggplot() +
  geom_density(data = as_tibble(runif(1e4, 0, 1)), 
               aes(x = value, fill = "uniform")) +
  geom_density(data = as_tibble(rbeta(1e4, 2, 2)), 
               aes(x = value, fill = "beta 2"), 
               alpha = 0.5) +
    geom_density(data = as_tibble(rbeta(1e4, 1.5, 1.5)), 
               aes(x = value, fill = "beta 1.5"), 
               alpha = 0.7) +
  theme_classic() +
  labs(x = "Mean and SD of Probability Parameter")
```

### Model 

```{stan output.var = "totpac.model"}
data {
  int<lower = 1> n;
  real tot_pac_money[n];
  int no_corp_pacs[n];
  int new_member[n];
  real pct_white[n];
  real pct_black[n];
  real pct_latino[n];
  real pct_asian[n];
  real pct_bachelors[n];
  real pct_clinton_16[n];
  real pct_dem_house_16[n];
  real log_median_hh_income[n];
  real log_tot_voting_age[n];
}

parameters {
  real<lower = 0> a;
  real b_np;
  real b_new;
  real b_white;
  real b_black;
  real b_latino;
  real b_asian;
  real b_bach;
  real b_mhh;
  real b_clint;
  real b_house;
  real b_vpop;
  real<lower = 0> scale;
  real prob;
}

model {
  // linear model
  vector[n] mu;
  for (i in 1:n) {
    mu[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] + 
      b_white * pct_white[i] + b_black * pct_black[i] + 
      b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
      b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
      b_house * pct_dem_house_16[i] + b_mhh * log_median_hh_income[i] +
      b_vpop * log_tot_voting_age[i];
    mu[i] = exp(mu[i]); // inverse link function
  }
  
  // priors
  a ~ normal(13, 15);
  b_np ~ normal(0, 14);
  b_new ~ normal(0, 14);
  b_white ~ normal(0, 14);
  b_black ~ normal(0, 14);
  b_latino ~ normal(0, 14);
  b_asian ~ normal(0, 14);
  b_bach ~ normal(0, 14);
  b_clint ~ normal(0, 14);
  b_house ~ normal(0, 14);
  b_vpop ~ normal(0, 14);
  b_mhh ~ normal(0, 14);
  scale ~ exponential(2);
  prob ~ beta(1.5, 1.5);
  
  // likelihood
  for ( i in 1:n) {
    if (tot_pac_money[i] == 0)
      target += (bernoulli_lpmf(1| prob));
    else
      target += (bernoulli_lpmf(0| prob) + gamma_lpdf(tot_pac_money[i]| mu[i]/scale, 1/scale));
    }//i
}

generated quantities {
  vector[n] mu;
  
  for (i in 1:n) {
  mu[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] + 
      b_white * pct_white[i] + b_black * pct_black[i] + 
      b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
      b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
      b_house * pct_dem_house_16[i] + b_mhh * log_median_hh_income[i] +
      b_vpop * log_tot_voting_age[i];
  mu[i] = exp(mu[i]); // inverse link function
  }
}
```

### Estimation

```{r}
# compose data
stan.data <- 
  estimation.data %>%
  dplyr::select(tot_pac_money, no_corp_pacs, new_member, pct_white, pct_black, 
                pct_latino, pct_asian, pct_bachelors, pct_clinton_16,
                pct_dem_house_16, log_tot_voting_age, log_median_hh_income) %>%
  mutate(no_corp_pacs = ifelse(no_corp_pacs == "YES", 1, 0),
         new_member = ifelse(new_member == "YES", 1, 0)) %>%
  mutate_at(.vars = vars(pct_white:log_median_hh_income), .funs = center) %>%
  compose_data()

# model estimation ------------------------------------------------------------
## Frequentist
pac.money.01 <- glm(tot_pac_money ~ no_corp_pacs + new_member + pct_white + pct_black + pct_latino + pct_asian + pct_bachelors + pct_clinton_16 + pct_dem_house_16 + log_median_hh_income + log_tot_voting_age,
                    family = Gamma(link = "log"),
                   data = as.data.frame(stan.data) %>% filter(tot_pac_money != 0) %>% mutate_at(.vars = vars(pct_white:log_median_hh_income), .funs = center))

## Bayesian
totpac.fit <- sampling(totpac.model,
                       chains = 4,
                       cores = 4,
                       iter = 8000,
                       warmup = 4000,
                       data = stan.data)

traceplot(totpac.fit, 
          inc_warmup = TRUE, 
          pars = c("a", "b_np", "b_new", "b_white", "b_black", "b_latino", 
                   "b_asian", "b_bach", "b_clint", "b_house", "b_vpop", 
                   "b_mhh", "scale"))

tidy(pac.money.01, conf.int = TRUE, conf.level = 0.89, digits = 3)
precis(totpac.fit, prob = 0.89, digits = 3)

post <- spread_draws(totpac.fit, mu[i]) %>% median_hdi()
ggplot(data = estimation.data, aes(x = tot_pac_money)) +
  geom_density(fill = "gray") +
  geom_density(data = post, aes(x = mu), fill = "skyblue", alpha = 0.7)
```


## Model of Number of PAC Contributions

### Simulating Priors

```{r}
# likelihood simulation
ggplot() +
  geom_density(data = as_tibble(rgamma(1e4, shape = 20, rate = 100)), 
               aes(x = value)) +
  theme_classic() +
  labs(x = "Mean and SD of Slope Parameters") +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) 

# prior simulation
## Intercept
ggplot() +
  geom_density(data = as_tibble(rnorm(1e4, exp(6), exp(12))),
               aes(x = value, fill = "Normal")) +
  theme_classic() +
  labs(x = "Mean and SD of Intercept") +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))

## Slope Parameters
ggplot() +
  geom_density(data = as_tibble(rnorm(1e4, exp(0), exp(12))),
               aes(x = value, fill = "normal")) +
  theme_classic() +
  labs(x = "Mean and SD of Slope Parameters") +
  scale_x_continuous(labels = dollar_format()) 

## Scale Parameter
ggplot() +
  geom_density(data = as_tibble(rexp(1e4, 1)), 
               aes(x = value, fill = "rate=1")) +
  geom_density(data = as_tibble(rexp(1e4, 2)), 
               aes(x = value, fill = "rate=2"), 
               alpha = 0.5) +
  theme_classic() +
  labs(x = "Mean and SD of Scale Parameter")

## Probability Parameter
ggplot() +
  geom_density(data = as_tibble(runif(1e4, 0, 1)), 
               aes(x = value, fill = "uniform")) +
  geom_density(data = as_tibble(rbeta(1e4, 2, 2)), 
               aes(x = value, fill = "beta 2"), 
               alpha = 0.5) +
    geom_density(data = as_tibble(rbeta(1e4, 1.5, 1.5)), 
               aes(x = value, fill = "beta 1.5"), 
               alpha = 0.7) +
  theme_classic() +
  labs(x = "Mean and SD of Probability Parameter")
```

### Model 

```{stan output.var = "numpac.model"}
data {
  int<lower = 1> n;
  int num_pac_contribs[n];
  int no_corp_pacs[n];
  int new_member[n];
  real pct_white[n];
  real pct_black[n];
  real pct_latino[n];
  real pct_asian[n];
  real pct_bachelors[n];
  real pct_clinton_16[n];
  real pct_dem_house_16[n];
  real log_median_hh_income[n];
  real log_tot_voting_age[n];
}

parameters {
  real<lower = 0> a;
  real b_np;
  real b_new;
  real b_white;
  real b_black;
  real b_latino;
  real b_asian;
  real b_bach;
  real b_mhh;
  real b_clint;
  real b_house;
  real b_vpop;
  real<lower = 0> scale; // the over-dispersion parameter
}

model {
  // linear model
  vector[n] mu;
  for (i in 1:n) {
    mu[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] + 
      b_white * pct_white[i] + b_black * pct_black[i] + 
      b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
      b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
      b_house * pct_dem_house_16[i] + b_mhh * log_median_hh_income[i] +
      b_vpop * log_tot_voting_age[i];
    mu[i] = exp(mu[i]); // inverse log-link
  }
  
  // priors
  a ~ normal(6, 12);
  b_np ~ normal(0, 12);
  b_new ~ normal(0, 12);
  b_white ~ normal(0, 12);
  b_black ~ normal(0, 12);
  b_latino ~ normal(0, 12);
  b_asian ~ normal(0, 12);
  b_bach ~ normal(0, 12);
  b_clint ~ normal(0, 12);
  b_house ~ normal(0, 12);
  b_vpop ~ normal(0, 12);
  b_mhh ~ normal(0, 12);
  scale ~ cauchy(0, 2);
  
  // likelihood
  num_pac_contribs ~ neg_binomial_2(mu, scale);
}

generated quantities {
  vector[n] mu;
  //vector[n] y_rep;
  
  for (i in 1:n) {
  mu[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] + 
      b_white * pct_white[i] + b_black * pct_black[i] + 
      b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
      b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
      b_house * pct_dem_house_16[i] + b_mhh * log_median_hh_income[i] +
      b_vpop * log_tot_voting_age[i];
  mu[i] = exp(mu[i]); // inverse log-link
  
  //posterior draws to get posterior predictive checks
  //y_rep[i] = neg_binomial_2_rng(exp(mu[i]), scale); 
  }
}
```

### Estimation

```{r}
# compose data
stan.data <- 
  estimation.data %>%
  dplyr::select(num_pac_contribs, no_corp_pacs, new_member, pct_white, pct_black, 
                pct_latino, pct_asian, pct_bachelors, pct_clinton_16,
                pct_dem_house_16, log_tot_voting_age, log_median_hh_income) %>%
  mutate(no_corp_pacs = ifelse(no_corp_pacs == "YES", 1, 0),
         new_member = ifelse(new_member == "YES", 1, 0)) %>%
  drop_na() %>%
  mutate_at(.vars = vars(pct_white:log_median_hh_income), .funs = center) %>%
  compose_data()

# model estimation ------------------------------------------------------------
## Frequentist
num.pacs.01 <- glm(num_pac_contribs ~ no_corp_pacs + new_member + pct_white + pct_black + pct_latino + pct_asian + pct_bachelors + log_median_hh_income + pct_clinton_16 + pct_dem_house_16 + log_tot_voting_age,
                   family = quasipoisson(link = "log"),
                  data = as.data.frame(stan.data))

## Bayesian
numpac.fit <- sampling(numpac.model,
                       chains = 4,
                       cores = 4,
                       iter = 8000,
                       warmup = 4000,
                       data = stan.data)

traceplot(numpac.fit, 
          inc_warmup = TRUE, 
          pars = c("a", "b_np", "b_new", "b_white", "b_black", "b_latino", 
                   "b_asian", "b_bach", "b_clint", "b_house", "b_vpop", 
                   "b_mhh", "scale"))

tidy(num.pacs.01, conf.int = TRUE, conf.level = 0.89, digits = 3)
precis(numpac.fit, prob = 0.89, digits = 3)

post <- spread_draws(numpac.fit, mu[i]) %>% median_hdi()
ggplot(data = estimation.data, aes(x = num_pac_contribs)) +
  geom_density(fill = "gray") +
  geom_density(data = post, aes(x = mu), fill = "skyblue", alpha = 0.7)
```


## Model of Business PAC Contributions

### Simulating Priors

```{r}
# likelihood simulation
ggplot() +
  geom_density(data = as_tibble(rgamma(1e4, shape = 20, rate = 100)), 
               aes(x = value)) +
  theme_classic() +
  labs(x = "Mean and SD of Slope Parameters") +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) 

# prior simulation
## Intercept
ggplot() +
  geom_density(data = as_tibble(rnorm(1e4, exp(12.5), exp(14))),
               aes(x = value, fill = "Normal")) +
  theme_classic() +
  labs(x = "Mean and SD of Intercept") +
  scale_x_continuous(labels = dollar_format()) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))

## Slope Parameters
ggplot() +
  geom_density(data = as_tibble(rnorm(1e4, exp(0), exp(13))),
               aes(x = value, fill = "normal")) +
  theme_classic() +
  labs(x = "Mean and SD of Slope Parameters") +
  scale_x_continuous(labels = dollar_format()) 

## Scale Parameter
ggplot() +
  geom_density(data = as_tibble(rexp(1e4, 1)), 
               aes(x = value, fill = "rate=1")) +
  geom_density(data = as_tibble(rexp(1e4, 2)), 
               aes(x = value, fill = "rate=2"), 
               alpha = 0.5) +
  theme_classic() +
  labs(x = "Mean and SD of Scale Parameter")

## Probability Parameter
ggplot() +
  geom_density(data = as_tibble(runif(1e4, 0, 1)), 
               aes(x = value, fill = "uniform")) +
  geom_density(data = as_tibble(rbeta(1e4, 2, 2)), 
               aes(x = value, fill = "beta 2"), 
               alpha = 0.5) +
    geom_density(data = as_tibble(rbeta(1e4, 1.5, 1.5)), 
               aes(x = value, fill = "beta 1.5"), 
               alpha = 0.7) +
  theme_classic() +
  labs(x = "Mean and SD of Probability Parameter")
```

### Model 

```{stan output.var = "bizpac.model"}
data {
  int<lower = 1> n;
  real business_pacs[n];
  int no_corp_pacs[n];
  int new_member[n];
  real pct_white[n];
  real pct_black[n];
  real pct_latino[n];
  real pct_asian[n];
  real pct_bachelors[n];
  real pct_clinton_16[n];
  real pct_dem_house_16[n];
  real log_median_hh_income[n];
  real log_tot_voting_age[n];
}

parameters {
  real a;
  real b_np;
  real b_new;
  real b_white;
  real b_black;
  real b_latino;
  real b_asian;
  real b_bach;
  real b_mhh;
  real b_clint;
  real b_house;
  real b_vpop;
  real<lower = 0> scale;
  real prob;
}

model {
  // linear model
  vector[n] mu;
  for (i in 1:n) {
    mu[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] + 
      b_white * pct_white[i] + b_black * pct_black[i] + 
      b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
      b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
      b_house * pct_dem_house_16[i] + b_mhh * log_median_hh_income[i] +
      b_vpop * log_tot_voting_age[i];
    mu[i] = exp(mu[i]); // inverse link function
  }
  
  // priors
  a ~ normal(12.5, 14);
  b_np ~ normal(0, 13);
  b_new ~ normal(0, 13);
  b_white ~ normal(0, 13);
  b_black ~ normal(0, 13);
  b_latino ~ normal(0, 13);
  b_asian ~ normal(0, 13);
  b_bach ~ normal(0, 13);
  b_clint ~ normal(0, 13);
  b_house ~ normal(0, 13);
  b_vpop ~ normal(0, 13);
  b_mhh ~ normal(0, 13);
  scale ~ exponential(2);
  prob ~ beta(1.5, 1.5);
  
  // likelihood
  for ( i in 1:n) {
    if (business_pacs[i] == 0)
      target += (bernoulli_lpmf(1| prob));
    else
      target += (bernoulli_lpmf(0| prob) + gamma_lpdf(business_pacs[i]| mu[i]/scale, 1/scale));
    }//i
}

generated quantities {
  vector[n] mu;
  
  for (i in 1:n) {
  mu[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] + 
      b_white * pct_white[i] + b_black * pct_black[i] + 
      b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
      b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
      b_house * pct_dem_house_16[i] + b_mhh * log_median_hh_income[i] +
      b_vpop * log_tot_voting_age[i];
  mu[i] = exp(mu[i]); // inverse link function
  }
}
```

### Estimation

```{r}
# compose data
stan.data <- 
  estimation.data %>%
  dplyr::select(business_pacs, no_corp_pacs, new_member, pct_white, pct_black, 
                pct_latino, pct_asian, pct_bachelors, pct_clinton_16,
                pct_dem_house_16, log_tot_voting_age, log_median_hh_income) %>%
  mutate(no_corp_pacs = ifelse(no_corp_pacs == "YES", 1, 0),
         new_member = ifelse(new_member == "YES", 1, 0)) %>%
  drop_na() %>%
  mutate_at(.vars = vars(pct_white:log_median_hh_income), .funs = center) %>%
  compose_data()

# model estimation ------------------------------------------------------------
## Frequentist
biz.pacs.01 <- glm(business_pacs ~ no_corp_pacs + new_member + pct_white + pct_black + pct_latino + pct_asian + pct_bachelors + pct_clinton_16 + pct_dem_house_16 + log_median_hh_income + log_tot_voting_age,
                   family = Gamma(link = "log"),
                   data = as.data.frame(stan.data) %>% filter(business_pacs != 0) %>% mutate_at(.vars = vars(pct_white:log_median_hh_income), .funs = center))

## Bayesian
bizpac.fit <- sampling(bizpac.model,
                       chains = 4,
                       cores = 4,
                       iter = 8000,
                       warmup = 4000,
                       data = stan.data)

traceplot(bizpac.fit, 
          inc_warmup = TRUE, 
          pars = c("a", "b_np", "b_new", "b_white", "b_black", "b_latino", 
                   "b_asian", "b_bach", "b_clint", "b_house", "b_vpop", 
                   "b_mhh", "scale"))

tidy(biz.pacs.01, conf.int = TRUE, conf.level = 0.89, digits = 3)
precis(bizpac.fit, prob = 0.89, digits = 3)

post <- spread_draws(bizpac.fit, mu[i]) %>% median_hdi()
ggplot(data = estimation.data, aes(x = business_pacs)) +
  geom_density(fill = "gray") +
  geom_density(data = post, aes(x = mu), fill = "skyblue", alpha = 0.7)
```


## Model of Labor PAC Contributions

### Simulating Priors

```{r}
# likelihood simulation
ggplot() +
  geom_density(data = as_tibble(rgamma(1e4, shape = 20, rate = 100)), 
               aes(x = value)) +
  theme_classic() +
  labs(x = "Mean and SD of Slope Parameters") +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) 

# prior simulation
## Intercept
ggplot() +
  geom_density(data = as_tibble(rnorm(1e4, exp(10.5), exp(13))),
               aes(x = value, fill = "Normal")) +
  theme_classic() +
  labs(x = "Mean and SD of Intercept") +
  scale_x_continuous(labels = dollar_format()) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))

## Slope Parameters
ggplot() +
  geom_density(data = as_tibble(rnorm(1e4, exp(0), exp(12))),
               aes(x = value, fill = "normal")) +
  theme_classic() +
  labs(x = "Mean and SD of Slope Parameters") +
  scale_x_continuous(labels = dollar_format()) 

## Scale Parameter
ggplot() +
  geom_density(data = as_tibble(rexp(1e4, 1)), 
               aes(x = value, fill = "rate=1")) +
  geom_density(data = as_tibble(rexp(1e4, 2)), 
               aes(x = value, fill = "rate=2"), 
               alpha = 0.5) +
  theme_classic() +
  labs(x = "Mean and SD of Scale Parameter")

## Probability Parameter
ggplot() +
  geom_density(data = as_tibble(runif(1e4, 0, 1)), 
               aes(x = value, fill = "uniform")) +
  geom_density(data = as_tibble(rbeta(1e4, 2, 2)), 
               aes(x = value, fill = "beta 2"), 
               alpha = 0.5) +
    geom_density(data = as_tibble(rbeta(1e4, 1.5, 1.5)), 
               aes(x = value, fill = "beta 1.5"), 
               alpha = 0.7) +
  theme_classic() +
  labs(x = "Mean and SD of Probability Parameter")
```

### Model 

```{stan output.var = "laborpac.model"}
data {
  int<lower = 1> n;
  real labor_pacs[n];
  int no_corp_pacs[n];
  int new_member[n];
  real pct_white[n];
  real pct_black[n];
  real pct_latino[n];
  real pct_asian[n];
  real pct_bachelors[n];
  real pct_clinton_16[n];
  real pct_dem_house_16[n];
  real log_median_hh_income[n];
  real log_tot_voting_age[n];
}

parameters {
  real<lower = 0> a;
  real b_np;
  real b_new;
  real b_white;
  real b_black;
  real b_latino;
  real b_asian;
  real b_bach;
  real b_mhh;
  real b_clint;
  real b_house;
  real b_vpop;
  real<lower = 0> scale;
  real prob;
}

model {
  // linear model
  vector[n] mu;
  for (i in 1:n) {
    mu[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] + 
      b_white * pct_white[i] + b_black * pct_black[i] + 
      b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
      b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
      b_house * pct_dem_house_16[i] + b_mhh * log_median_hh_income[i] +
      b_vpop * log_tot_voting_age[i];
    mu[i] = exp(mu[i]); // inverse link function
  }
  
  // priors
  a ~ normal(10.5, 13);
  b_np ~ normal(0, 12);
  b_new ~ normal(0, 12);
  b_white ~ normal(0, 12);
  b_black ~ normal(0, 12);
  b_latino ~ normal(0, 12);
  b_asian ~ normal(0, 12);
  b_bach ~ normal(0, 12);
  b_clint ~ normal(0, 12);
  b_house ~ normal(0, 12);
  b_vpop ~ normal(0, 12);
  b_mhh ~ normal(0, 12);
  scale ~ exponential(2);
  prob ~ beta(1.5, 1.5);
  
  // likelihood
  for ( i in 1:n) {
    if (labor_pacs[i] == 0)
      target += (bernoulli_lpmf(1| prob));
    else
      target += (bernoulli_lpmf(0| prob) + gamma_lpdf(labor_pacs[i]| mu[i]/scale, 1/scale));
    }//i
}

generated quantities {
  vector[n] mu;
  
  for (i in 1:n) {
  mu[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] + 
      b_white * pct_white[i] + b_black * pct_black[i] + 
      b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
      b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
      b_house * pct_dem_house_16[i] + b_mhh * log_median_hh_income[i] +
      b_vpop * log_tot_voting_age[i];
  mu[i] = exp(mu[i]); // inverse link function
  }
}
```


```{stan output.var = "int_laborpac.model"}
data {
  int<lower = 1> n;
  real labor_pacs[n];
  int no_corp_pacs[n];
  int new_member[n];
  real pct_white[n];
  real pct_black[n];
  real pct_latino[n];
  real pct_asian[n];
  real pct_bachelors[n];
  real pct_clinton_16[n];
  real pct_dem_house_16[n];
  real log_median_hh_income[n];
  real log_tot_voting_age[n];
}

parameters {
  real<lower = 0> a;
  real b_np;
  real b_new;
  real b_int;
  real b_white;
  real b_black;
  real b_latino;
  real b_asian;
  real b_bach;
  real b_mhh;
  real b_clint;
  real b_house;
  real b_vpop;
  real<lower = 0> scale;
  real prob;
}

model {
  // linear model
  vector[n] mu;
  for (i in 1:n) {
    mu[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] + 
      b_int * (no_corp_pacs[i] * new_member[i]) +
      b_white * pct_white[i] + b_black * pct_black[i] + 
      b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
      b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
      b_house * pct_dem_house_16[i] + b_mhh * log_median_hh_income[i] +
      b_vpop * log_tot_voting_age[i];
    mu[i] = exp(mu[i]); // inverse link function
  }
  
  // priors
  a ~ normal(10.5, 13);
  b_np ~ normal(0, 12);
  b_new ~ normal(0, 12);
  b_int ~ normal(0, 12);
  b_white ~ normal(0, 12);
  b_black ~ normal(0, 12);
  b_latino ~ normal(0, 12);
  b_asian ~ normal(0, 12);
  b_bach ~ normal(0, 12);
  b_clint ~ normal(0, 12);
  b_house ~ normal(0, 12);
  b_vpop ~ normal(0, 12);
  b_mhh ~ normal(0, 12);
  scale ~ exponential(2);
  prob ~ beta(1.5, 1.5);
  
  // likelihood
  for ( i in 1:n) {
    if (labor_pacs[i] == 0)
      target += (bernoulli_lpmf(1| prob));
    else
      target += (bernoulli_lpmf(0| prob) + gamma_lpdf(labor_pacs[i]| mu[i]/scale, 1/scale));
    }//i
}

generated quantities {
  vector[n] mu;
  
  for (i in 1:n) {
  mu[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] + 
    b_int * (no_corp_pacs[i] * new_member[i]) +
    b_white * pct_white[i] + b_black * pct_black[i] + 
    b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
    b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
    b_house * pct_dem_house_16[i] + b_mhh * log_median_hh_income[i] +
    b_vpop * log_tot_voting_age[i];
  mu[i] = exp(mu[i]); // inverse link function
  }
}
```

### Estimation

```{r}
# compose data
stan.data <- 
  estimation.data %>%
  dplyr::select(labor_pacs, no_corp_pacs, new_member, pct_white, pct_black, 
                pct_latino, pct_asian, pct_bachelors, pct_clinton_16,
                pct_dem_house_16, log_tot_voting_age, log_median_hh_income) %>%
  mutate(no_corp_pacs = ifelse(no_corp_pacs == "YES", 1, 0),
         new_member = ifelse(new_member == "YES", 1, 0)) %>%
  drop_na() %>%
  mutate_at(.vars = vars(pct_white:log_median_hh_income), .funs = center) %>%
  compose_data()

# model estimation ------------------------------------------------------------
## Frequentist
labor.pacs.01 <- glm(labor_pacs ~ no_corp_pacs + new_member + pct_white + pct_black + pct_latino + pct_asian + pct_bachelors + pct_clinton_16 + pct_dem_house_16 + log_median_hh_income + log_tot_voting_age,
                     family = Gamma(link = "log"),
                     data = as.data.frame(stan.data) %>% filter(labor_pacs != 0) %>% mutate_at(.vars = vars(pct_white:log_median_hh_income), .funs = center))

## Bayesian
laborpac.fit <- sampling(laborpac.model,
                         chains = 4,
                         cores = 4,
                         iter = 8000,
                         warmup = 4000,
                         data = stan.data)

traceplot(laborpac.fit, 
          inc_warmup = TRUE, 
          pars = c("a", "b_np", "b_new", "b_white", "b_black", "b_latino", 
                   "b_asian", "b_bach", "b_clint", "b_house", "b_vpop", 
                   "b_mhh", "scale"))

tidy(labor.pacs.01, conf.int = TRUE, conf.level = 0.89, digits = 3)
precis(laborpac.fit, prob = 0.89, digits = 3)

post <- spread_draws(laborpac.fit, mu[i]) %>% median_hdi()
ggplot(data = estimation.data, aes(x = labor_pacs)) +
  geom_density(fill = "gray") +
  geom_density(data = post, aes(x = mu), fill = "skyblue", alpha = 0.7)


int_laborpac.fit <- sampling(int_laborpac.model,
                             chains = 4,
                             cores = 4,
                             iter = 8000,
                             warmup = 4000,
                             data = stan.data)

traceplot(int_laborpac.fit, 
          inc_warmup = TRUE, 
          pars = c("a", "b_np", "b_new", "b_int", "b_white", "b_black", "b_latino", 
                   "b_asian", "b_bach", "b_clint", "b_house", "b_vpop", 
                   "b_mhh", "scale"))

precis(int_laborpac.fit, prob = 0.89, digits = 3)

post <- spread_draws(int_laborpac.fit, mu[i]) %>% median_hdi()
ggplot(data = estimation.data, aes(x = labor_pacs)) +
  geom_density(fill = "gray") +
  geom_density(data = post, aes(x = mu), fill = "skyblue", alpha = 0.7)
```


## Model of Ideological PAC Contributions

### Simulating Priors

```{r}
# likelihood simulation
ggplot() +
  geom_density(data = as_tibble(rgamma(1e4, shape = 20, rate = 100)), 
               aes(x = value)) +
  theme_classic() +
  labs(x = "Mean and SD of Slope Parameters") +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) 

# prior simulation
## Intercept
ggplot() +
  geom_density(data = as_tibble(rnorm(1e4, exp(10.5), exp(13))),
               aes(x = value, fill = "Normal")) +
  theme_classic() +
  labs(x = "Mean and SD of Intercept") +
  scale_x_continuous(labels = dollar_format()) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))

## Slope Parameters
ggplot() +
  geom_density(data = as_tibble(rnorm(1e4, exp(0), exp(12))),
               aes(x = value, fill = "normal")) +
  theme_classic() +
  labs(x = "Mean and SD of Slope Parameters") +
  scale_x_continuous(labels = dollar_format()) 

## Scale Parameter
ggplot() +
  geom_density(data = as_tibble(rexp(1e4, 1)), 
               aes(x = value, fill = "rate=1")) +
  geom_density(data = as_tibble(rexp(1e4, 2)), 
               aes(x = value, fill = "rate=2"), 
               alpha = 0.5) +
  theme_classic() +
  labs(x = "Mean and SD of Scale Parameter")

## Probability Parameter
ggplot() +
  geom_density(data = as_tibble(runif(1e4, 0, 1)), 
               aes(x = value, fill = "uniform")) +
  geom_density(data = as_tibble(rbeta(1e4, 2, 2)), 
               aes(x = value, fill = "beta 2"), 
               alpha = 0.5) +
    geom_density(data = as_tibble(rbeta(1e4, 1.5, 1.5)), 
               aes(x = value, fill = "beta 1.5"), 
               alpha = 0.7) +
  theme_classic() +
  labs(x = "Mean and SD of Probability Parameter")
```

### Model 

```{stan output.var = "ideopac.model"}
data {
  int<lower = 1> n;
  real ideological_pacs[n];
  int no_corp_pacs[n];
  int new_member[n];
  real pct_white[n];
  real pct_black[n];
  real pct_latino[n];
  real pct_asian[n];
  real pct_bachelors[n];
  real pct_clinton_16[n];
  real pct_dem_house_16[n];
  real log_median_hh_income[n];
  real log_tot_voting_age[n];
}

parameters {
  real<lower = 0> a;
  real b_np;
  real b_new;
  real b_white;
  real b_black;
  real b_latino;
  real b_asian;
  real b_bach;
  real b_mhh;
  real b_clint;
  real b_house;
  real b_vpop;
  real<lower = 0> scale;
  real prob;
}

model {
  // linear model
  vector[n] mu;
  for (i in 1:n) {
    mu[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] + 
      b_white * pct_white[i] + b_black * pct_black[i] + 
      b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
      b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
      b_house * pct_dem_house_16[i] + b_mhh * log_median_hh_income[i] +
      b_vpop * log_tot_voting_age[i];
    mu[i] = exp(mu[i]); // inverse link function
  }
  
  // priors
  a ~ normal(10.5, 13);
  b_np ~ normal(0, 12);
  b_new ~ normal(0, 12);
  b_white ~ normal(0, 12);
  b_black ~ normal(0, 12);
  b_latino ~ normal(0, 12);
  b_asian ~ normal(0, 12);
  b_bach ~ normal(0, 12);
  b_clint ~ normal(0, 12);
  b_house ~ normal(0, 12);
  b_vpop ~ normal(0, 12);
  b_mhh ~ normal(0, 12);
  scale ~ exponential(2);
  prob ~ beta(1.5, 1.5);
  
  // likelihood
  for ( i in 1:n) {
    if (ideological_pacs[i] == 0)
      target += (bernoulli_lpmf(1| prob));
    else
      target += (bernoulli_lpmf(0| prob) + gamma_lpdf(ideological_pacs[i]| mu[i]/scale, 1/scale));
    }//i
}

generated quantities {
  vector[n] mu;
  
  for (i in 1:n) {
  mu[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] + 
      b_white * pct_white[i] + b_black * pct_black[i] + 
      b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
      b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
      b_house * pct_dem_house_16[i] + b_mhh * log_median_hh_income[i] +
      b_vpop * log_tot_voting_age[i];
  mu[i] = exp(mu[i]); // inverse link function
  }
}
```

```{stan output.var = "int_ideopac.model"}
data {
  int<lower = 1> n;
  real ideological_pacs[n];
  int no_corp_pacs[n];
  int new_member[n];
  real pct_white[n];
  real pct_black[n];
  real pct_latino[n];
  real pct_asian[n];
  real pct_bachelors[n];
  real pct_clinton_16[n];
  real pct_dem_house_16[n];
  real log_median_hh_income[n];
  real log_tot_voting_age[n];
}

parameters {
  real<lower = 0> a;
  real b_np;
  real b_new;
  real b_int;
  real b_white;
  real b_black;
  real b_latino;
  real b_asian;
  real b_bach;
  real b_mhh;
  real b_clint;
  real b_house;
  real b_vpop;
  real<lower = 0> scale;
  real prob;
}

model {
  // linear model
  vector[n] mu;
  for (i in 1:n) {
    mu[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] + 
      b_int * (no_corp_pacs[i] * new_member[i]) +
      b_white * pct_white[i] + b_black * pct_black[i] + 
      b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
      b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
      b_house * pct_dem_house_16[i] + b_mhh * log_median_hh_income[i] +
      b_vpop * log_tot_voting_age[i];
    mu[i] = exp(mu[i]); // inverse link function
  }
  
  // priors
  a ~ normal(10.5, 13);
  b_np ~ normal(0, 12);
  b_new ~ normal(0, 12);
  b_int ~ normal(0, 12);
  b_white ~ normal(0, 12);
  b_black ~ normal(0, 12);
  b_latino ~ normal(0, 12);
  b_asian ~ normal(0, 12);
  b_bach ~ normal(0, 12);
  b_clint ~ normal(0, 12);
  b_house ~ normal(0, 12);
  b_vpop ~ normal(0, 12);
  b_mhh ~ normal(0, 12);
  scale ~ exponential(2);
  prob ~ beta(1.5, 1.5);
  
  // likelihood
  for ( i in 1:n) {
    if (ideological_pacs[i] == 0)
      target += (bernoulli_lpmf(1| prob));
    else
      target += (bernoulli_lpmf(0| prob) + gamma_lpdf(ideological_pacs[i]| mu[i]/scale, 1/scale));
    }//i
}

generated quantities {
  vector[n] mu;
  
  for (i in 1:n) {
  mu[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] +
      b_int * (no_corp_pacs[i] * new_member[i]) +
      b_white * pct_white[i] + b_black * pct_black[i] + 
      b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
      b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
      b_house * pct_dem_house_16[i] + b_mhh * log_median_hh_income[i] +
      b_vpop * log_tot_voting_age[i];
  mu[i] = exp(mu[i]); // inverse link function
  }
}
```

### Estimation

```{r}
# compose data
stan.data <- 
  estimation.data %>%
  dplyr::select(ideological_pacs, no_corp_pacs, new_member, pct_white, pct_black, 
                pct_latino, pct_asian, pct_bachelors, pct_clinton_16,
                pct_dem_house_16, log_tot_voting_age, log_median_hh_income) %>%
  mutate(no_corp_pacs = ifelse(no_corp_pacs == "YES", 1, 0),
         new_member = ifelse(new_member == "YES", 1, 0)) %>%
  drop_na() %>%
  mutate_at(.vars = vars(pct_white:log_median_hh_income), .funs = center) %>%
  compose_data()

# model estimation ------------------------------------------------------------
## Frequentist
ideol.pacs.01 <- glm(ideological_pacs ~ no_corp_pacs + new_member + pct_white + pct_black + pct_latino + pct_asian + pct_bachelors + pct_clinton_16 + pct_dem_house_16 + log_median_hh_income + log_tot_voting_age,
                     family = Gamma(link = "log"),
                     data = as.data.frame(stan.data) %>% filter(ideological_pacs != 0) %>% mutate_at(.vars = vars(pct_white:log_median_hh_income), .funs = center))

## Bayesian
ideopac.fit <- sampling(ideopac.model,
                        chains = 4,
                        cores = 4,
                        iter = 8000,
                        warmup = 4000,
                        data = stan.data)

traceplot(ideopac.fit, 
          inc_warmup = TRUE, 
          pars = c("a", "b_np", "b_new", "b_white", "b_black", "b_latino", 
                   "b_asian", "b_bach", "b_clint", "b_house", "b_vpop", 
                   "b_mhh", "scale"))

tidy(ideol.pacs.01, conf.int = TRUE, conf.level = 0.89, digits = 3)
precis(ideopac.fit, prob = 0.89, digits = 3)

post <- spread_draws(ideopac.fit, mu[i]) %>% median_hdi()
ggplot(data = estimation.data, aes(x = ideological_pacs)) +
  geom_density(fill = "gray") +
  geom_density(data = post, aes(x = mu), fill = "skyblue", alpha = 0.7)

int_ideopac.fit <- sampling(int_ideopac.model,
                            chains = 4,
                            cores = 4,
                            iter = 8000,
                            warmup = 4000,
                            data = stan.data)

traceplot(int_ideopac.fit, 
          inc_warmup = TRUE, 
          pars = c("a", "b_np", "b_new", "b_int", "b_white", "b_black", "b_latino", 
                   "b_asian", "b_bach", "b_clint", "b_house", "b_vpop", 
                   "b_mhh", "scale"))

\precis(int_ideopac.fit, prob = 0.89, digits = 3)

post <- spread_draws(int_ideopac.fit, mu[i]) %>% median_hdi()
ggplot(data = estimation.data, aes(x = ideological_pacs)) +
  geom_density(fill = "gray") +
  geom_density(data = post, aes(x = mu), fill = "skyblue", alpha = 0.7)
```


## Model of Independent Ideological PAC Contributions

### Simulating Priors

```{r}
# likelihood simulation
ggplot() +
  geom_density(data = as_tibble(rgamma(1e4, shape = 20, rate = 100)), 
               aes(x = value)) +
  theme_classic() +
  labs(x = "Mean and SD of Slope Parameters") +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) 

# prior simulation
## Intercept
ggplot() +
  geom_density(data = as_tibble(rnorm(1e4, exp(10.5), exp(13))),
               aes(x = value, fill = "Normal")) +
  theme_classic() +
  labs(x = "Mean and SD of Intercept") +
  scale_x_continuous(labels = dollar_format()) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))

## Slope Parameters
ggplot() +
  geom_density(data = as_tibble(rnorm(1e4, exp(0), exp(12))),
               aes(x = value, fill = "normal")) +
  theme_classic() +
  labs(x = "Mean and SD of Slope Parameters") +
  scale_x_continuous(labels = dollar_format()) 

## Scale Parameter
ggplot() +
  geom_density(data = as_tibble(rexp(1e4, 1)), 
               aes(x = value, fill = "rate=1")) +
  geom_density(data = as_tibble(rexp(1e4, 2)), 
               aes(x = value, fill = "rate=2"), 
               alpha = 0.5) +
  theme_classic() +
  labs(x = "Mean and SD of Scale Parameter")

## Probability Parameter
ggplot() +
  geom_density(data = as_tibble(runif(1e4, 0, 1)), 
               aes(x = value, fill = "uniform")) +
  geom_density(data = as_tibble(rbeta(1e4, 2, 2)), 
               aes(x = value, fill = "beta 2"), 
               alpha = 0.5) +
    geom_density(data = as_tibble(rbeta(1e4, 1.5, 1.5)), 
               aes(x = value, fill = "beta 1.5"), 
               alpha = 0.7) +
  theme_classic() +
  labs(x = "Mean and SD of Probability Parameter")
```

### Model 

```{stan output.var = "indideopac.model"}
data {
  int<lower = 1> n;
  real ind_pac_ideological[n];
  int no_corp_pacs[n];
  int new_member[n];
  real pct_white[n];
  real pct_black[n];
  real pct_latino[n];
  real pct_asian[n];
  real pct_bachelors[n];
  real pct_clinton_16[n];
  real pct_dem_house_16[n];
  real log_median_hh_income[n];
  real log_tot_voting_age[n];
}

parameters {
  real<lower = 0> a;
  real b_np;
  real b_new;
  real b_white;
  real b_black;
  real b_latino;
  real b_asian;
  real b_bach;
  real b_mhh;
  real b_clint;
  real b_house;
  real b_vpop;
  real<lower = 0> scale;
  real<lower = 0, upper = 1> prob;
}

model {
  // linear model
  vector[n] mu;
  for (i in 1:n) {
    mu[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] + 
      b_white * pct_white[i] + b_black * pct_black[i] + 
      b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
      b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
      b_house * pct_dem_house_16[i] + b_mhh * log_median_hh_income[i] +
      b_vpop * log_tot_voting_age[i];
    mu[i] = exp(mu[i]); // inverse link function
  }
  
  // priors
  a ~ normal(10.5, 13);
  b_np ~ normal(0, 12);
  b_new ~ normal(0, 12);
  b_white ~ normal(0, 12);
  b_black ~ normal(0, 12);
  b_latino ~ normal(0, 12);
  b_asian ~ normal(0, 12);
  b_bach ~ normal(0, 12);
  b_clint ~ normal(0, 12);
  b_house ~ normal(0, 12);
  b_vpop ~ normal(0, 12);
  b_mhh ~ normal(0, 12);
  scale ~ exponential(2);
  prob ~ beta(1.5, 1.5);
  
  // likelihood
  for ( i in 1:n) {
    if (ind_pac_ideological[i] == 0)
      target += (bernoulli_lpmf(1| prob));
    else
      target += (bernoulli_lpmf(0| prob) + gamma_lpdf(ind_pac_ideological[i]| mu[i]/scale, 1/scale));
    }//i
}

generated quantities {
  vector[n] mu;
  
  for (i in 1:n) {
  mu[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] + 
      b_white * pct_white[i] + b_black * pct_black[i] + 
      b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
      b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
      b_house * pct_dem_house_16[i] + b_mhh * log_median_hh_income[i] +
      b_vpop * log_tot_voting_age[i];
  mu[i] = exp(mu[i]); // inverse link function
  }
}
```

```{stan output.var = "int_indideopac.model"}
data {
  int<lower = 1> n;
  real ind_pac_ideological[n];
  int no_corp_pacs[n];
  int new_member[n];
  real pct_white[n];
  real pct_black[n];
  real pct_latino[n];
  real pct_asian[n];
  real pct_bachelors[n];
  real pct_clinton_16[n];
  real pct_dem_house_16[n];
  real log_median_hh_income[n];
  real log_tot_voting_age[n];
}

parameters {
  real<lower = 0> a;
  real b_np;
  real b_new;
  real b_int;
  real b_white;
  real b_black;
  real b_latino;
  real b_asian;
  real b_bach;
  real b_mhh;
  real b_clint;
  real b_house;
  real b_vpop;
  real<lower = 0> scale;
  real<lower = 0, upper = 1> prob;
}

model {
  // linear model
  vector[n] mu;
  for (i in 1:n) {
    mu[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] +
      b_int * (no_corp_pacs[i] * new_member[i]) +
      b_white * pct_white[i] + b_black * pct_black[i] + 
      b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
      b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
      b_house * pct_dem_house_16[i] + b_mhh * log_median_hh_income[i] +
      b_vpop * log_tot_voting_age[i];
    mu[i] = exp(mu[i]); // inverse link function
  }
  
  // priors
  a ~ normal(10.5, 13);
  b_np ~ normal(0, 12);
  b_new ~ normal(0, 12);
  b_int ~ normal(0, 12);
  b_white ~ normal(0, 12);
  b_black ~ normal(0, 12);
  b_latino ~ normal(0, 12);
  b_asian ~ normal(0, 12);
  b_bach ~ normal(0, 12);
  b_clint ~ normal(0, 12);
  b_house ~ normal(0, 12);
  b_vpop ~ normal(0, 12);
  b_mhh ~ normal(0, 12);
  scale ~ exponential(2);
  prob ~ beta(1.5, 1.5);
  
  // likelihood
  for ( i in 1:n) {
    if (ind_pac_ideological[i] == 0)
      target += (bernoulli_lpmf(1| prob));
    else
      target += (bernoulli_lpmf(0| prob) + gamma_lpdf(ind_pac_ideological[i]| mu[i]/scale, 1/scale));
    }//i
}

generated quantities {
  vector[n] mu;
  
  for (i in 1:n) {
  mu[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] +
    b_int * (no_corp_pacs[i] * new_member[i]) +
      b_white * pct_white[i] + b_black * pct_black[i] + 
      b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
      b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
      b_house * pct_dem_house_16[i] + b_mhh * log_median_hh_income[i] +
      b_vpop * log_tot_voting_age[i];
  mu[i] = exp(mu[i]); // inverse link function
  }
}
```

### Estimation

```{r}
# compose data
stan.data <- 
  estimation.data %>%
  dplyr::select(ind_pac_ideological, no_corp_pacs, new_member, pct_white, pct_black, 
                pct_latino, pct_asian, pct_bachelors, pct_clinton_16,
                pct_dem_house_16, log_tot_voting_age, log_median_hh_income) %>%
  mutate(no_corp_pacs = ifelse(no_corp_pacs == "YES", 1, 0),
         new_member = ifelse(new_member == "YES", 1, 0)) %>%
  drop_na() %>%
  mutate_at(.vars = vars(pct_white:log_median_hh_income), .funs = center) %>%
  compose_data()

# model estimation ------------------------------------------------------------
## Frequentist
# indideol.pacs.01 <- glm(ind_pac_ideological ~ no_corp_pacs + new_member + pct_white + pct_black + pct_latino + pct_asian + pct_bachelors + pct_clinton_16 + pct_dem_house_16 + log_median_hh_income + log_tot_voting_age,
#                      family = Gamma(link = "log"),
#                      data = as.data.frame(stan.data) %>% filter(ind_pac_ideological != 0) %>% mutate_at(.vars = vars(pct_white:log_median_hh_income), .funs = center))

## Bayesian
indideopac.fit <- sampling(indideopac.model,
                        chains = 4,
                        cores = 4,
                        iter = 8000,
                        warmup = 4000,
                        data = stan.data)

traceplot(indideopac.fit, 
          inc_warmup = TRUE, 
          pars = c("a", "b_np", "b_new", "b_white", "b_black", "b_latino", 
                   "b_asian", "b_bach", "b_clint", "b_house", "b_vpop", 
                   "b_mhh", "scale"))

#tidy(indideol.pacs.01, conf.int = TRUE, conf.level = 0.89, digits = 3)
precis(indideopac.fit, prob = 0.89, digits = 3)

post <- spread_draws(indideopac.fit, mu[i]) %>% median_hdi()
ggplot(data = estimation.data, aes(x = ind_pac_ideological)) +
  geom_density(fill = "gray") +
  geom_density(data = post, aes(x = mu), fill = "skyblue", alpha = 0.7)

int_indideopac.fit <- sampling(int_indideopac.model,
                               chains = 4,
                               cores = 4,
                               iter = 8000,
                               warmup = 4000,
                               data = stan.data)

traceplot(int_indideopac.fit, 
          inc_warmup = TRUE, 
          pars = c("a", "b_np", "b_new", "b_int", "b_white", "b_black", "b_latino", 
                   "b_asian", "b_bach", "b_clint", "b_house", "b_vpop", 
                   "b_mhh", "scale"))

#tidy(indideol.pacs.01, conf.int = TRUE, conf.level = 0.89, digits = 3)
precis(int_indideopac.fit, prob = 0.89, digits = 3)

post <- spread_draws(int_indideopac.fit, mu[i]) %>% median_hdi()
ggplot(data = estimation.data, aes(x = ind_pac_ideological)) +
  geom_density(fill = "gray") +
  geom_density(data = post, aes(x = mu), fill = "skyblue", alpha = 0.7)
```


## Model of Direct Ideological PAC Contributions

### Simulating Priors

```{r}
# likelihood simulation
ggplot() +
  geom_density(data = as_tibble(rgamma(1e4, shape = 20, rate = 100)), 
               aes(x = value)) +
  theme_classic() +
  labs(x = "Mean and SD of Slope Parameters") +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) 

# prior simulation
## Intercept
ggplot() +
  geom_density(data = as_tibble(rnorm(1e4, exp(10.5), exp(13))),
               aes(x = value, fill = "Normal")) +
  theme_classic() +
  labs(x = "Mean and SD of Intercept") +
  scale_x_continuous(labels = dollar_format()) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))

## Slope Parameters
ggplot() +
  geom_density(data = as_tibble(rnorm(1e4, exp(0), exp(12))),
               aes(x = value, fill = "normal")) +
  theme_classic() +
  labs(x = "Mean and SD of Slope Parameters") +
  scale_x_continuous(labels = dollar_format()) 

## Scale Parameter
ggplot() +
  geom_density(data = as_tibble(rexp(1e4, 1)), 
               aes(x = value, fill = "rate=1")) +
  geom_density(data = as_tibble(rexp(1e4, 2)), 
               aes(x = value, fill = "rate=2"), 
               alpha = 0.5) +
  theme_classic() +
  labs(x = "Mean and SD of Scale Parameter")

## Probability Parameter
ggplot() +
  geom_density(data = as_tibble(runif(1e4, 0, 1)), 
               aes(x = value, fill = "uniform")) +
  geom_density(data = as_tibble(rbeta(1e4, 2, 2)), 
               aes(x = value, fill = "beta 2"), 
               alpha = 0.5) +
    geom_density(data = as_tibble(rbeta(1e4, 1.5, 1.5)), 
               aes(x = value, fill = "beta 1.5"), 
               alpha = 0.7) +
  theme_classic() +
  labs(x = "Mean and SD of Probability Parameter")
```

### Model 

```{stan output.var = "dirideopac.model"}
data {
  int<lower = 1> n;
  real dir_pac_ideological[n];
  int no_corp_pacs[n];
  int new_member[n];
  real pct_white[n];
  real pct_black[n];
  real pct_latino[n];
  real pct_asian[n];
  real pct_bachelors[n];
  real pct_clinton_16[n];
  real pct_dem_house_16[n];
  real log_median_hh_income[n];
  real log_tot_voting_age[n];
}

parameters {
  real<lower = 0> a;
  real b_np;
  real b_new;
  real b_white;
  real b_black;
  real b_latino;
  real b_asian;
  real b_bach;
  real b_mhh;
  real b_clint;
  real b_house;
  real b_vpop;
  real<lower = 0> scale;
  real<lower = 0, upper = 1> prob;
}

model {
  // linear model
  vector[n] mu;
  for (i in 1:n) {
    mu[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] + 
      b_white * pct_white[i] + b_black * pct_black[i] + 
      b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
      b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
      b_house * pct_dem_house_16[i] + b_mhh * log_median_hh_income[i] +
      b_vpop * log_tot_voting_age[i];
    mu[i] = exp(mu[i]); // inverse link function
  }
  
  // priors
  a ~ normal(10.5, 13);
  b_np ~ normal(0, 12);
  b_new ~ normal(0, 12);
  b_white ~ normal(0, 12);
  b_black ~ normal(0, 12);
  b_latino ~ normal(0, 12);
  b_asian ~ normal(0, 12);
  b_bach ~ normal(0, 12);
  b_clint ~ normal(0, 12);
  b_house ~ normal(0, 12);
  b_vpop ~ normal(0, 12);
  b_mhh ~ normal(0, 12);
  scale ~ exponential(2);
  prob ~ beta(1.5, 1.5);
  
  // likelihood
  for ( i in 1:n) {
    if (dir_pac_ideological[i] == 0)
      target += (bernoulli_lpmf(1| prob));
    else
      target += (bernoulli_lpmf(0| prob) + gamma_lpdf(dir_pac_ideological[i]| mu[i]/scale, 1/scale));
    }//i
}

generated quantities {
  vector[n] mu;
  
  for (i in 1:n) {
  mu[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] + 
      b_white * pct_white[i] + b_black * pct_black[i] + 
      b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
      b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
      b_house * pct_dem_house_16[i] + b_mhh * log_median_hh_income[i] +
      b_vpop * log_tot_voting_age[i];
  mu[i] = exp(mu[i]); // inverse link function
  }
}
```

```{stan output.var = "int_dirideopac.model"}
data {
  int<lower = 1> n;
  real dir_pac_ideological[n];
  int no_corp_pacs[n];
  int new_member[n];
  real pct_white[n];
  real pct_black[n];
  real pct_latino[n];
  real pct_asian[n];
  real pct_bachelors[n];
  real pct_clinton_16[n];
  real pct_dem_house_16[n];
  real log_median_hh_income[n];
  real log_tot_voting_age[n];
}

parameters {
  real<lower = 0> a;
  real b_np;
  real b_new;
  real b_int;
  real b_white;
  real b_black;
  real b_latino;
  real b_asian;
  real b_bach;
  real b_mhh;
  real b_clint;
  real b_house;
  real b_vpop;
  real<lower = 0> scale;
  real<lower = 0, upper = 1> prob;
}

model {
  // linear model
  vector[n] mu;
  for (i in 1:n) {
    mu[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] +
      b_int * (no_corp_pacs[i] * new_member[i]) +
      b_white * pct_white[i] + b_black * pct_black[i] + 
      b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
      b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
      b_house * pct_dem_house_16[i] + b_mhh * log_median_hh_income[i] +
      b_vpop * log_tot_voting_age[i];
    mu[i] = exp(mu[i]); // inverse link function
  }
  
  // priors
  a ~ normal(10.5, 13);
  b_np ~ normal(0, 12);
  b_new ~ normal(0, 12);
  b_int ~ normal(0, 12);
  b_white ~ normal(0, 12);
  b_black ~ normal(0, 12);
  b_latino ~ normal(0, 12);
  b_asian ~ normal(0, 12);
  b_bach ~ normal(0, 12);
  b_clint ~ normal(0, 12);
  b_house ~ normal(0, 12);
  b_vpop ~ normal(0, 12);
  b_mhh ~ normal(0, 12);
  scale ~ exponential(2);
  prob ~ beta(1.5, 1.5);
  
  // likelihood
  for ( i in 1:n) {
    if (dir_pac_ideological[i] == 0)
      target += (bernoulli_lpmf(1| prob));
    else
      target += (bernoulli_lpmf(0| prob) + gamma_lpdf(dir_pac_ideological[i]| mu[i]/scale, 1/scale));
    }//i
}

generated quantities {
  vector[n] mu;
  
  for (i in 1:n) {
  mu[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] +
      b_int * (no_corp_pacs[i] * new_member[i]) +
      b_white * pct_white[i] + b_black * pct_black[i] + 
      b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
      b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
      b_house * pct_dem_house_16[i] + b_mhh * log_median_hh_income[i] +
      b_vpop * log_tot_voting_age[i];
  mu[i] = exp(mu[i]); // inverse link function
  }
}
```

### Estimation

```{r}
# compose data
stan.data <- 
  estimation.data %>%
  dplyr::select(dir_pac_ideological, no_corp_pacs, new_member, pct_white, pct_black, 
                pct_latino, pct_asian, pct_bachelors, pct_clinton_16,
                pct_dem_house_16, log_tot_voting_age, log_median_hh_income) %>%
  mutate(no_corp_pacs = ifelse(no_corp_pacs == "YES", 1, 0),
         new_member = ifelse(new_member == "YES", 1, 0)) %>%
  drop_na() %>%
  mutate_at(.vars = vars(pct_white:log_median_hh_income), .funs = center) %>%
  compose_data()

# model estimation ------------------------------------------------------------
## Frequentist
dirideol.pacs.01 <- glm(dir_pac_ideological ~ no_corp_pacs + new_member + pct_white + pct_black + pct_latino + pct_asian + pct_bachelors + pct_clinton_16 + pct_dem_house_16 + log_median_hh_income + log_tot_voting_age,
                     family = Gamma(link = "log"),
                     data = as.data.frame(stan.data) %>% filter(dir_pac_ideological != 0) %>% mutate_at(.vars = vars(pct_white:log_median_hh_income), .funs = center))

## Bayesian
dirideopac.fit <- sampling(dirideopac.model,
                        chains = 4,
                        cores = 4,
                        iter = 8000,
                        warmup = 4000,
                        data = stan.data)

traceplot(dirideopac.fit, 
          inc_warmup = TRUE, 
          pars = c("a", "b_np", "b_new", "b_white", "b_black", "b_latino", 
                   "b_asian", "b_bach", "b_clint", "b_house", "b_vpop", 
                   "b_mhh", "scale"))

tidy(dirideol.pacs.01, conf.int = TRUE, conf.level = 0.89, digits = 3)
precis(dirideopac.fit, prob = 0.89, digits = 3)

post <- spread_draws(dirideopac.fit, mu[i]) %>% median_hdi()
ggplot(data = estimation.data, aes(x = dir_pac_ideological)) +
  geom_density(fill = "gray") +
  geom_density(data = post, aes(x = mu), fill = "skyblue", alpha = 0.7)

ind_dirideopac.fit <- sampling(int_dirideopac.model,
                               chains = 4,
                               cores = 4,
                               iter = 8000,
                               warmup = 4000,
                               data = stan.data)

traceplot(ind_dirideopac.fit, 
          inc_warmup = TRUE, 
          pars = c("a", "b_np", "b_new", "b_int", "b_white", "b_black", "b_latino", 
                   "b_asian", "b_bach", "b_clint", "b_house", "b_vpop", 
                   "b_mhh", "scale"))

precis(ind_dirideopac.fit, prob = 0.89, digits = 3)

post <- spread_draws(ind_dirideopac.fit, mu[i]) %>% median_hdi()
ggplot(data = estimation.data, aes(x = dir_pac_ideological)) +
  geom_density(fill = "gray") +
  geom_density(data = post, aes(x = mu), fill = "skyblue", alpha = 0.7)
```


# Party Models

## Model of Leadership PAC Contributions

### Simulating Priors

```{r}
# likelihood simulation
ggplot() +
  geom_density(data = as_tibble(rgamma(1e4, shape = 20, rate = 100)), 
               aes(x = value)) +
  theme_classic() +
  labs(x = "Mean and SD of Slope Parameters") +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) 

# prior simulation
## Intercept
ggplot() +
  geom_density(data = as_tibble(rnorm(1e4, exp(10.5), exp(13))),
               aes(x = value, fill = "Normal")) +
  theme_classic() +
  labs(x = "Mean and SD of Intercept") +
  scale_x_continuous(labels = dollar_format()) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))

## Slope Parameters
ggplot() +
  geom_density(data = as_tibble(rnorm(1e4, exp(0), exp(12))),
               aes(x = value, fill = "normal")) +
  theme_classic() +
  labs(x = "Mean and SD of Slope Parameters") +
  scale_x_continuous(labels = dollar_format()) 

## Scale Parameter
ggplot() +
  geom_density(data = as_tibble(rexp(1e4, 1)), 
               aes(x = value, fill = "rate=1")) +
  geom_density(data = as_tibble(rexp(1e4, 2)), 
               aes(x = value, fill = "rate=2"), 
               alpha = 0.5) +
  theme_classic() +
  labs(x = "Mean and SD of Scale Parameter")

## Probability Parameter
ggplot() +
  geom_density(data = as_tibble(runif(1e4, 0, 1)), 
               aes(x = value, fill = "uniform")) +
  geom_density(data = as_tibble(rbeta(1e4, 2, 2)), 
               aes(x = value, fill = "beta 2"), 
               alpha = 0.5) +
    geom_density(data = as_tibble(rbeta(1e4, 1.5, 1.5)), 
               aes(x = value, fill = "beta 1.5"), 
               alpha = 0.7) +
  theme_classic() +
  labs(x = "Mean and SD of Probability Parameter")
```

### Model 

```{stan output.var = "ldrpac.model"}
data {
  int<lower = 1> n;
  real leadership_pacs[n];
  int no_corp_pacs[n];
  int new_member[n];
  real pct_white[n];
  real pct_black[n];
  real pct_latino[n];
  real pct_asian[n];
  real pct_bachelors[n];
  real pct_clinton_16[n];
  real pct_dem_house_16[n];
  real log_median_hh_income[n];
  real log_tot_voting_age[n];
}

parameters {
  real<lower = 0> a;
  real b_np;
  real b_new;
  real b_white;
  real b_black;
  real b_latino;
  real b_asian;
  real b_bach;
  real b_mhh;
  real b_clint;
  real b_house;
  real b_vpop;
  real<lower = 0> scale;
  real prob;
}

model {
  // linear model
  vector[n] mu;
  for (i in 1:n) {
    mu[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] + 
      b_white * pct_white[i] + b_black * pct_black[i] + 
      b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
      b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
      b_house * pct_dem_house_16[i] + b_mhh * log_median_hh_income[i] +
      b_vpop * log_tot_voting_age[i];
    mu[i] = exp(mu[i]); // inverse link function
  }
  
  // priors
  a ~ normal(10.5, 13);
  b_np ~ normal(0, 12);
  b_new ~ normal(0, 12);
  b_white ~ normal(0, 12);
  b_black ~ normal(0, 12);
  b_latino ~ normal(0, 12);
  b_asian ~ normal(0, 12);
  b_bach ~ normal(0, 12);
  b_clint ~ normal(0, 12);
  b_house ~ normal(0, 12);
  b_vpop ~ normal(0, 12);
  b_mhh ~ normal(0, 12);
  scale ~ exponential(2);
  prob ~ beta(1.5, 1.5);
  
  // likelihood
  for ( i in 1:n) {
    if (leadership_pacs[i] == 0)
      target += (bernoulli_lpmf(1| prob));
    else
      target += (bernoulli_lpmf(0| prob) + gamma_lpdf(leadership_pacs[i]| mu[i]/scale, 1/scale));
    }//i
}

generated quantities {
  vector[n] mu;
  
  for (i in 1:n) {
  mu[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] + 
      b_white * pct_white[i] + b_black * pct_black[i] + 
      b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
      b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
      b_house * pct_dem_house_16[i] + b_mhh * log_median_hh_income[i] +
      b_vpop * log_tot_voting_age[i];
  mu[i] = exp(mu[i]); // inverse link function
  }
}
```

```{stan output.var = "int_ldrpac.model"}
data {
  int<lower = 1> n;
  real leadership_pacs[n];
  int no_corp_pacs[n];
  int new_member[n];
  real pct_white[n];
  real pct_black[n];
  real pct_latino[n];
  real pct_asian[n];
  real pct_bachelors[n];
  real pct_clinton_16[n];
  real pct_dem_house_16[n];
  real log_median_hh_income[n];
  real log_tot_voting_age[n];
}

parameters {
  real<lower = 0> a;
  real b_np;
  real b_new;
  real b_int;
  real b_white;
  real b_black;
  real b_latino;
  real b_asian;
  real b_bach;
  real b_mhh;
  real b_clint;
  real b_house;
  real b_vpop;
  real<lower = 0> scale;
  real prob;
}

model {
  // linear model
  vector[n] mu;
  for (i in 1:n) {
    mu[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] + 
      b_int * (no_corp_pacs[i] * new_member[i]) +
      b_white * pct_white[i] + b_black * pct_black[i] + 
      b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
      b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
      b_house * pct_dem_house_16[i] + b_mhh * log_median_hh_income[i] +
      b_vpop * log_tot_voting_age[i];
    mu[i] = exp(mu[i]); // inverse link function
  }
  
  // priors
  a ~ normal(10.5, 13);
  b_np ~ normal(0, 12);
  b_new ~ normal(0, 12);
  b_int ~ normal(0, 12); 
  b_white ~ normal(0, 12);
  b_black ~ normal(0, 12);
  b_latino ~ normal(0, 12);
  b_asian ~ normal(0, 12);
  b_bach ~ normal(0, 12);
  b_clint ~ normal(0, 12);
  b_house ~ normal(0, 12);
  b_vpop ~ normal(0, 12);
  b_mhh ~ normal(0, 12);
  scale ~ exponential(2);
  prob ~ beta(1.5, 1.5);
  
  // likelihood
  for ( i in 1:n) {
    if (leadership_pacs[i] == 0)
      target += (bernoulli_lpmf(1| prob));
    else
      target += (bernoulli_lpmf(0| prob) + gamma_lpdf(leadership_pacs[i]| mu[i]/scale, 1/scale));
    }//i
}

generated quantities {
  vector[n] mu;
  
  for (i in 1:n) {
  mu[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] + 
      b_int * (no_corp_pacs[i] * new_member[i]) +
      b_white * pct_white[i] + b_black * pct_black[i] + 
      b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
      b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
      b_house * pct_dem_house_16[i] + b_mhh * log_median_hh_income[i] +
      b_vpop * log_tot_voting_age[i];
  mu[i] = exp(mu[i]); // inverse link function
  }
}
```

### Estimation

```{r}
# compose data
stan.data <- 
  estimation.data %>%
  dplyr::select(leadership_pacs, no_corp_pacs, new_member, pct_white, pct_black, 
                pct_latino, pct_asian, pct_bachelors, pct_clinton_16,
                pct_dem_house_16, log_tot_voting_age, log_median_hh_income) %>%
  mutate(no_corp_pacs = ifelse(no_corp_pacs == "YES", 1, 0),
         new_member = ifelse(new_member == "YES", 1, 0)) %>%
  drop_na() %>%
  mutate_at(.vars = vars(pct_white:log_median_hh_income), .funs = center) %>%
  compose_data()

# model estimation ------------------------------------------------------------
## Frequentist
ldr.pacs.01 <- glm(leadership_pacs ~ no_corp_pacs + new_member + pct_white + pct_black + pct_latino + pct_asian + pct_bachelors + pct_clinton_16 + pct_dem_house_16 + log_median_hh_income + log_tot_voting_age,
                   family = Gamma(link = "log"),
                   data = as.data.frame(stan.data) %>% filter(leadership_pacs != 0) %>% mutate_at(.vars = vars(pct_white:log_median_hh_income), .funs = center))

## Bayesian
ldrpac.fit <- sampling(ldrpac.model,
                       chains = 4,
                       cores = 4,
                       iter = 8000,
                       warmup = 4000,
                       data = stan.data)

traceplot(ldrpac.fit, 
          inc_warmup = TRUE, 
          pars = c("a", "b_np", "b_new", "b_white", "b_black", "b_latino", 
                   "b_asian", "b_bach", "b_clint", "b_house", "b_vpop", 
                   "b_mhh", "scale"))

tidy(ldr.pacs.01, conf.int = TRUE, conf.level = 0.89, digits = 3)
precis(ldrpac.fit, prob = 0.89, digits = 3)

post <- spread_draws(ldrpac.fit, mu[i]) %>% median_hdi()
ggplot(data = estimation.data, aes(x = leadership_pacs)) +
  geom_density(fill = "gray") +
  geom_density(data = post, aes(x = mu), fill = "skyblue", alpha = 0.7)

int_ldrpac.fit <- sampling(int_ldrpac.model,
                           chains = 4,
                           cores = 4,
                           iter = 8000,
                           warmup = 4000,
                           data = stan.data)

traceplot(int_ldrpac.fit, 
          inc_warmup = TRUE, 
          pars = c("a", "b_np", "b_new", "b_int", "b_white", "b_black", "b_latino", 
                   "b_asian", "b_bach", "b_clint", "b_house", "b_vpop", 
                   "b_mhh", "scale"))

precis(int_ldrpac.fit, prob = 0.89, digits = 3)

post <- spread_draws(int_ldrpac.fit, mu[i]) %>% median_hdi()
ggplot(data = estimation.data, aes(x = leadership_pacs)) +
  geom_density(fill = "gray") +
  geom_density(data = post, aes(x = mu), fill = "skyblue", alpha = 0.7)
```


## Model of Committee PAC Contributions

### Simulating Priors

```{r}
# likelihood simulation
ggplot() +
  geom_density(data = as_tibble(rgamma(1e4, shape = 20, rate = 100)), 
               aes(x = value)) +
  theme_classic() +
  labs(x = "Mean and SD of Slope Parameters") +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) 

# prior simulation
## Intercept
ggplot() +
  geom_density(data = as_tibble(rnorm(1e4, exp(10.5), exp(13))),
               aes(x = value, fill = "Normal")) +
  theme_classic() +
  labs(x = "Mean and SD of Intercept") +
  scale_x_continuous(labels = dollar_format()) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))

## Slope Parameters
ggplot() +
  geom_density(data = as_tibble(rnorm(1e4, exp(0), exp(12))),
               aes(x = value, fill = "normal")) +
  theme_classic() +
  labs(x = "Mean and SD of Slope Parameters") +
  scale_x_continuous(labels = dollar_format()) 

## Scale Parameter
ggplot() +
  geom_density(data = as_tibble(rexp(1e4, 1)), 
               aes(x = value, fill = "rate=1")) +
  geom_density(data = as_tibble(rexp(1e4, 2)), 
               aes(x = value, fill = "rate=2"), 
               alpha = 0.5) +
  theme_classic() +
  labs(x = "Mean and SD of Scale Parameter")

## Probability Parameter
ggplot() +
  geom_density(data = as_tibble(runif(1e4, 0, 1)), 
               aes(x = value, fill = "uniform")) +
  geom_density(data = as_tibble(rbeta(1e4, 2, 2)), 
               aes(x = value, fill = "beta 2"), 
               alpha = 0.5) +
    geom_density(data = as_tibble(rbeta(1e4, 1.5, 1.5)), 
               aes(x = value, fill = "beta 1.5"), 
               alpha = 0.7) +
  theme_classic() +
  labs(x = "Mean and SD of Probability Parameter")
```

### Model 

```{stan output.var = "cmtpac.model"}
data {
  int<lower = 1> n;
  real dir_pac_cand_committee[n];
  int no_corp_pacs[n];
  int new_member[n];
  real pct_white[n];
  real pct_black[n];
  real pct_latino[n];
  real pct_asian[n];
  real pct_bachelors[n];
  real pct_clinton_16[n];
  real pct_dem_house_16[n];
  real log_median_hh_income[n];
  real log_tot_voting_age[n];
}

parameters {
  real<lower = 0> a;
  real b_np;
  real b_new;
  real b_white;
  real b_black;
  real b_latino;
  real b_asian;
  real b_bach;
  real b_mhh;
  real b_clint;
  real b_house;
  real b_vpop;
  real<lower = 0> scale;
  real prob;
}

model {
  // linear model
  vector[n] mu;
  for (i in 1:n) {
    mu[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] + 
      b_white * pct_white[i] + b_black * pct_black[i] + 
      b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
      b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
      b_house * pct_dem_house_16[i] + b_mhh * log_median_hh_income[i] +
      b_vpop * log_tot_voting_age[i];
    mu[i] = exp(mu[i]); // inverse link function
  }
  
  // priors
  a ~ normal(10.5, 13);
  b_np ~ normal(0, 12);
  b_new ~ normal(0, 12);
  b_white ~ normal(0, 12);
  b_black ~ normal(0, 12);
  b_latino ~ normal(0, 12);
  b_asian ~ normal(0, 12);
  b_bach ~ normal(0, 12);
  b_clint ~ normal(0, 12);
  b_house ~ normal(0, 12);
  b_vpop ~ normal(0, 12);
  b_mhh ~ normal(0, 12);
  scale ~ exponential(2);
  prob ~ beta(1.5, 1.5);
  
  // likelihood
  for ( i in 1:n) {
    if (dir_pac_cand_committee[i] == 0)
      target += (bernoulli_lpmf(1| prob));
    else
      target += (bernoulli_lpmf(0| prob) + gamma_lpdf(dir_pac_cand_committee[i]| mu[i]/scale, 1/scale));
    }//i
}

generated quantities {
  vector[n] mu;
  
  for (i in 1:n) {
  mu[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] + 
      b_white * pct_white[i] + b_black * pct_black[i] + 
      b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
      b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
      b_house * pct_dem_house_16[i] + b_mhh * log_median_hh_income[i] +
      b_vpop * log_tot_voting_age[i];
  mu[i] = exp(mu[i]); // inverse link function
  }
}
```

```{stan output.var = "int_cmtpac.model"}
data {
  int<lower = 1> n;
  real dir_pac_cand_committee[n];
  int no_corp_pacs[n];
  int new_member[n];
  real pct_white[n];
  real pct_black[n];
  real pct_latino[n];
  real pct_asian[n];
  real pct_bachelors[n];
  real pct_clinton_16[n];
  real pct_dem_house_16[n];
  real log_median_hh_income[n];
  real log_tot_voting_age[n];
}

parameters {
  real<lower = 0> a;
  real b_np;
  real b_new;
  real b_int;
  real b_white;
  real b_black;
  real b_latino;
  real b_asian;
  real b_bach;
  real b_mhh;
  real b_clint;
  real b_house;
  real b_vpop;
  real<lower = 0> scale;
  real prob;
}

model {
  // linear model
  vector[n] mu;
  for (i in 1:n) {
    mu[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] +
      b_int * (no_corp_pacs[i] * new_member[i]) +
      b_white * pct_white[i] + b_black * pct_black[i] + 
      b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
      b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
      b_house * pct_dem_house_16[i] + b_mhh * log_median_hh_income[i] +
      b_vpop * log_tot_voting_age[i];
    mu[i] = exp(mu[i]); // inverse link function
  }
  
  // priors
  a ~ normal(10.5, 13);
  b_np ~ normal(0, 12);
  b_new ~ normal(0, 12);
  b_int ~ normal(0, 12);
  b_white ~ normal(0, 12);
  b_black ~ normal(0, 12);
  b_latino ~ normal(0, 12);
  b_asian ~ normal(0, 12);
  b_bach ~ normal(0, 12);
  b_clint ~ normal(0, 12);
  b_house ~ normal(0, 12);
  b_vpop ~ normal(0, 12);
  b_mhh ~ normal(0, 12);
  scale ~ exponential(2);
  prob ~ beta(1.5, 1.5);
  
  // likelihood
  for ( i in 1:n) {
    if (dir_pac_cand_committee[i] == 0)
      target += (bernoulli_lpmf(1| prob));
    else
      target += (bernoulli_lpmf(0| prob) + gamma_lpdf(dir_pac_cand_committee[i]| mu[i]/scale, 1/scale));
    }//i
}

generated quantities {
  vector[n] mu;
  
  for (i in 1:n) {
  mu[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] +
      b_int * (no_corp_pacs[i] * new_member[i]) +
      b_white * pct_white[i] + b_black * pct_black[i] + 
      b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
      b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
      b_house * pct_dem_house_16[i] + b_mhh * log_median_hh_income[i] +
      b_vpop * log_tot_voting_age[i];
  mu[i] = exp(mu[i]); // inverse link function
  }
}
```

### Estimation

```{r}
# compose data
stan.data <- 
  estimation.data %>%
  dplyr::select(dir_pac_cand_committee, no_corp_pacs, new_member, pct_white, pct_black, 
                pct_latino, pct_asian, pct_bachelors, pct_clinton_16,
                pct_dem_house_16, log_tot_voting_age, log_median_hh_income) %>%
  mutate(no_corp_pacs = ifelse(no_corp_pacs == "YES", 1, 0),
         new_member = ifelse(new_member == "YES", 1, 0)) %>%
  drop_na() %>%
  mutate_at(.vars = vars(pct_white:log_median_hh_income), .funs = center) %>%
  compose_data()

# model estimation ------------------------------------------------------------
## Frequentist
cmte.pacs.01 <- glm(dir_pac_cand_committee ~ no_corp_pacs + new_member + pct_white + pct_black + pct_latino + pct_asian + pct_bachelors + pct_clinton_16 + pct_dem_house_16 + log_median_hh_income + log_tot_voting_age,
                     family = Gamma(link = "log"),
                     data = as.data.frame(stan.data) %>% filter(dir_pac_cand_committee != 0) %>% mutate_at(.vars = vars(pct_white:log_median_hh_income), .funs = center))

## Bayesian
cmtpac.fit <- sampling(cmtpac.model,
                       chains = 4,
                       cores = 4,
                       iter = 8000,
                       warmup = 4000,
                       data = stan.data)

traceplot(cmtpac.fit, 
          inc_warmup = TRUE, 
          pars = c("a", "b_np", "b_new", "b_white", "b_black", "b_latino", 
                   "b_asian", "b_bach", "b_clint", "b_house", "b_vpop", 
                   "b_mhh", "scale"))

tidy(cmte.pacs.01, conf.int = TRUE, conf.level = 0.89, digits = 3)
precis(cmtpac.fit, prob = 0.89, digits = 3)

post <- spread_draws(cmtpac.fit, mu[i]) %>% median_hdi()
ggplot(data = estimation.data, aes(x = dir_pac_cand_committee)) +
  geom_density(fill = "gray") +
  geom_density(data = post, aes(x = mu), fill = "skyblue", alpha = 0.7)

int_cmtpac.fit <- sampling(int_cmtpac.model,
                           chains = 4,
                           cores = 4,
                           iter = 8000,
                           warmup = 4000,
                           data = stan.data)

traceplot(int_cmtpac.fit, 
          inc_warmup = TRUE, 
          pars = c("a", "b_np", "b_new", "b_int", "b_white", "b_black", "b_latino", 
                   "b_asian", "b_bach", "b_clint", "b_house", "b_vpop", 
                   "b_mhh", "scale"))

precis(int_cmtpac.fit, prob = 0.89, digits = 3)

post <- spread_draws(int_cmtpac.fit, mu[i]) %>% median_hdi()
ggplot(data = estimation.data, aes(x = dir_pac_cand_committee)) +
  geom_density(fill = "gray") +
  geom_density(data = post, aes(x = mu), fill = "skyblue", alpha = 0.7)
```

## Model of Party Contributions

### Simulating Priors

```{r}
# likelihood simulation
ggplot() +
  geom_density(data = as_tibble(rgamma(1e4, shape = 20, rate = 100)), 
               aes(x = value)) +
  theme_classic() +
  labs(x = "Mean and SD of Slope Parameters") +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) 

# prior simulation
## Intercept
ggplot() +
  geom_density(data = as_tibble(rnorm(1e4, exp(12), exp(14))),
               aes(x = value, fill = "Normal")) +
  theme_classic() +
  labs(x = "Mean and SD of Intercept") +
  scale_x_continuous(labels = dollar_format()) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))

## Slope Parameters
ggplot() +
  geom_density(data = as_tibble(rnorm(1e4, exp(0), exp(13))),
               aes(x = value, fill = "normal")) +
  theme_classic() +
  labs(x = "Mean and SD of Slope Parameters") +
  scale_x_continuous(labels = dollar_format()) 

## Scale Parameter
ggplot() +
  geom_density(data = as_tibble(rexp(1e4, 1)), 
               aes(x = value, fill = "rate=1")) +
  geom_density(data = as_tibble(rexp(1e4, 2)), 
               aes(x = value, fill = "rate=2"), 
               alpha = 0.5) +
  theme_classic() +
  labs(x = "Mean and SD of Scale Parameter")

## Probability Parameter
ggplot() +
  geom_density(data = as_tibble(runif(1e4, 0, 1)), 
               aes(x = value, fill = "uniform")) +
  geom_density(data = as_tibble(rbeta(1e4, 2, 2)), 
               aes(x = value, fill = "beta 2"), 
               alpha = 0.5) +
    geom_density(data = as_tibble(rbeta(1e4, 1.5, 1.5)), 
               aes(x = value, fill = "beta 1.5"), 
               alpha = 0.7) +
  theme_classic() +
  labs(x = "Mean and SD of Probability Parameter")
```

### Model 

```{stan output.var = "prtypac.model"}
data {
  int<lower = 1> n;
  real dir_pac_party_committee[n];
  int no_corp_pacs[n];
  int new_member[n];
  real pct_white[n];
  real pct_black[n];
  real pct_latino[n];
  real pct_asian[n];
  real pct_bachelors[n];
  real pct_clinton_16[n];
  real pct_dem_house_16[n];
  real log_median_hh_income[n];
  real log_tot_voting_age[n];
}

parameters {
  real<lower = 0> a;
  real b_np;
  real b_new;
  real b_white;
  real b_black;
  real b_latino;
  real b_asian;
  real b_bach;
  real b_mhh;
  real b_clint;
  real b_house;
  real b_vpop;
  real<lower = 0> scale;
  real prob;
}

model {
  // linear model
  vector[n] mu;
  for (i in 1:n) {
    mu[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] + 
      b_white * pct_white[i] + b_black * pct_black[i] + 
      b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
      b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
      b_house * pct_dem_house_16[i] + b_mhh * log_median_hh_income[i] +
      b_vpop * log_tot_voting_age[i];
    mu[i] = exp(mu[i]); // inverse link function
  }
  
  // priors
  a ~ normal(12, 14);
  b_np ~ normal(0, 13);
  b_new ~ normal(0, 13);
  b_white ~ normal(0, 13);
  b_black ~ normal(0, 13);
  b_latino ~ normal(0, 13);
  b_asian ~ normal(0, 13);
  b_bach ~ normal(0, 13);
  b_clint ~ normal(0, 13);
  b_house ~ normal(0, 13);
  b_vpop ~ normal(0, 13);
  b_mhh ~ normal(0, 13);
  scale ~ exponential(2);
  prob ~ beta(1.5, 1.5);
  
  // likelihood
  for ( i in 1:n) {
    if (dir_pac_party_committee[i] == 0)
      target += (bernoulli_lpmf(1| prob));
    else
      target += (bernoulli_lpmf(0| prob) + gamma_lpdf(dir_pac_party_committee[i]| mu[i]/scale, 1/scale));
    }//i
}

generated quantities {
  vector[n] mu;
  
  for (i in 1:n) {
  mu[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] + 
      b_white * pct_white[i] + b_black * pct_black[i] + 
      b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
      b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
      b_house * pct_dem_house_16[i] + b_mhh * log_median_hh_income[i] +
      b_vpop * log_tot_voting_age[i];
  mu[i] = exp(mu[i]); // inverse link function
  }
}
```

```{stan output.var = "int_prtypac.model"}
data {
  int<lower = 1> n;
  real dir_pac_party_committee[n];
  int no_corp_pacs[n];
  int new_member[n];
  real pct_white[n];
  real pct_black[n];
  real pct_latino[n];
  real pct_asian[n];
  real pct_bachelors[n];
  real pct_clinton_16[n];
  real pct_dem_house_16[n];
  real log_median_hh_income[n];
  real log_tot_voting_age[n];
}

parameters {
  real<lower = 0> a;
  real b_np;
  real b_new;
  real b_int;
  real b_white;
  real b_black;
  real b_latino;
  real b_asian;
  real b_bach;
  real b_mhh;
  real b_clint;
  real b_house;
  real b_vpop;
  real<lower = 0> scale;
  real prob;
}

model {
  // linear model
  vector[n] mu;
  for (i in 1:n) {
    mu[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] +
      b_int * (no_corp_pacs[i] * new_member[i]) +
      b_white * pct_white[i] + b_black * pct_black[i] + 
      b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
      b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
      b_house * pct_dem_house_16[i] + b_mhh * log_median_hh_income[i] +
      b_vpop * log_tot_voting_age[i];
    mu[i] = exp(mu[i]); // inverse link function
  }
  
  // priors
  a ~ normal(12, 14);
  b_np ~ normal(0, 13);
  b_new ~ normal(0, 13);
  b_int ~ normal(0, 13);
  b_white ~ normal(0, 13);
  b_black ~ normal(0, 13);
  b_latino ~ normal(0, 13);
  b_asian ~ normal(0, 13);
  b_bach ~ normal(0, 13);
  b_clint ~ normal(0, 13);
  b_house ~ normal(0, 13);
  b_vpop ~ normal(0, 13);
  b_mhh ~ normal(0, 13);
  scale ~ exponential(2);
  prob ~ beta(1.5, 1.5);
  
  // likelihood
  for ( i in 1:n) {
    if (dir_pac_party_committee[i] == 0)
      target += (bernoulli_lpmf(1| prob));
    else
      target += (bernoulli_lpmf(0| prob) + gamma_lpdf(dir_pac_party_committee[i]| mu[i]/scale, 1/scale));
    }//i
}

generated quantities {
  vector[n] mu;
  
  for (i in 1:n) {
  mu[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] +
      b_int * (no_corp_pacs[i] * new_member[i]) +
      b_white * pct_white[i] + b_black * pct_black[i] + 
      b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
      b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
      b_house * pct_dem_house_16[i] + b_mhh * log_median_hh_income[i] +
      b_vpop * log_tot_voting_age[i];
  mu[i] = exp(mu[i]); // inverse link function
  }
}
```

### Estimation

```{r}
# compose data
stan.data <- 
  estimation.data %>%
  dplyr::select(dir_pac_party_committee, no_corp_pacs, new_member, pct_white, pct_black, 
                pct_latino, pct_asian, pct_bachelors, pct_clinton_16,
                pct_dem_house_16, log_tot_voting_age, log_median_hh_income) %>%
  mutate(no_corp_pacs = ifelse(no_corp_pacs == "YES", 1, 0),
         new_member = ifelse(new_member == "YES", 1, 0)) %>%
  drop_na() %>%
  mutate_at(.vars = vars(pct_white:log_median_hh_income), .funs = center) %>%
  compose_data()

# model estimation ------------------------------------------------------------
## Frequentist
party.contribs.01 <- glm(dir_pac_party_committee ~ no_corp_pacs + new_member + pct_white + pct_black + pct_latino + pct_asian + pct_bachelors + pct_clinton_16 + pct_dem_house_16 + log_median_hh_income + log_tot_voting_age,
                     family = Gamma(link = "log"),
                     data = as.data.frame(stan.data) %>% filter(dir_pac_party_committee != 0) %>% mutate_at(.vars = vars(pct_white:log_median_hh_income), .funs = center))

## Bayesian
prtypac.fit <- sampling(prtypac.model,
                        chains = 4,
                        cores = 4,
                        iter = 8000,
                        warmup = 4000,
                        data = stan.data)

traceplot(prtypac.fit, 
          inc_warmup = TRUE, 
          pars = c("a", "b_np", "b_new", "b_white", "b_black", "b_latino", 
                   "b_asian", "b_bach", "b_clint", "b_house", "b_vpop", 
                   "b_mhh", "scale"))

tidy(party.contribs.01, conf.int = TRUE, conf.level = 0.89, digits = 3)
precis(prtypac.fit, prob = 0.89, digits = 3)

post <- spread_draws(prtypac.fit, mu[i]) %>% median_hdi()
ggplot(data = estimation.data, aes(x = dir_pac_party_committee)) +
  geom_density(fill = "gray") +
  geom_density(data = post, aes(x = mu), fill = "skyblue", alpha = 0.7)

int_prtypac.fit <- sampling(int_prtypac.model,
                            chains = 4,
                            cores = 4,
                            iter = 8000,
                            warmup = 4000,
                            data = stan.data)

traceplot(int_prtypac.fit, 
          inc_warmup = TRUE, 
          pars = c("a", "b_np", "b_new", "b_int", "b_white", "b_black", "b_latino", 
                   "b_asian", "b_bach", "b_clint", "b_house", "b_vpop", 
                   "b_mhh", "scale"))

precis(int_prtypac.fit, prob = 0.89, digits = 3)

post <- spread_draws(int_prtypac.fit, mu[i]) %>% median_hdi()
ggplot(data = estimation.data, aes(x = dir_pac_party_committee)) +
  geom_density(fill = "gray") +
  geom_density(data = post, aes(x = mu), fill = "skyblue", alpha = 0.7)
```


## Model of Self-finance Contributions

### Simulating Priors

```{r}
# likelihood simulation
ggplot() +
  geom_density(data = as_tibble(rgamma(1e4, shape = 20, rate = 100)), 
               aes(x = value)) +
  theme_classic() +
  labs(x = "Mean and SD of Slope Parameters") +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) 

# prior simulation
## Intercept
ggplot() +
  geom_density(data = as_tibble(rnorm(1e4, exp(10), exp(11))),
               aes(x = value, fill = "Normal")) +
  theme_classic() +
  labs(x = "Mean and SD of Intercept") +
  scale_x_continuous(labels = dollar_format()) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))

## Slope Parameters
ggplot() +
  geom_density(data = as_tibble(rnorm(1e4, exp(0), exp(11))),
               aes(x = value, fill = "normal")) +
  theme_classic() +
  labs(x = "Mean and SD of Slope Parameters") +
  scale_x_continuous(labels = dollar_format()) 

## Scale Parameter
ggplot() +
  geom_density(data = as_tibble(rexp(1e4, 1)), 
               aes(x = value, fill = "rate=1")) +
  geom_density(data = as_tibble(rexp(1e4, 2)), 
               aes(x = value, fill = "rate=2"), 
               alpha = 0.5) +
  theme_classic() +
  labs(x = "Mean and SD of Scale Parameter")

## Probability Parameter
ggplot() +
  geom_density(data = as_tibble(runif(1e4, 0, 1)), 
               aes(x = value, fill = "uniform")) +
  geom_density(data = as_tibble(rbeta(1e4, 2, 2)), 
               aes(x = value, fill = "beta 2"), 
               alpha = 0.5) +
    geom_density(data = as_tibble(rbeta(1e4, 1.5, 1.5)), 
               aes(x = value, fill = "beta 1.5"), 
               alpha = 0.7) +
  theme_classic() +
  labs(x = "Mean and SD of Probability Parameter")
```

### Model 

```{stan output.var = "slffin.model"}
data {
  int<lower = 1> n;
  real indiv_self_finance[n];
  int no_corp_pacs[n];
  int new_member[n];
  real pct_white[n];
  real pct_black[n];
  real pct_latino[n];
  real pct_asian[n];
  real pct_bachelors[n];
  real pct_clinton_16[n];
  real pct_dem_house_16[n];
  real log_median_hh_income[n];
  real log_tot_voting_age[n];
}

parameters {
  real<lower = 0> a;
  real b_np;
  real b_new;
  real b_white;
  real b_black;
  real b_latino;
  real b_asian;
  real b_bach;
  real b_mhh;
  real b_clint;
  real b_house;
  real b_vpop;
  real<lower = 0> scale;
  real<lower = 0, upper = 1> prob;
}

model {
  // linear model
  vector[n] mu;
  for (i in 1:n) {
    mu[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] + 
      b_white * pct_white[i] + b_black * pct_black[i] + 
      b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
      b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
      b_house * pct_dem_house_16[i] + b_mhh * log_median_hh_income[i] +
      b_vpop * log_tot_voting_age[i];
    mu[i] = exp(mu[i]); // inverse link function
  }
  
  // priors
  a ~ normal(10, 11);
  b_np ~ normal(0, 11);
  b_new ~ normal(0, 11);
  b_white ~ normal(0, 11);
  b_black ~ normal(0, 11);
  b_latino ~ normal(0, 11);
  b_asian ~ normal(0, 11);
  b_bach ~ normal(0, 11);
  b_clint ~ normal(0, 11);
  b_house ~ normal(0, 11);
  b_vpop ~ normal(0, 11);
  b_mhh ~ normal(0, 11);
  scale ~ exponential(2);
  prob ~ beta(1.5, 1.5);
  
  // likelihood
  for ( i in 1:n) {
    if (indiv_self_finance[i] == 0)
      target += (bernoulli_lpmf(1| prob));
    else
      target += (bernoulli_lpmf(0| prob) + gamma_lpdf(indiv_self_finance[i]| mu[i]/scale, 1/scale));
    }//i
}

generated quantities {
  vector[n] mu;
  
  for (i in 1:n) {
  mu[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] + 
      b_white * pct_white[i] + b_black * pct_black[i] + 
      b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
      b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
      b_house * pct_dem_house_16[i] + b_mhh * log_median_hh_income[i] +
      b_vpop * log_tot_voting_age[i];
  mu[i] = exp(mu[i]); // inverse link function
  }
}
```

```{stan output.var = "int_slffin.model"}
data {
  int<lower = 1> n;
  real indiv_self_finance[n];
  int no_corp_pacs[n];
  int new_member[n];
  real pct_white[n];
  real pct_black[n];
  real pct_latino[n];
  real pct_asian[n];
  real pct_bachelors[n];
  real pct_clinton_16[n];
  real pct_dem_house_16[n];
  real log_median_hh_income[n];
  real log_tot_voting_age[n];
}

parameters {
  real<lower = 0> a;
  real b_np;
  real b_new;
  real b_int;
  real b_white;
  real b_black;
  real b_latino;
  real b_asian;
  real b_bach;
  real b_mhh;
  real b_clint;
  real b_house;
  real b_vpop;
  real<lower = 0> scale;
  real<lower = 0, upper = 1> prob;
}

model {
  // linear model
  vector[n] mu;
  for (i in 1:n) {
    mu[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] +
      b_int * (no_corp_pacs[i] * new_member[i]) +
      b_white * pct_white[i] + b_black * pct_black[i] + 
      b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
      b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
      b_house * pct_dem_house_16[i] + b_mhh * log_median_hh_income[i] +
      b_vpop * log_tot_voting_age[i];
    mu[i] = exp(mu[i]); // inverse link function
  }
  
  // priors
  a ~ normal(10, 11);
  b_np ~ normal(0, 11);
  b_new ~ normal(0, 11);
  b_int ~ normal(0, 11);
  b_white ~ normal(0, 11);
  b_black ~ normal(0, 11);
  b_latino ~ normal(0, 11);
  b_asian ~ normal(0, 11);
  b_bach ~ normal(0, 11);
  b_clint ~ normal(0, 11);
  b_house ~ normal(0, 11);
  b_vpop ~ normal(0, 11);
  b_mhh ~ normal(0, 11);
  scale ~ exponential(2);
  prob ~ beta(1.5, 1.5);
  
  // likelihood
  for ( i in 1:n) {
    if (indiv_self_finance[i] == 0)
      target += (bernoulli_lpmf(1| prob));
    else
      target += (bernoulli_lpmf(0| prob) + gamma_lpdf(indiv_self_finance[i]| mu[i]/scale, 1/scale));
    }//i
}

generated quantities {
  vector[n] mu;
  
  for (i in 1:n) {
  mu[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] +
      b_int * (no_corp_pacs[i] * new_member[i]) +
      b_white * pct_white[i] + b_black * pct_black[i] + 
      b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
      b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
      b_house * pct_dem_house_16[i] + b_mhh * log_median_hh_income[i] +
      b_vpop * log_tot_voting_age[i];
  mu[i] = exp(mu[i]); // inverse link function
  }
}
```

### Estimation

```{r}
# compose data
stan.data <- 
  estimation.data %>%
  dplyr::select(indiv_self_finance, no_corp_pacs, new_member, pct_white, pct_black, 
                pct_latino, pct_asian, pct_bachelors, pct_clinton_16,
                pct_dem_house_16, log_tot_voting_age, log_median_hh_income) %>%
  mutate(no_corp_pacs = ifelse(no_corp_pacs == "YES", 1, 0),
         new_member = ifelse(new_member == "YES", 1, 0)) %>%
  drop_na() %>%
  mutate_at(.vars = vars(pct_white:log_median_hh_income), .funs = center) %>%
  compose_data()

# model estimation ------------------------------------------------------------
## Frequentist
self.contribs.01 <- glm(indiv_self_finance ~ no_corp_pacs + new_member + pct_white + pct_black + pct_latino + pct_asian + pct_bachelors + pct_clinton_16 + pct_dem_house_16 + log_median_hh_income + log_tot_voting_age,
                     family = Gamma(link = "log"),
                     data = as.data.frame(stan.data) %>% filter(indiv_self_finance != 0) %>% mutate_at(.vars = vars(pct_white:log_median_hh_income), .funs = center))

## Bayesian
slffin.fit <- sampling(slffin.model,
                       chains = 4,
                       cores = 4,
                       iter = 12000,
                       warmup = 6000,
                       data = stan.data)

traceplot(slffin.fit, 
          inc_warmup = TRUE, 
          pars = c("a", "b_np", "b_new", "b_white", "b_black", "b_latino", 
                   "b_asian", "b_bach", "b_clint", "b_house", "b_vpop", 
                   "b_mhh", "scale"))

#tidy(self.contribs.01, conf.int = TRUE, conf.level = 0.89, digits = 3)
precis(slffin.fit, prob = 0.89, digits = 3)

post <- spread_draws(slffin.fit, mu[i]) %>% median_hdi()
ggplot(data = estimation.data, aes(x = indiv_self_finance)) +
  geom_density(fill = "gray") +
  geom_density(data = post, aes(x = mu), fill = "skyblue", alpha = 0.7) +
  xlim(0, 100)

int_slffin.fit <- sampling(int_slffin.model,
                           chains = 4,
                           cores = 4,
                           iter = 12000,
                           warmup = 6000,
                           data = stan.data)

traceplot(int_slffin.fit, 
          inc_warmup = TRUE, 
          pars = c("a", "b_np", "b_new", "b_int", "b_white", "b_black", "b_latino", 
                   "b_asian", "b_bach", "b_clint", "b_house", "b_vpop", 
                   "b_mhh", "scale"))

precis(int_slffin.fit, prob = 0.89, digits = 3)

post <- spread_draws(int_slffin.fit, mu[i]) %>% median_hdi()
ggplot(data = estimation.data, aes(x = indiv_self_finance)) +
  geom_density(fill = "gray") +
  geom_density(data = post, aes(x = mu), fill = "skyblue", alpha = 0.7) +
  xlim(0, 100)
```


## Model of Contributions from other Candidates

### Simulating Priors

```{r}
# likelihood simulation
ggplot() +
  geom_density(data = as_tibble(rgamma(1e4, shape = 20, rate = 100)), 
               aes(x = value)) +
  theme_classic() +
  labs(x = "Mean and SD of Slope Parameters") +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) 

# prior simulation
## Intercept
ggplot() +
  geom_density(data = as_tibble(rnorm(1e4, exp(8), exp(10))),
               aes(x = value, fill = "Normal")) +
  theme_classic() +
  labs(x = "Mean and SD of Intercept") +
  scale_x_continuous(labels = dollar_format()) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))

## Slope Parameters
ggplot() +
  geom_density(data = as_tibble(rnorm(1e4, exp(0), exp(10))),
               aes(x = value, fill = "normal")) +
  theme_classic() +
  labs(x = "Mean and SD of Slope Parameters") +
  scale_x_continuous(labels = dollar_format()) 

## Scale Parameter
ggplot() +
  geom_density(data = as_tibble(rexp(1e4, 1)), 
               aes(x = value, fill = "rate=1")) +
  geom_density(data = as_tibble(rexp(1e4, 2)), 
               aes(x = value, fill = "rate=2"), 
               alpha = 0.5) +
  theme_classic() +
  labs(x = "Mean and SD of Scale Parameter")

## Probability Parameter
ggplot() +
  geom_density(data = as_tibble(runif(1e4, 0, 1)), 
               aes(x = value, fill = "uniform")) +
  geom_density(data = as_tibble(rbeta(1e4, 1, 2)), 
               aes(x = value, fill = "beta 2"), 
               alpha = 0.5) +
    geom_density(data = as_tibble(rbeta(1e4, 1.5, 1.5)), 
               aes(x = value, fill = "beta 1.5"), 
               alpha = 0.7) +
  theme_classic() +
  labs(x = "Mean and SD of Probability Parameter")
```

### Model 

```{stan output.var = "candcontribs.model"}
data {
  int<lower = 1> n;
  real candidate_contribs[n];
  int no_corp_pacs[n];
  int new_member[n];
  real pct_white[n];
  real pct_black[n];
  real pct_latino[n];
  real pct_asian[n];
  real pct_bachelors[n];
  real pct_clinton_16[n];
  real pct_dem_house_16[n];
  real log_median_hh_income[n];
  real log_tot_voting_age[n];
}

parameters {
  real<lower = 0> a;
  real b_np;
  real b_new;
  real b_white;
  real b_black;
  real b_latino;
  real b_asian;
  real b_bach;
  real b_mhh;
  real b_clint;
  real b_house;
  real b_vpop;
  real<lower = 0> scale;
  real<lower = 0, upper = 1> prob;
}

model {
  // linear model
  vector[n] mu;
  for (i in 1:n) {
    mu[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] +
      b_white * pct_white[i] + b_black * pct_black[i] + 
      b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
      b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
      b_house * pct_dem_house_16[i] + b_mhh * log_median_hh_income[i] +
      b_vpop * log_tot_voting_age[i];
    mu[i] = exp(mu[i]); // inverse link function
  }
  
  // priors
  a ~ normal(8, 10);
  b_np ~ normal(0, 10);
  b_new ~ normal(0, 10);
  b_white ~ normal(0, 10);
  b_black ~ normal(0, 10);
  b_latino ~ normal(0, 10);
  b_asian ~ normal(0, 10);
  b_bach ~ normal(0, 10);
  b_clint ~ normal(0, 10);
  b_house ~ normal(0, 10);
  b_vpop ~ normal(0, 10);
  b_mhh ~ normal(0, 10);
  scale ~ exponential(2);
  prob ~ beta(1.5, 1.5);
  
  // likelihood
  for ( i in 1:n) {
    if (candidate_contribs[i] == 0)
      target += (bernoulli_lpmf(1| prob));
    else
      target += (bernoulli_lpmf(0| prob) + gamma_lpdf(candidate_contribs[i]| mu[i]/scale, 1/scale));
    }//i
}

generated quantities {
  vector[n] mu;
  
  for (i in 1:n) {
  mu[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] + 
      b_white * pct_white[i] + b_black * pct_black[i] + 
      b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
      b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
      b_house * pct_dem_house_16[i] + b_mhh * log_median_hh_income[i] +
      b_vpop * log_tot_voting_age[i];
  mu[i] = exp(mu[i]); // inverse link function
  }
}
```

```{stan output.var = "int_candcontribs.model"}
data {
  int<lower = 1> n;
  real candidate_contribs[n];
  int no_corp_pacs[n];
  int new_member[n];
  real pct_white[n];
  real pct_black[n];
  real pct_latino[n];
  real pct_asian[n];
  real pct_bachelors[n];
  real pct_clinton_16[n];
  real pct_dem_house_16[n];
  real log_median_hh_income[n];
  real log_tot_voting_age[n];
}

parameters {
  real<lower = 0> a;
  real b_np;
  real b_new;
  real b_int;
  real b_white;
  real b_black;
  real b_latino;
  real b_asian;
  real b_bach;
  real b_mhh;
  real b_clint;
  real b_house;
  real b_vpop;
  real<lower = 0> scale;
  real<lower = 0, upper = 1> prob;
}

model {
  // linear model
  vector[n] mu;
  for (i in 1:n) {
    mu[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] +
      b_int * (no_corp_pacs[i] * new_member[i]) +
      b_white * pct_white[i] + b_black * pct_black[i] + 
      b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
      b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
      b_house * pct_dem_house_16[i] + b_mhh * log_median_hh_income[i] +
      b_vpop * log_tot_voting_age[i];
    mu[i] = exp(mu[i]); // inverse link function
  }
  
  // priors
  a ~ normal(8, 10);
  b_np ~ normal(0, 10);
  b_new ~ normal(0, 10);
  b_int ~ normal(0, 10);
  b_white ~ normal(0, 10);
  b_black ~ normal(0, 10);
  b_latino ~ normal(0, 10);
  b_asian ~ normal(0, 10);
  b_bach ~ normal(0, 10);
  b_clint ~ normal(0, 10);
  b_house ~ normal(0, 10);
  b_vpop ~ normal(0, 10);
  b_mhh ~ normal(0, 10);
  scale ~ exponential(2);
  prob ~ beta(1.5, 1.5);
  
  // likelihood
  for ( i in 1:n) {
    if (candidate_contribs[i] == 0)
      target += (bernoulli_lpmf(1| prob));
    else
      target += (bernoulli_lpmf(0| prob) + gamma_lpdf(candidate_contribs[i]| mu[i]/scale, 1/scale));
    }//i
}

generated quantities {
  vector[n] mu;
  
  for (i in 1:n) {
  mu[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] +
      b_int * (no_corp_pacs[i] * new_member[i]) +
      b_white * pct_white[i] + b_black * pct_black[i] + 
      b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
      b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
      b_house * pct_dem_house_16[i] + b_mhh * log_median_hh_income[i] +
      b_vpop * log_tot_voting_age[i];
  mu[i] = exp(mu[i]); // inverse link function
  }
}
```

### Estimation

```{r}
# compose data
stan.data <- 
  estimation.data %>%
  dplyr::select(candidate_contribs, no_corp_pacs, new_member, pct_white, pct_black, 
                pct_latino, pct_asian, pct_bachelors, pct_clinton_16,
                pct_dem_house_16, log_tot_voting_age, log_median_hh_income) %>%
  mutate(no_corp_pacs = ifelse(no_corp_pacs == "YES", 1, 0),
         new_member = ifelse(new_member == "YES", 1, 0)) %>%
  drop_na() %>%
  mutate_at(.vars = vars(pct_white:log_median_hh_income), .funs = center) %>%
  compose_data()

# model estimation ------------------------------------------------------------
## Frequentist
# cand.contribs.01 <- glm(candidate_contribs ~ no_corp_pacs + new_member + pct_white + pct_black + pct_latino + pct_asian + pct_bachelors + pct_clinton_16 + pct_dem_house_16 + log_median_hh_income + log_tot_voting_age,
#                         family = Gamma(link = "log"),
#                         data = as.data.frame(stan.data) %>% filter(candidate_contribs != 0) %>% mutate_at(.vars = vars(pct_white:log_median_hh_income), .funs = center))

## Bayesian
candcontribs.fit <- sampling(candcontribs.model,
                             chains = 4,
                             cores = 4,
                             iter = 20000,
                             warmup = 10000,
                             data = stan.data)

traceplot(candcontribs.fit, 
          inc_warmup = TRUE, 
          pars = c("a", "b_np", "b_new", "b_white", "b_black", "b_latino", 
                   "b_asian", "b_bach", "b_clint", "b_house", "b_vpop", 
                   "b_mhh", "scale"))

#tidy(cand.contribs.01, conf.int = TRUE, conf.level = 0.89, digits = 3)
precis(candcontribs.fit, prob = 0.89, digits = 3)

post <- spread_draws(candcontribs.fit, mu[i]) %>% median_hdi()
ggplot(data = estimation.data, aes(x = candidate_contribs)) +
  geom_density(fill = "gray") +
  geom_density(data = post, aes(x = mu), fill = "skyblue", alpha = 0.7) +
  xlim(0, 100)

int_candcontribs.fit <- sampling(int_candcontribs.model,
                                 chains = 4,
                                 cores = 4,
                                 iter = 20000,
                                 warmup = 10000,
                                 data = stan.data)

traceplot(int_candcontribs.fit, 
          inc_warmup = TRUE, 
          pars = c("a", "b_np", "b_new", "b_int", "b_white", "b_black", "b_latino", 
                   "b_asian", "b_bach", "b_clint", "b_house", "b_vpop", 
                   "b_mhh", "scale"))

#tidy(cand.contribs.01, conf.int = TRUE, conf.level = 0.89, digits = 3)
precis(int_candcontribs.fit, prob = 0.89, digits = 3)

post <- spread_draws(int_candcontribs.fit, mu[i]) %>% median_hdi()
ggplot(data = estimation.data, aes(x = candidate_contribs)) +
  geom_density(fill = "gray") +
  geom_density(data = post, aes(x = mu), fill = "skyblue", alpha = 0.7) +
  xlim(0, 100)
```


# Individual Models

## Model of Small Individual Contributions

### Simulating Priors

```{r}
# likelihood simulation
ggplot() +
  geom_density(data = as_tibble(rgamma(1e4, shape = 20, rate = 100)), 
               aes(x = value)) +
  theme_classic() +
  labs(x = "Mean and SD of Slope Parameters") +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) 

# prior simulation
## Intercept
ggplot() +
  geom_density(data = as_tibble(rnorm(1e4, exp(10), exp(14))),
               aes(x = value, fill = "Normal")) +
  theme_classic() +
  labs(x = "Mean and SD of Intercept") +
  scale_x_continuous(labels = dollar_format()) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))

## Slope Parameters
ggplot() +
  geom_density(data = as_tibble(rnorm(1e4, exp(0), exp(13))),
               aes(x = value, fill = "normal")) +
  theme_classic() +
  labs(x = "Mean and SD of Slope Parameters") +
  scale_x_continuous(labels = dollar_format()) 

## Scale Parameter
ggplot() +
  geom_density(data = as_tibble(rexp(1e4, 1)), 
               aes(x = value, fill = "rate=1")) +
  geom_density(data = as_tibble(rexp(1e4, 2)), 
               aes(x = value, fill = "rate=2"), 
               alpha = 0.5) +
  theme_classic() +
  labs(x = "Mean and SD of Scale Parameter")

## Probability Parameter
ggplot() +
  geom_density(data = as_tibble(runif(1e4, 0, 1)), 
               aes(x = value, fill = "uniform")) +
  geom_density(data = as_tibble(rbeta(1e4, 2, 2)), 
               aes(x = value, fill = "beta 2"), 
               alpha = 0.5) +
    geom_density(data = as_tibble(rbeta(1e4, 1.5, 1.5)), 
               aes(x = value, fill = "beta 1.5"), 
               alpha = 0.7) +
  theme_classic() +
  labs(x = "Mean and SD of Probability Parameter")
```

### Model 

```{stan output.var = "smlindv.model"}
data {
  int<lower = 1> n;
  real small_indiv[n];
  int no_corp_pacs[n];
  int new_member[n];
  real pct_white[n];
  real pct_black[n];
  real pct_latino[n];
  real pct_asian[n];
  real pct_bachelors[n];
  real pct_clinton_16[n];
  real pct_dem_house_16[n];
  real log_median_hh_income[n];
  real log_tot_voting_age[n];
}

parameters {
  real<lower = 0> a;
  real b_np;
  real b_new;
  real b_white;
  real b_black;
  real b_latino;
  real b_asian;
  real b_bach;
  real b_mhh;
  real b_clint;
  real b_house;
  real b_vpop;
  real<lower = 0> scale;
  real prob;
}

model {
  // linear model
  vector[n] mu;
  for (i in 1:n) {
    mu[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] + 
      b_white * pct_white[i] + b_black * pct_black[i] + 
      b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
      b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
      b_house * pct_dem_house_16[i] + b_mhh * log_median_hh_income[i] +
      b_vpop * log_tot_voting_age[i];
    mu[i] = exp(mu[i]); // inverse link function
  }
  
  // priors
  a ~ normal(10, 14);
  b_np ~ normal(0, 13);
  b_new ~ normal(0, 13);
  b_white ~ normal(0, 13);
  b_black ~ normal(0, 13);
  b_latino ~ normal(0, 13);
  b_asian ~ normal(0, 13);
  b_bach ~ normal(0, 13);
  b_clint ~ normal(0, 13);
  b_house ~ normal(0, 13);
  b_vpop ~ normal(0, 13);
  b_mhh ~ normal(0, 13);
  scale ~ exponential(2);
  prob ~ beta(1.5, 1.5);
  
  // likelihood
  for ( i in 1:n) {
    if (small_indiv[i] == 0)
      target += (bernoulli_lpmf(1| prob));
    else
      target += (bernoulli_lpmf(0| prob) + gamma_lpdf(small_indiv[i]| mu[i]/scale, 1/scale));
    }//i
}

generated quantities {
  vector[n] mu;
  
  for (i in 1:n) {
  mu[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] + 
      b_white * pct_white[i] + b_black * pct_black[i] + 
      b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
      b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
      b_house * pct_dem_house_16[i] + b_mhh * log_median_hh_income[i] +
      b_vpop * log_tot_voting_age[i];
  mu[i] = exp(mu[i]); // inverse link function
  }
}
```

### Estimation

```{r}
# compose data
stan.data <- 
  estimation.data %>%
  dplyr::select(small_indiv, no_corp_pacs, new_member, pct_white, pct_black, 
                pct_latino, pct_asian, pct_bachelors, pct_clinton_16,
                pct_dem_house_16, log_tot_voting_age, log_median_hh_income) %>%
  mutate(no_corp_pacs = ifelse(no_corp_pacs == "YES", 1, 0),
         new_member = ifelse(new_member == "YES", 1, 0)) %>%
  drop_na() %>%
  mutate_at(.vars = vars(pct_white:log_median_hh_income), .funs = center) %>%
  compose_data()

# model estimation ------------------------------------------------------------
## Frequentist
small.01 <- glm(small_indiv ~ no_corp_pacs + new_member + pct_white + pct_black + pct_latino + pct_asian + pct_bachelors + pct_clinton_16 + pct_dem_house_16 + log_median_hh_income + log_tot_voting_age,
                     family = Gamma(link = "log"),
                     data = as.data.frame(stan.data) %>% filter(small_indiv != 0) %>% mutate_at(.vars = vars(pct_white:log_median_hh_income), .funs = center))

## Bayesian
smlindv.fit <- sampling(smlindv.model,
                        chains = 4,
                        cores = 4,
                        iter = 8000,
                        warmup = 4000,
                        data = stan.data)

traceplot(smlindv.fit, 
          inc_warmup = TRUE, 
          pars = c("a", "b_np", "b_new", "b_white", "b_black", "b_latino", 
                   "b_asian", "b_bach", "b_clint", "b_house", "b_vpop", 
                   "b_mhh", "scale"))

tidy(small.01, conf.int = TRUE, conf.level = 0.89, digits = 3)
precis(smlindv.fit, prob = 0.89, digits = 3)

post <- spread_draws(smlindv.fit, mu[i]) %>% median_hdi()
ggplot(data = estimation.data, aes(x = small_indiv)) +
  geom_density(fill = "gray") +
  geom_density(data = post, aes(x = mu), fill = "skyblue", alpha = 0.7)
```


## Model of Large Individual Contributions

### Simulating Priors

```{r}
# likelihood simulation
ggplot() +
  geom_density(data = as_tibble(rgamma(1e4, shape = 20, rate = 100)), 
               aes(x = value)) +
  theme_classic() +
  labs(x = "Mean and SD of Slope Parameters") +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) 

# prior simulation
## Intercept
ggplot() +
  geom_density(data = as_tibble(rnorm(1e4, exp(11), exp(14))),
               aes(x = value, fill = "Normal")) +
  theme_classic() +
  labs(x = "Mean and SD of Intercept") +
  scale_x_continuous(labels = dollar_format()) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))

## Slope Parameters
ggplot() +
  geom_density(data = as_tibble(rnorm(1e4, exp(0), exp(13))),
               aes(x = value, fill = "normal")) +
  theme_classic() +
  labs(x = "Mean and SD of Slope Parameters") +
  scale_x_continuous(labels = dollar_format()) 

## Scale Parameter
ggplot() +
  geom_density(data = as_tibble(rexp(1e4, 1)), 
               aes(x = value, fill = "rate=1")) +
  geom_density(data = as_tibble(rexp(1e4, 2)), 
               aes(x = value, fill = "rate=2"), 
               alpha = 0.5) +
  theme_classic() +
  labs(x = "Mean and SD of Scale Parameter")

## Probability Parameter
ggplot() +
  geom_density(data = as_tibble(runif(1e4, 0, 1)), 
               aes(x = value, fill = "uniform")) +
  geom_density(data = as_tibble(rbeta(1e4, 2, 2)), 
               aes(x = value, fill = "beta 2"), 
               alpha = 0.5) +
    geom_density(data = as_tibble(rbeta(1e4, 1.5, 1.5)), 
               aes(x = value, fill = "beta 1.5"), 
               alpha = 0.7) +
  theme_classic() +
  labs(x = "Mean and SD of Probability Parameter")
```

### Model 

```{stan output.var = "lrgindv.model"}
data {
  int<lower = 1> n;
  real large_indiv[n];
  int no_corp_pacs[n];
  int new_member[n];
  real pct_white[n];
  real pct_black[n];
  real pct_latino[n];
  real pct_asian[n];
  real pct_bachelors[n];
  real pct_clinton_16[n];
  real pct_dem_house_16[n];
  real log_median_hh_income[n];
  real log_tot_voting_age[n];
}

parameters {
  real<lower = 0> a;
  real b_np;
  real b_new;
  real b_white;
  real b_black;
  real b_latino;
  real b_asian;
  real b_bach;
  real b_mhh;
  real b_clint;
  real b_house;
  real b_vpop;
  real<lower = 0> scale;
  real prob;
}

model {
  // linear model
  vector[n] mu;
  for (i in 1:n) {
    mu[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] + 
      b_white * pct_white[i] + b_black * pct_black[i] + 
      b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
      b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
      b_house * pct_dem_house_16[i] + b_mhh * log_median_hh_income[i] +
      b_vpop * log_tot_voting_age[i];
    mu[i] = exp(mu[i]); // inverse link function
  }
  
  // priors
  a ~ normal(11, 14);
  b_np ~ normal(0, 13);
  b_new ~ normal(0, 13);
  b_white ~ normal(0, 13);
  b_black ~ normal(0, 13);
  b_latino ~ normal(0, 13);
  b_asian ~ normal(0, 13);
  b_bach ~ normal(0, 13);
  b_clint ~ normal(0, 13);
  b_house ~ normal(0, 13);
  b_vpop ~ normal(0, 13);
  b_mhh ~ normal(0, 13);
  scale ~ exponential(2);
  prob ~ beta(1.5, 1.5);
  
  // likelihood
  for ( i in 1:n) {
    if (large_indiv[i] == 0)
      target += (bernoulli_lpmf(1| prob));
    else
      target += (bernoulli_lpmf(0| prob) + gamma_lpdf(large_indiv[i]| mu[i]/scale, 1/scale));
    }//i
}

generated quantities {
  vector[n] mu;
  
  for (i in 1:n) {
  mu[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] + 
      b_white * pct_white[i] + b_black * pct_black[i] + 
      b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
      b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
      b_house * pct_dem_house_16[i] + b_mhh * log_median_hh_income[i] +
      b_vpop * log_tot_voting_age[i];
  mu[i] = exp(mu[i]); // inverse link function
  }
}
```

### Estimation

```{r}
# compose data
stan.data <- 
  estimation.data %>%
  dplyr::select(large_indiv, no_corp_pacs, new_member, pct_white, pct_black, 
                pct_latino, pct_asian, pct_bachelors, pct_clinton_16,
                pct_dem_house_16, log_tot_voting_age, log_median_hh_income) %>%
  mutate(no_corp_pacs = ifelse(no_corp_pacs == "YES", 1, 0),
         new_member = ifelse(new_member == "YES", 1, 0)) %>%
  drop_na() %>%
  mutate_at(.vars = vars(pct_white:log_median_hh_income), .funs = center) %>%
  compose_data()

# model estimation ------------------------------------------------------------
## Frequentist
large.01 <- glm(large_indiv ~ no_corp_pacs + new_member + pct_white + pct_black + pct_latino + pct_asian + pct_bachelors + pct_clinton_16 + pct_dem_house_16 + log_median_hh_income + log_tot_voting_age,
                     family = Gamma(link = "log"),
                     data = as.data.frame(stan.data) %>% filter(large_indiv != 0) %>% mutate_at(.vars = vars(pct_white:log_median_hh_income), .funs = center))

## Bayesian
lrgindv.fit <- sampling(lrgindv.model,
                        chains = 4,
                        cores = 4,
                        iter = 8000,
                        warmup = 4000,
                        data = stan.data)

traceplot(lrgindv.fit, 
          inc_warmup = TRUE, 
          pars = c("a", "b_np", "b_new", "b_white", "b_black", "b_latino", 
                   "b_asian", "b_bach", "b_clint", "b_house", "b_vpop", 
                   "b_mhh", "scale"))

tidy(large.01, conf.int = TRUE, conf.level = 0.89, digits = 3)
precis(lrgindv.fit, prob = 0.89, digits = 3)

post <- spread_draws(lrgindv.fit, mu[i]) %>% median_hdi()
ggplot(data = estimation.data, aes(x = small_indiv)) +
  geom_density(fill = "gray") +
  geom_density(data = post, aes(x = mu), fill = "skyblue", alpha = 0.7)
```


## Model of Total Individual Contributions

### Simulating Priors

```{r}
# likelihood simulation
ggplot() +
  geom_density(data = as_tibble(rgamma(1e4, shape = 20, rate = 100)), 
               aes(x = value)) +
  theme_classic() +
  labs(x = "Mean and SD of Slope Parameters") +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) 

# prior simulation
## Intercept
ggplot() +
  geom_density(data = as_tibble(rnorm(1e4, exp(12), exp(14))),
               aes(x = value, fill = "Normal")) +
  theme_classic() +
  labs(x = "Mean and SD of Intercept") +
  scale_x_continuous(labels = dollar_format()) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))

## Slope Parameters
ggplot() +
  geom_density(data = as_tibble(rnorm(1e4, exp(0), exp(14))),
               aes(x = value, fill = "normal")) +
  theme_classic() +
  labs(x = "Mean and SD of Slope Parameters") +
  scale_x_continuous(labels = dollar_format()) 

## Scale Parameter
ggplot() +
  geom_density(data = as_tibble(rexp(1e4, 1)), 
               aes(x = value, fill = "rate=1")) +
  geom_density(data = as_tibble(rexp(1e4, 2)), 
               aes(x = value, fill = "rate=2"), 
               alpha = 0.5) +
  theme_classic() +
  labs(x = "Mean and SD of Scale Parameter")

## Probability Parameter
ggplot() +
  geom_density(data = as_tibble(runif(1e4, 0, 1)), 
               aes(x = value, fill = "uniform")) +
  geom_density(data = as_tibble(rbeta(1e4, 2, 2)), 
               aes(x = value, fill = "beta 2"), 
               alpha = 0.5) +
    geom_density(data = as_tibble(rbeta(1e4, 1.5, 1.5)), 
               aes(x = value, fill = "beta 1.5"), 
               alpha = 0.7) +
  theme_classic() +
  labs(x = "Mean and SD of Probability Parameter")
```

### Model 

```{stan output.var = "totindv.model"}
data {
  int<lower = 1> n;
  real net_indiv_total[n];
  int no_corp_pacs[n];
  int new_member[n];
  real pct_white[n];
  real pct_black[n];
  real pct_latino[n];
  real pct_asian[n];
  real pct_bachelors[n];
  real pct_clinton_16[n];
  real pct_dem_house_16[n];
  real log_median_hh_income[n];
  real log_tot_voting_age[n];
}

parameters {
  real<lower = 0> a;
  real b_np;
  real b_new;
  real b_white;
  real b_black;
  real b_latino;
  real b_asian;
  real b_bach;
  real b_mhh;
  real b_clint;
  real b_house;
  real b_vpop;
  real<lower = 0> scale;
  real prob;
}

model {
  // linear model
  vector[n] mu;
  for (i in 1:n) {
    mu[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] + 
      b_white * pct_white[i] + b_black * pct_black[i] + 
      b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
      b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
      b_house * pct_dem_house_16[i] + b_mhh * log_median_hh_income[i] +
      b_vpop * log_tot_voting_age[i];
    mu[i] = exp(mu[i]); // inverse link function
  }
  
  // priors
  a ~ normal(12, 14);
  b_np ~ normal(0, 14);
  b_new ~ normal(0, 14);
  b_white ~ normal(0, 14);
  b_black ~ normal(0, 14);
  b_latino ~ normal(0, 14);
  b_asian ~ normal(0, 14);
  b_bach ~ normal(0, 14);
  b_clint ~ normal(0, 14);
  b_house ~ normal(0, 14);
  b_vpop ~ normal(0, 14);
  b_mhh ~ normal(0, 14);
  scale ~ exponential(2);
  prob ~ beta(1.5, 1.5);
  
  // likelihood
  for ( i in 1:n) {
    if (net_indiv_total[i] == 0)
      target += (bernoulli_lpmf(1| prob));
    else
      target += (bernoulli_lpmf(0| prob) + gamma_lpdf(net_indiv_total[i]| mu[i]/scale, 1/scale));
    }//i
}

generated quantities {
  vector[n] mu;
  
  for (i in 1:n) {
  mu[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] + 
      b_white * pct_white[i] + b_black * pct_black[i] + 
      b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
      b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
      b_house * pct_dem_house_16[i] + b_mhh * log_median_hh_income[i] +
      b_vpop * log_tot_voting_age[i];
  mu[i] = exp(mu[i]); // inverse link function
  }
}
```

### Estimation

```{r}
# compose data
stan.data <- 
  estimation.data %>%
  dplyr::select(net_indiv_total, no_corp_pacs, new_member, pct_white, pct_black, 
                pct_latino, pct_asian, pct_bachelors, pct_clinton_16,
                pct_dem_house_16, log_tot_voting_age, log_median_hh_income) %>%
  mutate(no_corp_pacs = ifelse(no_corp_pacs == "YES", 1, 0),
         new_member = ifelse(new_member == "YES", 1, 0)) %>%
  drop_na() %>%
  mutate_at(.vars = vars(pct_white:log_median_hh_income), .funs = center) %>%
  compose_data()

# model estimation ------------------------------------------------------------
## Frequentist
indiv.tot.01 <- glm(net_indiv_total ~ no_corp_pacs + new_member + pct_white + pct_black + pct_latino + pct_asian + pct_bachelors + pct_clinton_16 + pct_dem_house_16 + log_median_hh_income + log_tot_voting_age,
                     family = Gamma(link = "log"),
                     data = as.data.frame(stan.data) %>% filter(net_indiv_total != 0) %>% mutate_at(.vars = vars(pct_white:log_median_hh_income), .funs = center))

## Bayesian
totindv.fit <- sampling(totindv.model,
                        chains = 4,
                        cores = 4,
                        iter = 8000,
                        warmup = 4000,
                        data = stan.data)

traceplot(totindv.fit, 
          inc_warmup = TRUE, 
          pars = c("a", "b_np", "b_new", "b_white", "b_black", "b_latino", 
                   "b_asian", "b_bach", "b_clint", "b_house", "b_vpop", 
                   "b_mhh", "scale"))

tidy(indiv.tot.01, conf.int = TRUE, conf.level = 0.89, digits = 3)
precis(totindv.fit, prob = 0.89, digits = 3)

post <- spread_draws(totindv.fit, mu[i]) %>% median_hdi()
ggplot(data = estimation.data, aes(x = net_indiv_total)) +
  geom_density(fill = "gray") +
  geom_density(data = post, aes(x = mu), fill = "skyblue", alpha = 0.7)
```


## Model of Individual Ideological PAC Contributions

### Simulating Priors

```{r}
# likelihood simulation
ggplot() +
  geom_density(data = as_tibble(rgamma(1e4, shape = 20, rate = 100)), 
               aes(x = value)) +
  theme_classic() +
  labs(x = "Mean and SD of Slope Parameters") +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) 

# prior simulation
## Intercept
ggplot() +
  geom_density(data = as_tibble(rnorm(1e4, exp(10.5), exp(13))),
               aes(x = value, fill = "Normal")) +
  theme_classic() +
  labs(x = "Mean and SD of Intercept") +
  scale_x_continuous(labels = dollar_format()) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))

## Slope Parameters
ggplot() +
  geom_density(data = as_tibble(rnorm(1e4, exp(0), exp(12))),
               aes(x = value, fill = "normal")) +
  theme_classic() +
  labs(x = "Mean and SD of Slope Parameters") +
  scale_x_continuous(labels = dollar_format()) 

## Scale Parameter
ggplot() +
  geom_density(data = as_tibble(rexp(1e4, 1)), 
               aes(x = value, fill = "rate=1")) +
  geom_density(data = as_tibble(rexp(1e4, 2)), 
               aes(x = value, fill = "rate=2"), 
               alpha = 0.5) +
  theme_classic() +
  labs(x = "Mean and SD of Scale Parameter")

## Probability Parameter
ggplot() +
  geom_density(data = as_tibble(runif(1e4, 0, 1)), 
               aes(x = value, fill = "uniform")) +
  geom_density(data = as_tibble(rbeta(1e4, 2, 2)), 
               aes(x = value, fill = "beta 2"), 
               alpha = 0.5) +
    geom_density(data = as_tibble(rbeta(1e4, 1.5, 1.5)), 
               aes(x = value, fill = "beta 1.5"), 
               alpha = 0.7) +
  theme_classic() +
  labs(x = "Mean and SD of Probability Parameter")
```

### Model 

```{stan output.var = "individeopac.model"}
data {
  int<lower = 1> n;
  real indiv_ideological[n];
  int no_corp_pacs[n];
  int new_member[n];
  real pct_white[n];
  real pct_black[n];
  real pct_latino[n];
  real pct_asian[n];
  real pct_bachelors[n];
  real pct_clinton_16[n];
  real pct_dem_house_16[n];
  real log_median_hh_income[n];
  real log_tot_voting_age[n];
}

parameters {
  real<lower = 0> a;
  real b_np;
  real b_new;
  real b_white;
  real b_black;
  real b_latino;
  real b_asian;
  real b_bach;
  real b_mhh;
  real b_clint;
  real b_house;
  real b_vpop;
  real<lower = 0> scale;
  real<lower = 0, upper = 1> prob;
}

model {
  // linear model
  vector[n] mu;
  for (i in 1:n) {
    mu[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] + 
      b_white * pct_white[i] + b_black * pct_black[i] + 
      b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
      b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
      b_house * pct_dem_house_16[i] + b_mhh * log_median_hh_income[i] +
      b_vpop * log_tot_voting_age[i];
    mu[i] = exp(mu[i]); // inverse link function
  }
  
  // priors
  a ~ normal(10.5, 13);
  b_np ~ normal(0, 12);
  b_new ~ normal(0, 12);
  b_white ~ normal(0, 12);
  b_black ~ normal(0, 12);
  b_latino ~ normal(0, 12);
  b_asian ~ normal(0, 12);
  b_bach ~ normal(0, 12);
  b_clint ~ normal(0, 12);
  b_house ~ normal(0, 12);
  b_vpop ~ normal(0, 12);
  b_mhh ~ normal(0, 12);
  scale ~ exponential(2);
  prob ~ beta(1.5, 1.5);
  
  // likelihood
  for ( i in 1:n) {
    if (indiv_ideological[i] == 0)
      target += (bernoulli_lpmf(1| prob));
    else
      target += (bernoulli_lpmf(0| prob) + gamma_lpdf(indiv_ideological[i]| mu[i]/scale, 1/scale));
    }//i
}

generated quantities {
  vector[n] mu;
  
  for (i in 1:n) {
  mu[i] = a + b_np * no_corp_pacs[i] + b_new * new_member[i] + 
      b_white * pct_white[i] + b_black * pct_black[i] + 
      b_latino * pct_latino[i] + b_asian * pct_asian[i] + 
      b_bach * pct_bachelors[i] + b_clint * pct_clinton_16[i] + 
      b_house * pct_dem_house_16[i] + b_mhh * log_median_hh_income[i] +
      b_vpop * log_tot_voting_age[i];
  mu[i] = exp(mu[i]); // inverse link function
  }
}
```

### Estimation

```{r}
# compose data
stan.data <- 
  estimation.data %>%
  dplyr::select(indiv_ideological, no_corp_pacs, new_member, pct_white, pct_black, 
                pct_latino, pct_asian, pct_bachelors, pct_clinton_16,
                pct_dem_house_16, log_tot_voting_age, log_median_hh_income) %>%
  mutate(no_corp_pacs = ifelse(no_corp_pacs == "YES", 1, 0),
         new_member = ifelse(new_member == "YES", 1, 0)) %>%
  drop_na() %>%
  mutate_at(.vars = vars(pct_white:log_median_hh_income), .funs = center) %>%
  compose_data()

# model estimation ------------------------------------------------------------
## Frequentist
individeol.pacs.01 <- glm(indiv_ideological ~ no_corp_pacs + new_member + pct_white + pct_black + pct_latino + pct_asian + pct_bachelors + pct_clinton_16 + pct_dem_house_16 + log_median_hh_income + log_tot_voting_age,
                     family = Gamma(link = "log"),
                     data = as.data.frame(stan.data) %>% filter(indiv_ideological != 0) %>% mutate_at(.vars = vars(pct_white:log_median_hh_income), .funs = center))

## Bayesian
individeopac.fit <- sampling(individeopac.model,
                        chains = 4,
                        cores = 4,
                        iter = 8000,
                        warmup = 4000,
                        data = stan.data)

traceplot(ideopac.fit, 
          inc_warmup = TRUE, 
          pars = c("a", "b_np", "b_new", "b_white", "b_black", "b_latino", 
                   "b_asian", "b_bach", "b_clint", "b_house", "b_vpop", 
                   "b_mhh", "scale"))

tidy(individeol.pacs.01, conf.int = TRUE, conf.level = 0.89, digits = 3)
precis(individeopac.fit, prob = 0.89, digits = 3)

post <- spread_draws(individeopac.fit, mu[i]) %>% median_hdi()
ggplot(data = estimation.data, aes(x = indiv_ideological)) +
  geom_density(fill = "gray") +
  geom_density(data = post, aes(x = mu), fill = "skyblue", alpha = 0.7)
```





# Results Summary

```{r}
# Save models
# save(voting.fit, file = "E:/Project/voting_fit.Rda")
# save(turnout.fit, file = "E:/Project/turnout_fit.Rda")
# save(totpac.fit, file = "E:/Project/totpac_fit.Rda")
# save(numpac.fit, file = "E:/Project/numpac_fit.Rda")
# save(bizpac.fit, file = "E:/Project/bizpac_fit.Rda")
# save(laborpac.fit, file = "E:/Project/labor_fit.Rda")
# save(ideopac.fit, file = "E:/Project/ideopac_fit.Rda")
# save(indideopac.fit, file = "E:/Project/indideopac_fit.Rda")
# save(dirideopac.fit, file = "E:/Project/dirideopac_fit.Rda")
# save(ldrpac.fit, file = "E:/Project/ldrpac_fit.Rda")
# save(cmtpac.fit, file = "E:/Project/cmtpac_fit.Rda")
# save(prtypac.fit, file = "E:/Project/prtypac_fit.Rda")
# save(slffin.fit, file = "E:/Project/slffin_fit.Rda")
# save(candcontribs.fit, file = "E:/Project/candcontribs_fit.Rda")
# save(smlindv.fit, file = "E:/Project/smlindv_fit.Rda")
# save(lrgindv.fit, file = "E:/Project/lrgindv_fit.Rda")
# save(totindv.fit, file = "E:/Project/totindiv_fit.Rda")
# save(individeopac.fit, file = "E:/Project/individeopac_fit.Rda")

# load models
load(file = "Models/voting_fit.Rda")
load(file = "Models/turnout_fit.Rda")
load(file = "Models/totpac_fit.Rda")
load(file = "Models/numpac_fit.Rda")
load(file = "Models/bizpac_fit.Rda")
load(file = "Models/labor_fit.Rda")
load(file = "Models/ideopac_fit.Rda")
load(file = "Models/indideopac_fit.Rda")
load(file = "Models/dirideopac_fit.Rda")
load(file = "Models/ldrpac_fit.Rda")
load(file = "Models/cmtpac_fit.Rda")
load(file = "Models/prtypac_fit.Rda")
load(file = "Models/slffin_fit.Rda")
load(file = "Models/candcontribs_fit.Rda")
load(file = "Models/smlindv_fit.Rda")
load(file = "Models/lrgindv_fit.Rda")
load(file = "Models/totindiv_fit.Rda")
load(file = "Models/individeopac_fit.Rda")


models <- c("totpac.fit", "numpac.fit", "bizpac.fit", "laborpac.fit", 
            "ideopac.fit", "cmtpac.fit", "smlindv.fit", "lrgindv.fit",
            "totindv.fit", "prtypac.fit", "slffin.fit", "candcontribs.fit")

for (i in 1:length(models)) {
  models[[i]] <- as.data.frame(models[i])
}

# extract posterior predictions
## PACs
post.1 <- totpac.fit %>% spread_draws(a, b_np) %>% mutate(model = "totpac.fit") 
post.2 <- bizpac.fit %>% spread_draws(a, b_np) %>% mutate(model = "bizpac.fit")
post.3 <- laborpac.fit %>% spread_draws(a, b_np) %>% mutate(model = "laborpac.fit")
post.4 <- ideopac.fit %>% spread_draws(a, b_np) %>% mutate(model = "ideopac.fit")
post.5 <- indideopac.fit %>% spread_draws(a, b_np) %>% mutate(model = "indideopac.fit")
post.6 <- dirideopac.fit %>% spread_draws(a, b_np) %>% mutate(model = "dirideopac.fit")
post.7 <- numpac.fit %>% spread_draws(a, b_np) %>% mutate(model = "numpac.fit")
post.pac <- bind_rows(post.1, post.2, post.3, post.4, post.5, post.6, post.7)

## party contributions
post.7 <- as.data.frame(ldrpac.fit) %>% dplyr::select(a, b_np) %>% mutate(model = "ldrpac.fit")
post.8 <- as.data.frame(cmtpac.fit) %>% dplyr::select(a, b_np) %>% mutate(model = "cmtpac.fit")
post.9 <- as.data.frame(prtypac.fit) %>% dplyr::select(a, b_np) %>% mutate(model = "prtypac.fit")
post.10 <- as.data.frame(slffin.fit) %>% dplyr::select(a, b_np) %>% mutate(model = "slffin.fit")
post.11 <- as.data.frame(candcontribs.fit) %>% dplyr::select(a, b_np) %>% mutate(model = "candcontribs.fit")
post.party <- bind_rows(post.7, post.8, post.9, post.10, post.11)

## individual contributions
post.12 <- as.data.frame(smlindv.fit) %>% dplyr::select(a, b_np) %>% mutate(model = "smlindv.fit")
post.13 <- as.data.frame(lrgindv.fit) %>% dplyr::select(a, b_np) %>% mutate(model = "lrgindv.fit")
post.14 <- as.data.frame(totindv.fit) %>% dplyr::select(a, b_np) %>% mutate(model = "totindv.fit")
post.15 <- as.data.frame(individeopac.fit) %>% dplyr::select(a, b_np) %>% mutate(model = "individeopac.fit")
post.indv <- bind_rows(post.12, post.13, post.14, post.15)

## voting
post.16 <- as.data.frame(voting.fit) %>% dplyr::select(a, b_np) %>% mutate(model = "voting.fit")
post.17 <- as.data.frame(turnout.fit) %>% dplyr::select(a, b_np) %>% mutate(model = "turnout.fit")
post.vote <- bind_rows(post.16, post.17)


# PAC results -----------------------------------------------------------------
## Coefficient plot
post.pac %>%
  mutate(b_np = exp(b_np) - 1) %>%
  #group_by(model) %>%
  #median_hdi(exp(b_np) - 1, .width = c(0.89)) %>%
  #filter(prediction == 1) %>%
  ggplot() +
  #geom_pointintervalh() +
  stat_halfeyeh(aes(y = fct_reorder(model, b_np), x = b_np), 
                .width = c(0.89, 0.5), 
                point_interval = median_hdi) +
  # geom_text(aes(label = median_hdi(b_np)),
  #           hjust = 0.5,
  #           vjust = -1.5) +
  geom_vline(aes(xintercept = 0), linetype = "dashed") +
  scale_x_continuous(labels = percent_format(),
                     breaks = pretty_breaks(n = 8)) +
  scale_y_discrete(labels = c("Business PACs", "Indirect Ideological PACs",
                              "Total PACs", "Labor PACs", "Number of PACs",
                              "Direct Ideological PACs", "Ideological PACs")) +
  labs(x = "% Decrease", y = "") +
  theme_pubr()
ggsave("Figures/Results/pac_coef.pdf", height = 4, width = 7)

## predicted values
pred.pac <- 
  post.pac %>%
  group_by(model) %>%
  mutate(a = exp(a),
         b_np = exp(b_np),
         no_pac_pred = a * b_np,
         pac_pred = a) %>%
  dplyr::select(model, no_pac_pred, pac_pred) %>%
  #gather(no_pac_pred, pac_pred, key = "prediction", value = "predicted_val") %>%
  # mutate(prediction = factor(prediction, 
  #                            levels = c("no_pac_pred", "pac_pred"),
  #                            labels = c("No to Corp. PACs Donations", "Yes to Corp. PAC Donations"))) %>%
  group_by(model) %>%
  median_hdi(.width = 0.89)

ggplot() +
  geom_pointintervalh(data = pred.pac,
                      aes(y = fct_rev(model), x = no_pac_pred, xmin = no_pac_pred.lower, xmax = no_pac_pred.upper, size = 100),
                      color = "black") +
  geom_pointintervalh(data = pred.pac, 
                      aes(y = fct_rev(model), x = pac_pred, xmin = pac_pred.lower, xmax = pac_pred.upper, size = 100),
                      position = "dodge",
                      color = "blue") +
  #facet_wrap(~ prediction) +
  coord_flip() +
  #geom_text(aes(label = comma(round(predicted_val, digits = 2))), hjust = 0.5, vjust = -1.5) +
  scale_x_continuous(labels = dollar_format(),
                     breaks = pretty_breaks(n = 6),
                     limits = c(0, 100000)) +
  scale_y_discrete(labels = c("Total PACs", "Number of PACs", "Labor PACs","Indirect Ideological PACs", "Ideological PACs", "Direct Ideological PACs", "Business PACs")) +
  labs(x = "", y = "") +
  theme_pubr() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
ggsave("Figures/Results/pac_preds.pdf", height = 4)

# Individual Results ----------------------------------------------------------
## Coefficient plot
post.indv %>%
  mutate(b_np = exp(b_np)) %>%
  #group_by(model) %>%
  #median_hdi(exp(b_np) - 1, .width = c(0.89)) %>%
  #filter(prediction == 1) %>%
  ggplot() +
  #geom_pointintervalh() +
  stat_halfeyeh(aes(y = fct_reorder(model, b_np), x = b_np), 
                .width = c(0.89, 0.5), 
                point_interval = median_hdi) +
  geom_vline(aes(xintercept = 0), linetype = "dashed") +
  scale_x_continuous(labels = percent_format()) +
  scale_y_discrete(labels = c("Large Individual",
                              "Individual Ideological",
                              "Total Individual",
                              "Small Individual")) +
  labs(x = "% Increase in Contributions", y = "") +
  theme_pubr()
ggsave("Figures/Results/indv_coef.pdf", height = 4, width = 7)

## predicted values
pred.indv <- 
  post.indv %>%
  group_by(model) %>%
  mutate(a = exp(a),
         b_np = exp(b_np),
         no_pac_pred = a * b_np,
         pac_pred = a) %>%
  dplyr::select(model, no_pac_pred, pac_pred) %>%
  gather(no_pac_pred, pac_pred, key = "prediction", value = "predicted_val") %>%
  mutate(prediction = factor(prediction, 
                             levels = c("no_pac_pred", "pac_pred"),
                             labels = c("No Corp. PACs Donations", "PAC Donations"))) %>%
  group_by(model, prediction) %>%
  median_hdi(predicted_val, .width = 0.89)

ggplot(data = pred.indv, aes(y = fct_rev(model), x = predicted_val, xmin = .lower, xmax = .upper)) +
  geom_pointintervalh() +
  facet_wrap(~ prediction) +
  coord_flip() +
  geom_text(aes(label = comma(round(predicted_val, digits = 2))), hjust = 0.5, vjust = -1.5) +
  scale_x_continuous(labels = scales::dollar_format(),
                     breaks = scales::pretty_breaks(n = 6),
                     limits = c(0, 900000)) +
  scale_y_discrete(labels = c("Total", 
                              "Small", 
                              "Large")) +
  labs(x = "",
       y = "") +
  theme_pubr() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
ggsave("Figures/Results/indv_preds.pdf", height = 4)

# Party Results ---------------------------------------------------------------
## Coefficient plot
post.party %>%
  group_by(model) %>%
  median_hdi(exp(b_np) - 1, .width = c(0.89)) %>%
  #filter(prediction == 1) %>%
  ggplot(aes(y = fct_rev(model), x = `exp(b_np) - 1`, xmin = .lower, xmax = .upper)) +
  geom_pointintervalh() +
  #stat_halfeyeh(.width = c(0.89, 0.5), point_interval = median_hdi) +
  geom_text(aes(label = round(`exp(b_np) - 1`, digits = 2)), hjust = 0.5, vjust = -1.5) +
  geom_vline(aes(xintercept = 0), linetype = "dashed") +
  scale_x_continuous(labels = scales::percent_format()) +
  scale_y_discrete(labels = c("Self-Financing", "Party Committees", "Party Candidate Committees", "Candidate Contributions")) +
  labs(x = "% Change in Contributions",
       y = "") +
  theme_pubr()
ggsave("Figures/Results/party_coef.pdf", height = 4)

## predicted values
pred.party <- 
  post.party %>%
  group_by(model) %>%
  mutate(a = exp(a),
         b_np = exp(b_np),
         no_pac_pred = a * b_np,
         pac_pred = a) %>%
  dplyr::select(model, no_pac_pred, pac_pred) %>%
  gather(no_pac_pred, pac_pred, key = "prediction", value = "predicted_val") %>%
  mutate(prediction = factor(prediction, 
                             levels = c("no_pac_pred", "pac_pred"),
                             labels = c("No Corp. PACs Donations", "PAC Donations"))) %>%
  group_by(model, prediction) %>%
  median_hdi(predicted_val, .width = 0.89)

ggplot(data = pred.party, aes(y = fct_rev(model), x = predicted_val, xmin = .lower, xmax = .upper)) +
  geom_pointintervalh() +
  facet_wrap(~ prediction) +
  coord_flip() +
  geom_text(aes(label = comma(round(predicted_val, digits = 2))), hjust = 0.5, vjust = -2.2) +
  scale_x_continuous(labels = scales::dollar_format(),
                     breaks = scales::pretty_breaks(n = 6),
                     limits = c(0, 3000)) +
  scale_y_discrete(labels = c("Self-Financing", "Party Committees", 
                              "Party Candidate Committees", 
                              "Candidate Contributions")) +
  labs(x = "",
       y = "") +
  theme_pubr() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
ggsave("Figures/Results/party_preds.pdf", height = 5)

# Vote Results ----------------------------------------------------------------
## Coefficient plot
post.vote %>%
  group_by(model) %>%
  median_hdi(exp(b_np) - 1, .width = c(0.89)) %>%
  #filter(prediction == 1) %>%
  ggplot(aes(y = fct_rev(model), x = `exp(b_np) - 1`, xmin = .lower, xmax = .upper)) +
  geom_pointintervalh() +
  #stat_halfeyeh(.width = c(0.89, 0.5), point_interval = median_hdi) +
  geom_text(aes(label = round(`exp(b_np) - 1`, digits = 2)), hjust = 0.5, vjust = -1.5) +
  geom_vline(aes(xintercept = 0), linetype = "dashed") +
  scale_x_continuous(labels = scales::percent_format()) +
  scale_y_discrete(labels = c("Vote Share", "V.A.P. Turnout")) +
  labs(x = "% Change",
       y = "") +
  theme_pubr()
ggsave("Figures/Results/vote_coef.pdf", height = 4)

## predicted values
pred.vote <- 
  post.vote %>%
  group_by(model) %>%
  mutate(a = exp(a),
         b_np = exp(b_np),
         no_pac_pred = a * b_np,
         pac_pred = a) %>%
  dplyr::select(model, no_pac_pred, pac_pred) %>%
  gather(no_pac_pred, pac_pred, key = "prediction", value = "predicted_val") %>%
  mutate(prediction = factor(prediction, 
                             levels = c("no_pac_pred", "pac_pred"),
                             labels = c("No Corp. PACs Donations", "PAC Donations"))) %>%
  group_by(model, prediction) %>%
  median_hdi(predicted_val, .width = 0.89)

ggplot(data = pred.vote, aes(y = fct_rev(model), x = predicted_val, xmin = .lower, xmax = .upper)) +
  geom_pointintervalh() +
  facet_wrap(~ prediction) +
  coord_flip() +
  geom_text(aes(label = comma(round(predicted_val, digits = 2))), hjust = -0.75, vjust = -1) +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 6),
                     limits = c(0, 100)) +
  scale_y_discrete(labels = c("Vote Share", "V.A.P. Turnout")) +
  labs(x = "",
       y = "") +
  theme_pubr() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
ggsave("Figures/Results/vote_preds.pdf", height = 4)
```



## Propensity Score Matching

```{r}
library(MatchIt)
match.data <- 
  estimation.data %>%
  dplyr::select(no_corp_pacs, new_member, pct_white, pct_black, 
                pct_latino, pct_asian, pct_bachelors, median_hh_income, 
                pct_clinton_16, pct_dem_house_16, small_indiv, large_indiv, 
                net_indiv_total, vote_pct, tot_pac_money, business_pacs, 
                labor_pacs, ideological_pacs, candidate_contribs, 
                num_pac_contribs, vap_turnout, tot_voting_age,
                pac_cand_committee, indiv_party_committee, 
                indiv_cand_committee, indiv_self_finance, pac_party_committee) %>%
  na.omit() %>%
  mutate(no_corp_pacs = ifelse(no_corp_pacs == "YES", 1, 0))

mod.match <- matchit(no_corp_pacs ~ new_member + pct_white + pct_black + 
                       pct_latino + pct_asian + pct_bachelors + 
                       median_hh_income + pct_clinton_16 + pct_dem_house_16 +
                       tot_voting_age,
                     method = "nearest",
                     distance = "probit",
                     data = match.data)
data.match <- match.data(mod.match)

summary(mod.match)
plot(mod.match, type = "hist")
plot(mod.match, type = "jitter")

matched.vote.01 <- lm(vote_pct ~ no_corp_pacs + new_member + pct_white + pct_black + pct_latino + pct_asian + pct_bachelors + median_hh_income + pct_clinton_16 + pct_dem_house_16 + tot_voting_age,
              data = data.match)

matched.turnout.01 <- lm(vap_turnout ~ no_corp_pacs + new_member + pct_white + pct_black + pct_latino + pct_asian + pct_bachelors + median_hh_income + pct_clinton_16 + pct_dem_house_16 + tot_voting_age,
              data = data.match)

matched.small.01 <- lm(small_indiv ~ no_corp_pacs + new_member + pct_white + pct_black + pct_latino + pct_asian + pct_bachelors + median_hh_income + pct_clinton_16 + pct_dem_house_16 + tot_voting_age,
               data = data.match)

matched.large.01 <- lm(large_indiv ~ no_corp_pacs + new_member + pct_white + pct_black + pct_latino + pct_asian + pct_bachelors + median_hh_income + pct_clinton_16 + pct_dem_house_16 + tot_voting_age,
               data = data.match)

matched.pac.money.01 <- lm(tot_pac_money ~ no_corp_pacs + new_member + pct_white + pct_black + pct_latino + pct_asian + pct_bachelors + median_hh_income + pct_clinton_16 + pct_dem_house_16 + tot_voting_age,
                   data = data.match)

matched.biz.pacs.01 <- lm(business_pacs ~ no_corp_pacs + new_member + pct_white + pct_black + pct_latino + pct_asian + pct_bachelors + median_hh_income + pct_clinton_16 + pct_dem_house_16 + tot_voting_age,
                  data = data.match)

matched.labor.pacs.01 <- lm(labor_pacs ~ no_corp_pacs + new_member + pct_white + pct_black + pct_latino + pct_asian + pct_bachelors + median_hh_income + pct_clinton_16 + pct_dem_house_16 + tot_voting_age,
                    data = data.match)

matched.ideol.pacs.01 <- lm(ideological_pacs ~ no_corp_pacs + new_member + pct_white + pct_black + pct_latino + pct_asian + pct_bachelors + median_hh_income + pct_clinton_16 + pct_dem_house_16 + tot_voting_age,
                            data = data.match)

matched.cmte.pacs.01 <- lm(pac_cand_committee ~ no_corp_pacs + new_member + pct_white + pct_black + pct_latino + pct_asian + pct_bachelors + median_hh_income + pct_clinton_16 + pct_dem_house_16 + tot_voting_age,
                           data = data.match)

matched.cmte.pacs.02 <- lm(indiv_cand_committee ~ no_corp_pacs + new_member + pct_white + pct_black + pct_latino + pct_asian + pct_bachelors + median_hh_income + pct_clinton_16 + pct_dem_house_16 + tot_voting_age,
                           data = data.match)

matched.party.contribs.01 <- lm(pac_party_committee ~ no_corp_pacs + new_member + pct_white + pct_black + pct_latino + pct_asian + pct_bachelors + median_hh_income + pct_clinton_16 + pct_dem_house_16 + tot_voting_age,
                                data = data.match)

matched.party.contribs.02 <- lm(indiv_party_committee ~ no_corp_pacs + new_member + pct_white + pct_black + pct_latino + pct_asian + pct_bachelors + median_hh_income + pct_clinton_16 + pct_dem_house_16 + tot_voting_age,
                                data = data.match)

matched.self.contribs.01 <- lm(indiv_self_finance ~ no_corp_pacs + new_member + pct_white + pct_black + pct_latino + pct_asian + pct_bachelors + median_hh_income + pct_clinton_16 + pct_dem_house_16 + tot_voting_age,
                               data = data.match)

matched.cand.contribs.01 <- lm(candidate_contribs ~ no_corp_pacs + new_member + pct_white + pct_black + pct_latino + pct_asian + pct_bachelors + median_hh_income + pct_clinton_16 + pct_dem_house_16 + tot_voting_age,
                       data = data.match)

matched.indiv.tot.01 <- lm(net_indiv_total ~ no_corp_pacs + new_member + pct_white + pct_black + pct_latino + pct_asian + pct_bachelors + median_hh_income + pct_clinton_16 + pct_dem_house_16 + tot_voting_age,
                   data = data.match)

matched.num.pacs.01 <- lm(num_pac_contribs ~ no_corp_pacs + new_member + pct_white + pct_black + pct_latino + pct_asian + pct_bachelors + median_hh_income + pct_clinton_16 + pct_dem_house_16 + tot_voting_age,
                  data = data.match)

stargazer(matched.vote.01, matched.turnout.01, matched.small.01, 
          matched.large.01, matched.pac.money.01, 
          matched.biz.pacs.01, matched.labor.pacs.01, 
          matched.ideol.pacs.01, matched.cmte.pacs.01, matched.cmte.pacs.02,
          matched.party.contribs.01, matched.party.contribs.02, 
          matched.self.contribs.01, matched.cand.contribs.01, 
          matched.indiv.tot.01, matched.num.pacs.01,
          type = "text")
```


# Model Diagnostics

```{r Diagnostics}

```