---
title: "Step III: Data Analysis"
subtitle: 'PACs and Small-dollar Donations'
author:
  - name: Nicholas R. Jenkins 
    affiliation: University of California, Riverside
    affiliation_url: https://www.ucr.edu
abstract: |
  This document shows all the code used to analyze the data for this project. 
  All analyses were done with R version `r R.version$major`.`r R.version$minor` 
  "`r R.version$nickname`" and Stan version `r stan_version()` in RStudio. 
  
  Each step has been carefully documented and will replicate the results in the 
  manuscript. The code for this document can be downloaded using the button 
  in the top right corner. For any questions about this code, please contact 
  Nick Jenkins at 
  [nicholas.jenkins@email.ucr.edu](mailto:nicholas.jenkins@email.ucr.edu).
date: "`r Sys.Date()`"
output: 
  html_notebook: 
    highlight: pygments
    theme: paper
    toc: yes
    code_folding: 
    toc_float: true
bibliography: /Users/nick/Documents/Research/References/BibTeX/biblatex.bib
editor_options: 
  chunk_output_type: inline
---

# Environment Preperation

This section clears the current working environment and loads the packages used to visualize the data. I also create the function `comma()` to format any in-line output values to have thousands separators and only two digits. 

```{r setup, warning = FALSE, message = FALSE, echo = TRUE, results = "hide"}
# Clear Environment -----------------------------------------------------------
rm(list = ls())

# Load Packages ---------------------------------------------------------------
packages <- c("tidyverse", "foreign", "stargazer", "lme4", "multcomp", 
              "lmerTest", "ggmcmc", "ggridges", "rstan", "rstanarm", "brms",
              "rethinking", "patchwork", "tidybayes", "sjstats", "sjPlot",
              "bayesplot", "sjmisc", "ggpubr", "broom", "scales", "ggthemes",
              "ggrepel", "BayesPostEst", "cmdstanr", "bayestestR")
lapply(packages, require, character.only = TRUE)

# Functions -------------------------------------------------------------------
# Inline Formatting
comma <- function(x) format(x, digits = 2, big.mark = ",")

# Inverse Hyperbolic Sin Transformation Function
ihs <- function(x) {
    y <- log(x + sqrt(x^2 + 1))
    return(y)
}

# Set Global Chunk Options ----------------------------------------------------
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  comment = "##",
  R.options = list(width = 70)
)
```


# Import Data

This section imports the data cleaned in the "Step I: Data Cleaning" document to begin analyzing the data. 

```{r Data Import}
load("Data/Clean Data/estimation_data.Rda")
#load("E:/Project/Data/Clean Data/estimation_data.RDa")

estimation.data <- 
  estimation.data %>%
  mutate(pct_white_c = std(pct_white, robust = "2sd"),
         pct_black_c = std(pct_black, robust = "2sd"),
         pct_latino_c = std(pct_latino, robust = "2sd"),
         pct_asian_c = std(pct_asian, robust = "2sd"),
         pct_bachelors_c = std(pct_bachelors, robust = "2sd"),
         pct_clinton_16_c = std(pct_clinton_16, robust = "2sd"),
         pct_dem_house_16_c = std(pct_dem_house_16, robust = "2sd"),
         log_tot_voting_age_c = std(log_tot_voting_age, robust = "2sd"),
         log_median_hh_income_c = std(log_median_hh_income, robust = "2sd"))
```


# PAC Models

## Model Fitting

```{r}
biz.pac.fit <- brm(bf(business_pacs ~ no_corp_pacs + new_member + pct_white_c +
                        pct_black_c + pct_latino_c + pct_asian_c + 
                        pct_bachelors_c + pct_clinton_16_c + 
                        pct_dem_house_16_c + log_tot_voting_age_c +
                        log_median_hh_income_c,
                      hu ~ no_corp_pacs + new_member),
                   family = hurdle_gamma(link = "log", link_hu = "logit"),
                   prior = c(prior(normal(13, 12), class = Intercept),
                             prior(normal(-1, 0.5), class = b, 
                                   coef = "no_corp_pacsYES"),
                             prior(normal(0, 0.5), class = b),
                             prior(normal(0, 1), dpar = "hu", class = Intercept),
                             prior(normal(0, 0.5), dpar = "hu", class = b)),
                   sample_prior = "yes",
                   cores = 4,
                   iter = 4000,
                   backend = "cmdstan",
                   data = estimation.data)

describe_posterior(biz.pac.fit, ci = 0.9, ci_method = "hdi",
                   test = c("p_direction"))

num.pac.fit <- brm(num_pac_contribs ~ no_corp_pacs + new_member + pct_white_c +
                     pct_black_c + pct_latino_c + pct_asian_c + 
                     pct_bachelors_c + pct_clinton_16_c + 
                     pct_dem_house_16_c + log_tot_voting_age_c +
                     log_median_hh_income_c,
                   family = negbinomial(link = "log"),
                   prior = c(prior(normal(7, 6), class = Intercept),
                             prior(normal(-1, 0.5), class = b, 
                                   coef = "no_corp_pacsYES"),
                             prior(normal(0, 0.5), class = b)),
                   sample_prior = "yes",
                   cores = 4,
                   iter = 4000,
                   backend = "cmdstan",
                   data = estimation.data)

describe_posterior(num.pac.fit, ci = 0.9, ci_method = "hdi",
                   test = c("p_direction"))
```

## Model Diagnostics

### Prior Influence

```{r}
# business pac contributions
biz.pac.priors <- prior_samples(biz.pac.fit)
biz.pac.post <- posterior_samples(biz.pac.fit)

ggplot() +
  geom_density(data = biz.pac.priors, aes(x = b_no_corp_pacsYES)) +
  geom_density(data = biz.pac.post, aes(x = b_no_corp_pacsYES))

# number of business pac contributions
num.pac.priors <- prior_samples(num.pac.fit)
num.pac.post <- posterior_samples(num.pac.fit)

ggplot() +
  geom_density(data = num.pac.priors, aes(x = b_no_corp_pacsYES)) +
  geom_density(data = num.pac.post, aes(x = b_no_corp_pacsYES))
```

### Posterior Predictive Checks

```{r}
# business pac contributions --------------------------------------------------
y.biz.pac <- estimation.data$business_pacs

# extract the fitted values
y.rep <- posterior_predict(biz.pac.fit, draws = 500)
dim(y.rep)

ppc_dens_overlay(y = y.biz.pac[1:235], yrep = y.rep[1:100, ])

# number business pac contributors --------------------------------------------
y.num.pac <- estimation.data$num_pac_contribs

# extract the fitted values
y.rep <- posterior_predict(num.pac.fit, draws = 500)
dim(y.rep)

ppc_dens_overlay(y = y.num.pac[1:235], yrep = y.rep[1:100, ])
```


## Model Results

### Results Tables

```{r}
library(xtable)

# Business PAC Fit
xtable(describe_posterior(biz.pac.fit, ci = 0.9, ci_method = "hdi",
                   test = c("p_direction")))
```

### Coefficient Plots

```{r}
# Gamma Likelihood ------------------------------------------------------------
# extract posterior predictions
biz.pac.coef <- 
  biz.pac.fit %>%
  spread_draws(b_no_corp_pacsYES) %>%
  mutate(model = "Business PAC $")

## main effects
library(latex2exp)
biz.pac.coef %>%
  mutate(b_np = exp(b_no_corp_pacsYES) - 1) %>%
  ggplot() +
  stat_halfeyeh(aes(y = fct_reorder(model, b_np), x = b_np), 
                .width = c(0.9), 
                point_interval = median_hdi,
                fill = "#A4A4A4",
                color = "black",
                alpha = 0.9) +
  geom_vline(aes(xintercept = 0), linetype = "dashed", color = "grey55") +
  scale_x_continuous(labels = percent_format(),
                     breaks = pretty_breaks(n = 6)) +
  labs(x = TeX("% Change in Contributions ($\\e^{\\beta} - 1$)"), 
       y = "Outcome Variable") +
  theme_pubr() +
  theme(axis.text.y = element_text(angle = 90, vjust = 0, hjust = 0.5))
ggsave("Figures/Results/pac_gamma_coef.pdf", height = 4, width = 7) 

# Binomial Likelihood ---------------------------------------------------------
biz.pac.coef <- 
  biz.pac.fit %>%
  spread_draws(b_hu_no_corp_pacsYES) %>%
  mutate(model = "Business PAC $")

## main effects
library(latex2exp)
biz.pac.coef %>%
  mutate(b_np = plogis(b_hu_no_corp_pacsYES)) %>%
  ggplot() +
  stat_halfeyeh(aes(y = fct_reorder(model, b_np), x = b_np), 
                .width = c(0.9), 
                point_interval = median_hdi,
                fill = "#A4A4A4",
                color = "black",
                alpha = 0.9) +
  geom_vline(aes(xintercept = 0), linetype = "dashed", color = "grey55") +
  scale_x_continuous(labels = percent_format(),
                     breaks = pretty_breaks(n = 6)) +
  labs(x = TeX("Probability of Not Receiving Contributions ($logit^{-1}(\\beta)$)"), 
       y = "Outcome Variable") +
  theme_pubr()
ggsave("Figures/Results/pac_binom_coef.pdf", height = 4, width = 7) 
```


# Individual Models

## Model Fitting

```{r}
small.indv.fit <- brm(small_indiv ~ no_corp_pacs + new_member + pct_white_c +
                           pct_black_c + pct_latino_c + pct_asian_c + 
                           pct_bachelors_c + pct_clinton_16_c + 
                           pct_dem_house_16_c + log_tot_voting_age_c +
                           log_median_hh_income_c,
                      family = Gamma(link = "log"),
                      prior = c(prior(normal(13, 13), class = Intercept),
                                prior(normal(0.2, 0.5), class = b, 
                                      coef = "no_corp_pacsYES"),
                                prior(normal(0, 0.5), class = b)),
                      sample_prior = "yes",
                      cores = 4,
                      iter = 4000,
                      backend = "cmdstan",
                      data = estimation.data)

describe_posterior(small.indv.fit, ci = 0.9, ci_method = "hdi",
                   test = c("p_direction"))

biz.indv.fit <- brm(biz_contribs ~ no_corp_pacs + new_member + pct_white_c +
                      pct_black_c + pct_latino_c + pct_asian_c + 
                      pct_bachelors_c + pct_clinton_16_c + pct_dem_house_16_c + 
                      log_tot_voting_age_c + log_median_hh_income_c,
                    family = Gamma(link = "log"),
                    prior = c(prior(normal(13, 13), class = Intercept),
                              prior(normal(0, 0.5), class = b)),
                    sample_prior = "yes",
                    cores = 4,
                    iter = 4000,
                    backend = "cmdstan",
                    data = estimation.data)

describe_posterior(biz.indv.fit, ci = 0.9, ci_method = "hdi",
                   test = c("p_direction"))

out.dist.biz.fit <- brm(bf(out_of_dist_biz_contrib ~ no_corp_pacs + new_member + 
                             pct_white_c + pct_black_c + pct_latino_c + 
                             pct_asian_c + pct_bachelors_c + pct_clinton_16_c + 
                             pct_dem_house_16_c + log_tot_voting_age_c +
                             log_median_hh_income_c,
                           hu ~ no_corp_pacs + new_member),
                        family = hurdle_gamma(link = "log", link_hu = "logit"),
                        prior = c(prior(normal(13, 13), class = Intercept),
                                  prior(normal(0, 0.5), class = b),
                                  prior(normal(0, 1), dpar = "hu", class = Intercept),
                                  prior(normal(0, 0.5), dpar = "hu", class = b)),
                        sample_prior = "yes",
                        cores = 4,
                        iter = 4000,
                        backend = "cmdstan",
                        data = estimation.data)

describe_posterior(out.dist.biz.fit, ci = 0.9, ci_method = "hdi",
                   test = c("p_direction"))
```

## Model Diagnostics

### Prior Influence

```{r}
# small individual contributions ----------------------------------------------
small.indiv.priors <- prior_samples(small.indv.fit)
small.indiv.post <- posterior_samples(small.indv.fit)

ggplot() +
  geom_density(data = small.indiv.priors, aes(x = b_no_corp_pacsYES)) +
  geom_density(data = small.indiv.post, aes(x = b_no_corp_pacsYES))

# business individual contributions -------------------------------------------
biz.indv.priors <- prior_samples(biz.indv.fit)
biz.indv.post <- posterior_samples(biz.indv.fit)

ggplot() +
  geom_density(data = biz.indv.priors, aes(x = b)) +
  geom_density(data = biz.indv.post, aes(x = b_no_corp_pacsYES))

# business individual contributions from out-of-district ----------------------
out.biz.indv.priors <- prior_samples(out.dist.biz.fit)
out.biz.indv.post <- posterior_samples(out.dist.biz.fit)

ggplot() +
  geom_density(data = out.biz.indv.priors, aes(x = b)) +
  geom_density(data = out.biz.indv.post, aes(x = b_no_corp_pacsYES))
```

### Posterior Predictive Checks

```{r}
# # small individual contributions --------------------------------------------
y.small.indv <- estimation.data$small_indiv

# extract the fitted values
y.rep <- posterior_predict(small.indv.fit, draws = 500)
dim(y.rep)

ppc_dens_overlay(y = y.small.indv[1:235], yrep = y.rep[1:100, ]) + 
  xlim(0, 400000)

# business individual contributions -------------------------------------------
y.biz.indv <- estimation.data$indiv_biz

# extract the fitted values
y.rep <- posterior_predict(biz.indv.fit, draws = 500)
dim(y.rep)

ppc_dens_overlay(y = y.biz.indv[1:235], yrep = y.rep[1:100, ]) +
  xlim(0, 5000000)
```


## Model Results

### Results Tables

```{r}

```

### Coefficient Plots

```{r}
# Gamma Likelihood ------------------------------------------------------------
# extract posterior predictions
small.indv.coef <- 
  small.indv.fit %>%
  spread_draws(b_no_corp_pacsYES) %>%
  mutate(model = "Small Indiv. $")

biz.indv.coef <- 
  biz.indv.fit %>%
  spread_draws(b_no_corp_pacsYES) %>%
  mutate(model = "Business Indiv. $")

out.biz.indv.coef <- 
  out.dist.biz.fit %>%
  spread_draws(b_no_corp_pacsYES) %>%
  mutate(model = "Out-of-District Business Indiv. $")

indv.models <- 
  bind_rows(small.indv.coef, biz.indv.coef, out.biz.indv.coef) %>%
  mutate(b_np = exp(b_no_corp_pacsYES) - 1)

## main effects
library(latex2exp)
indv.models %>%
  #filter(model == "Out-of-District Business Indiv. $") %>%
  ggplot() +
  stat_halfeyeh(aes(y = fct_reorder(model, b_np), x = b_np), 
                .width = c(0.9), 
                point_interval = median_hdi,
                fill = "#A4A4A4",
                color = "black",
                alpha = 0.9) +
  geom_vline(aes(xintercept = 0), linetype = "dashed", color = "grey55") +
  scale_x_continuous(labels = percent_format(),
                     breaks = pretty_breaks(n = 6)) +
  labs(x = TeX("% Change in Contributions ($\\e^{\\beta} - 1$)"), 
       y = "Outcome Variable") +
  theme_pubr()
ggsave("Figures/Results/indv_gamma_coef.pdf", height = 4, width = 7) 

# Binomial Likelihood ---------------------------------------------------------
out.biz.indv.coef <- 
  out.dist.biz.fit %>%
  spread_draws(b_hu_no_corp_pacsYES) %>%
  mutate(model = "Out-of-District Business Indiv. $")

## main effects
library(latex2exp)
out.biz.indv.coef %>%
  rename(b_np = b_hu_no_corp_pacsYES) %>%
  ggplot() +
  stat_halfeyeh(aes(y = fct_reorder(model, b_np), x = b_np), 
                .width = c(0.9), 
                point_interval = median_hdi,
                fill = "#A4A4A4",
                color = "black",
                alpha = 0.9) +
  geom_vline(aes(xintercept = 0), linetype = "dashed", color = "grey55") +
  scale_x_continuous(labels = percent_format(),
                     breaks = pretty_breaks(n = 4)) +
  labs(x = TeX("Probability of Not Receiving Contributions ($logit^{-1}(\\beta)$)"), 
       y = "Outcome Variable") +
  theme_pubr()
ggsave("Figures/Results/indv_binom_coef.pdf", height = 4, width = 7) 
```


# Proportion Models

```{r}
estimation.data <- 
  estimation.data %>%
  mutate(tot_contribs = business_pacs + small_indiv + biz_contribs + 
           out_of_dist_biz_contrib,
         biz_pac_prop = business_pacs / tot_contribs,
         small_indiv_prop = small_indiv / tot_contribs,
         biz_contribs_prop = biz_contribs / tot_contribs,
         out_of_dist_biz_contrib_prop = out_of_dist_biz_contrib / tot_contribs,
         sum = biz_pac_prop + biz_contribs_prop + small_indiv_prop + 
           out_of_dist_biz_contrib_prop)

dir.estimation.data <- 
  estimation.data %>%
  filter(biz_pac_prop != 0) %>%
  filter(small_indiv_prop != 0) %>%
  filter(biz_contribs_prop != 0) %>%
  filter(out_of_dist_biz_contrib_prop != 0)

dir.estimation.data$y <- 
  with(dir.estimation.data, cbind(biz_pac_prop, small_indiv_prop, 
                                  biz_contribs_prop, 
                                  out_of_dist_biz_contrib_prop))

dir.fit <- brm(y ~ no_corp_pacs + new_member + pct_white_c +
                 pct_black_c + pct_latino_c + pct_asian_c + 
                 pct_bachelors_c + pct_clinton_16_c + 
                 pct_dem_house_16_c + log_tot_voting_age_c +
                 log_median_hh_income_c,
               family = dirichlet(link = "logit"),
               cores = 4,
               iter = 4000,
               backend = "cmdstanr",
               data = dir.estimation.data)
describe_posterior(dir.fit, ci = 0.9, ci_method = "hdi",
                   test = c("p_direction"))

ce <- conditional_effects(dir.fit, categorical = T, effects = "no_corp_pacs", 
                          prob = 0.9, method = "posterior_epred")[[1]]

ggplot(data = ce, aes(x = no_corp_pacs, y = estimate__, ymin = lower__,
                      ymax = upper__, shape = cats__, color = cats__)) +
  geom_point(position = position_dodge(width = 0.5), size = 4.5) +
  geom_errorbar(position = position_dodge(width = 0.5), width = 0.2) +
  scale_color_manual(values = c("gray62", "gray38", "grey20", "black"),
                     labels = c("Business PACs", "Small Individual", 
                                "Business Individual", 
                                "Out-of-District Business Indiv.")) +
  scale_shape_manual(values = c(15, 19, 17, 18),
                     labels = c("Business PACs", "Small Individual", 
                                "Business Individual", 
                                "Out-of-District Business Indiv.")) +
  labs(x = "Candidate Accepts Corporate PAC Contributions?",
       y = "Proportion of Contributions",
       color = "Contributions from:",
       shape = "Contributions from:") +
  scale_x_discrete(labels = c("Yes", "No")) +
  scale_y_continuous(labels = percent_format(), limits = c(0, 0.6),
                     breaks = pretty_breaks(n = 6)) +
  theme_pubclean()
ggsave("Figures/dir_model_results.pdf", plot = last_plot(),
       width = 9, height = 5)
```